### 2016-04-05 milestone1/paper/paper.tex
added datasets and structure [milestone1]

%%%%%%%%%%%%%%%%%%%%%%% file moduleX_template.tex %%%%%%%%%%%%%%%%%
%
%
% This is a template for creating your papers for the course KRW
% It is based on the standard Latex template for Springer publications
% but contains a suggestion for the structure and some content of the
% paper.
%
% Please adapt this document wherever needed.
%
% For more information about the required Latex Style check the document
% typeinst.pdf in the StyleFiles directory.
%
%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%

\documentclass[runningheads,a4paper]{StyleFiles/llncs}

\usepackage{url}
\usepackage{graphicx}
\usepackage{amssymb}

\newcommand{\keywords}[1]{\par\addvspace\baselineskip
\noindent\keywordname\enspace\ignorespaces#1}

\begin{document}

\mainmatter  % start of an individual contribution

% first the title is needed
\title{Data- and Systems Paper: your title here}

% a short form should be given in case it is too long for the running head
\titlerunning{Data- and Systems Paper}

% the name(s) of the author(s) follow(s) next
%
% NB: Chinese authors should write their first names(s) in front of
% their surnames. This ensures that the names appear correctly in
% the running heads and the author index.
%
\author{Names}
%
\authorrunning{Put your names here}
% (feature abused for this document to repeat the title also on left hand pages)

% the affiliations are given next; don't give your e-mail address
% unless you accept that it will be published
\institute{\url{first@email.nl} \and \url{second@email.nl}}

\maketitle

\begin{abstract}
The abstract should summarize the contents of the paper and should
contain at least 70 and at most 150 words. It should be written using the
\emph{abstract} environment.
\end{abstract}

\section{Introduction}
% Introduce the sections that follow. What is the core contribution of this paper, and why is that interesting? It is useful to start with a real-life problem, and then explain how your system/dataset (will) solve(s) that problem by means of KR technology. Why is this novel? Has this (or something similar) been done before?

\section{Scenario / Use Case}
% you could describe the use-case you have in mind that makes use of your chosen data about some matter concerning Amsterdam. Describe the overall idea, but also some concrete usage scenarios (e.g. as part of an actual system). Maybe interaction flow-diagrams etc could be useful, or what is called "personas" https://en.wikipedia.org/wiki/Persona_%28user_experience%29.

\section{Data sources}
% which datasets have you used and converted? Provide the core properties of those datasets. Also describe other datasets that you might want to integrate, and even data that still needs to be found, or even created.

\section{Building Knowledge Graphs}
% Give details about the data curation and conversion process: which (parts of the) data have you converted, why and how. Which tools did you use? If you wrote your own code, provide a pointer to it. You might wish to add subsections discussing conceptual and technical problems in this process.

\section{Semantic considerations}
% In the 2nd and 3rd lectures we introduced formal Semantics for RDF, RDFS and SPARQL. Please use your own knowledge graph to give some (simple) examples for entailment. Choose a subgraph G (feel free to adapt it if needed) and explain what it stands for, and what the intended meaning is. Given the problem and use-case you have in mind, how do the examples of entailment contribute to a solution?

\subsection{RDF and RDFS entailment}
% Give a small graph G' which is entailed by your subgraph G. Feel free to use the same G' that you want to use in your SPARQL query later. Explain why G' is entailed (this is really simple).

% Extend G with a few RDFS triples T={t1,...,tn} and provide a small graph G'' so that G u T |= G'' but not G u T |= G'.

\subsection{SPARQL}
% Give a SPARQL query that provides different answers on the basis of interpreting the knowledge graph with an RDF entailment regime as opposed to an RDFS regime, and explain why you get different answers.

% What is the relation between this fact in terms of model checking and reasoning?

% Investigate and discuss whether there are interesting cases of entailment in your own data.

\section{Discussion}
% Here you summarize the preceding sections, describe the lessons learnt and discuss future work.
% Present a screenshot of a mock-up or working (preferred!) version of your system an describe what it does.
% Argue why the preceding sections show that your solution (partially) solves the problem you introduced in the introduction.

\bibliographystyle{plain}
\bibliography{bibliography}

\end{document}

### 2016-04-05 milestone1/paper/paper.tex
make a start on the paper [milestone1]

@@
 Maybe interaction flow-diagrams etc could be useful, or what is called "personas" https://en.wikipedia.org/wiki/Persona_%28user_experience%29.
+The integration of those datasets could be an advantage where the need of
+cross-searching them is necessary. Let's take the example of John, whom is in a
+wheelchair and needs to go to a theater of Friday night. John would be really
+happy to know in advance where the parking slots closest to the theater are. By
+using our integrated dataset, John, could make such a search in a
+straightforward way.
+
+Another use-case consists in whether we are interested at looking if the
+distribution of parking slots near theaters or main events is uniform. In this
+case the dataset would be useful for an interactive visualization.
 
@@
 Also describe other datasets that you might want to integrate, and even data that still needs to be found, or even created.
+We decided to integrate the Gemeente's open data about theater events, museums
+and galleries and handicap's parking slots. Those datasets are available in CSV
+or JSON formats. We chose to convert from the JSON format because it is a more
+powerful representation than CSV and because JSON and RDF formats can be easily
+mapped one to another.
+
+\subsection{Theaters Dataset}
+% TODO describe theaters dataset (fields, contained data, semantics)
+
+\subsection{Museums and Galleries Dataset}
+% TODO describe museums and galleries dataset
+
+\subsection{Handicap's Parking Slots Dataset}
+% TODO describe this dataset
 

### 2016-04-05 milestone1/convert-theaters.py
started converting theaters dataset [milestone1]

@@ -1,0 +1,32 @@
+#|/usr/bin/env python
+
+import json
+from rdflib import Dataset, URIRef, Literal, Namespace, RDF, RDFS, OWL, XSD
+from iribaker import to_iri
+
+
+with open('data/Theater.json', 'rb') as f:
+    theaters = json.load(f)
+
+    resource = 'http://data.krw.d2s.labs.vu.nl/group6/resource/'
+    RESOURCE = Namespace(resource)
+
+    vocab = 'http://data.krw.d2s.labs.vu.nl/group6/vocab/'
+    VOCAB = Namespace(vocab)
+
+    graph_uri = URIRef(resource + 'milestone1')
+
+    dataset = Dataset()
+    dataset.bind('g6data', RESOURCE)
+    dataset.bind('g6vocab', VOCAB)
+
+    graph = dataset.graph(graph_uri)
+
+    for event_data in theaters:
+        event = URIRef(to_iri(resource + event_data['title']))
+        title = Literal(event_data['title'], datatype=XSD['string'])
+
+        graph.add((event, VOCAB['title'], title))
+
+    print dataset.serialize(format='trig')
+

### 2016-04-06 milestone1/convert-datasets.py
first conversion of theaters and museums datasets [mls1]

@@ -1,0 +1,105 @@
+#!/usr/bin/env python
+
+import json
+from datetime import datetime
+from rdflib import Dataset, URIRef, Literal, Namespace, RDF, RDFS, OWL, XSD
+from iribaker import to_iri
+
+
+def convert_dataset(path):
+    f = open(path, 'r')
+    theaters = json.load(f)
+
+    resource = 'http://data.krw.d2s.labs.vu.nl/group6/resource/'
+    RESOURCE = Namespace(resource)
+
+    vocab = 'http://data.krw.d2s.labs.vu.nl/group6/vocab/'
+    VOCAB = Namespace(vocab)
+
+    graph_uri = URIRef(resource + 'milestone1')
+
+    dataset = Dataset()
+    dataset.bind('g6data', RESOURCE)
+    dataset.bind('g6vocab', VOCAB)
+    dataset.default_context.parse('vocab.ttl', format='turtle')
+
+    graph = dataset.graph(graph_uri)
+
+    for event_data in theaters:
+        event = URIRef(to_iri(resource + event_data['title']))
+        title = Literal(event_data['title'], datatype=XSD['string'])
+        
+        dates = event_data['dates']
+        if dates != []:
+            single_dates = [Literal(datetime.strptime(d, '%d-%m-%Y').date())
+                for d in dates['singles']] if dates.has_key('singles') else []
+            start_date = Literal(datetime.strptime(dates['startdate'], '%d-%m-%Y').date()) \
+                if dates.has_key('startdate') else None
+            end_date = Literal(datetime.strptime(dates['enddate'], '%d-%m-%Y').date()) \
+                if dates.has_key('enddate') and dates['enddate'] != '' else None
+
+        location_dict = event_data['location']
+        location = URIRef(to_iri(resource + location_dict['name']))
+        location_name = Literal(location_dict['name'], datatype=XSD['string'])
+        location_address = Literal(location_dict['adress'])
+        location_city = Literal(location_dict['city'])
+        location_zip = Literal(location_dict['zipcode'])
+        location_lat = Literal(location_dict['latitude'])
+        location_lon = Literal(location_dict['longitude'])
+
+        if event_data['media']:
+            medias = [(Literal(m['url']), m['main'] == 'true') for m in event_data['media']]
+
+        urls = [Literal(url) for url in event_data['urls']]
+
+        details_dict = event_data['details']
+        details = []
+        for lang in details_dict.iterkeys():
+            detail = {}
[…]

### 2016-04-06 milestone1/convert-theaters.py

@@ -1,32 +1,0 @@
-#|/usr/bin/env python
-
-import json
-from rdflib import Dataset, URIRef, Literal, Namespace, RDF, RDFS, OWL, XSD
-from iribaker import to_iri
-
-
-with open('data/Theater.json', 'rb') as f:
-    theaters = json.load(f)
-
-    resource = 'http://data.krw.d2s.labs.vu.nl/group6/resource/'
-    RESOURCE = Namespace(resource)
-
-    vocab = 'http://data.krw.d2s.labs.vu.nl/group6/vocab/'
-    VOCAB = Namespace(vocab)
-
-    graph_uri = URIRef(resource + 'milestone1')
-
-    dataset = Dataset()
-    dataset.bind('g6data', RESOURCE)
-    dataset.bind('g6vocab', VOCAB)
-
-    graph = dataset.graph(graph_uri)
-
-    for event_data in theaters:
-        event = URIRef(to_iri(resource + event_data['title']))
-        title = Literal(event_data['title'], datatype=XSD['string'])
-
-        graph.add((event, VOCAB['title'], title))
-
-    print dataset.serialize(format='trig')
-

### 2016-04-06 milestone1/convert-datasets.py
use geo ontology [mls1]

@@ -12,9 +12,10 @@ def convert_dataset(path):
 
     resource = 'http://data.krw.d2s.labs.vu.nl/group6/resource/'
     RESOURCE = Namespace(resource)
-
     vocab = 'http://data.krw.d2s.labs.vu.nl/group6/vocab/'
     VOCAB = Namespace(vocab)
+    geo = 'http://www.w3.org/2003/01/geo/wgs84_pos#'
+    GEO = Namespace(geo)
 
     graph_uri = URIRef(resource + 'milestone1')
 
@@ -39,26 +40,30 @@ def convert_dataset(path):
                 if dates.has_key('enddate') and dates['enddate'] != '' else None
 
         location_dict = event_data['location']
-        location = URIRef(to_iri(resource + location_dict['name']))
-        location_name = Literal(location_dict['name'], datatype=XSD['string'])
-        location_address = Literal(location_dict['adress'])
-        location_city = Literal(location_dict['city'])
-        location_zip = Literal(location_dict['zipcode'])
-        location_lat = Literal(location_dict['latitude'])
-        location_lon = Literal(location_dict['longitude'])
+        if location_dict['name'] != '':
+            location = URIRef(to_iri(resource + location_dict['name']))
+            location_name = Literal(location_dict['name'], datatype=XSD['string'])
+            location_address = Literal(location_dict['adress'])
+            location_city = Literal(location_dict['city'])
+            location_zip = Literal(location_dict['zipcode'])
+            location_lat = Literal(location_dict['latitude'])
+            location_lon = Literal(location_dict['longitude'])
 
         if event_data['media']:
-            medias = [(Literal(m['url']), m['main'] == 'true') for m in event_data['media']]
+            medias = [(Literal(m['url'], datatype=XSD['anyURI']), m['main'] == 'true') for m in event_data['media']]
 
-        urls = [Literal(url) for url in event_data['urls']]
+        urls = [Literal(url, datatype=XSD['anyURI']) for url in event_data['urls']]
 
         details_dict = event_data['details']
         details = []
         for lang in details_dict.iterkeys():
             detail = {}
-            detail['calendar_summary'] = Literal(details_dict[lang]['calendarsummary'], lang=lang)
-            detail['long_description'] = Literal(details_dict[lang]['longdescription'], lang=lang)
-            detail['short_description'] = Literal(details_dict[lang]['shortdescription'], lang=lang)
+            if details_dict[lang]['calendarsummary'] != '':
[…]

### 2016-04-06 milestone1/convert-datasets.py
upload datasets to stardog [mls1]

@@ -4,6 +4,7 @@ import json
 from datetime import datetime
 from rdflib import Dataset, URIRef, Literal, Namespace, RDF, RDFS, OWL, XSD
 from iribaker import to_iri
+import requests
 
 
 def convert_dataset(path):
@@ -104,11 +105,33 @@ def convert_dataset(path):
     return dataset
 
 
+def upload_to_stardog(data):
+    TUTORIAL_REPOSITORY = "http://stardog.krw.d2s.labs.vu.nl/group6"
+    transaction_begin_url = TUTORIAL_REPOSITORY + "/transaction/begin"
+    
+    # Start the transaction, and get a transaction_id
+    response = requests.post(transaction_begin_url, headers={'Accept': 'text/plain'})
+    transaction_id = response.content
+    print 'Transaction ID', transaction_id
+
+    # POST the data to the transaction
+    post_url = TUTORIAL_REPOSITORY + "/" + transaction_id + "/add"
+    response = requests.post(post_url, data=data, headers={'Accept': 'text/plain', 'Content-type': 'application/trig'})
+
+    # Close the transaction
+    transaction_close_url = TUTORIAL_REPOSITORY + "/transaction/commit/" + transaction_id
+    response = requests.post(transaction_close_url)
+
+    return str(response.status_code)
+
+
 t_dataset = convert_dataset('data/Theater.json')
 with open('data/Theater.trig', 'w') as f:
     t_dataset.serialize(f, format='trig')
+upload_to_stardog(t_dataset.serialize(format='trig'))
 
 mg_dataset = convert_dataset('data/MuseaGalleries.json')
 with open('data/MuseaGalleries.trig', 'w') as f:
     mg_dataset.serialize(f, format='trig')
+upload_to_stardog(mg_dataset.serialize(format='trig'))
 

### 2016-04-06 milestone1/convert-datasets.py
some refactoring [mls1]

@@ -5,29 +5,25 @@ from datetime import datetime
 from rdflib import Dataset, URIRef, Literal, Namespace, RDF, RDFS, OWL, XSD
 from iribaker import to_iri
 import requests
+from SPARQLWrapper import SPARQLWrapper, JSON
+from pprint import pprint
 
 
-def convert_dataset(path):
+resource = 'http://data.krw.d2s.labs.vu.nl/group6/resource/'
+RESOURCE = Namespace(resource)
+vocab = 'http://data.krw.d2s.labs.vu.nl/group6/vocab/'
+VOCAB = Namespace(vocab)
+geo = 'http://www.w3.org/2003/01/geo/wgs84_pos#'
+GEO = Namespace(geo)
+
+repo_url = "http://stardog.krw.d2s.labs.vu.nl/group6"
+
+
+def convert_dataset(path, dataset, graph):
     f = open(path, 'r')
-    theaters = json.load(f)
+    json_data = json.load(f)
 
-    resource = 'http://data.krw.d2s.labs.vu.nl/group6/resource/'
-    RESOURCE = Namespace(resource)
-    vocab = 'http://data.krw.d2s.labs.vu.nl/group6/vocab/'
-    VOCAB = Namespace(vocab)
-    geo = 'http://www.w3.org/2003/01/geo/wgs84_pos#'
-    GEO = Namespace(geo)
-
-    graph_uri = URIRef(resource + 'milestone1')
-
-    dataset = Dataset()
-    dataset.bind('g6data', RESOURCE)
-    dataset.bind('g6vocab', VOCAB)
-    dataset.default_context.parse('vocab.ttl', format='turtle')
-
-    graph = dataset.graph(graph_uri)
-
-    for event_data in theaters:
+    for event_data in json_data:
         event = URIRef(to_iri(resource + event_data['title']))
         title = Literal(event_data['title'], datatype=XSD['string'])
         
@@ -102,12 +98,25 @@ def convert_dataset(path):
             if detail.has_key('short_description'):
                 graph.add((event, VOCAB['short_description'], detail['short_description']))
 
-    return dataset
+    return dataset, graph
+
+
+def drop_stardog():
+    query = "DELETE { ?s ?p ?o . } WHERE { ?s ?p ?o  . }"
+
+    endpoint = repo_url + '/query'
+    sparql = SPARQLWrapper(endpoint)
+    sparql.setQuery(query)
+
+    sparql.setReturnFormat(JSON)
+    sparql.addParameter('Accept','application/sparql-results+json')
+
[…]

### 2016-04-06 milestone1/convert-datasets.py
convert parking dataset [mls1]

@@ -24,8 +24,8 @@ def convert_dataset(path, dataset, graph):
     json_data = json.load(f)
 
     for event_data in json_data:
-        event = URIRef(to_iri(resource + event_data['title']))
-        title = Literal(event_data['title'], datatype=XSD['string'])
+        event = URIRef(to_iri(resource + event_data['title'].strip()))
+        title = Literal(event_data['title'].strip(), datatype=XSD['string'])
         
         dates = event_data['dates']
         if dates != []:
@@ -37,30 +37,32 @@ def convert_dataset(path, dataset, graph):
                 if dates.has_key('enddate') and dates['enddate'] != '' else None
 
         location_dict = event_data['location']
-        if location_dict['name'] != '':
-            location = URIRef(to_iri(resource + location_dict['name']))
-            location_name = Literal(location_dict['name'], datatype=XSD['string'])
-            location_address = Literal(location_dict['adress'])
-            location_city = Literal(location_dict['city'])
-            location_zip = Literal(location_dict['zipcode'])
-            location_lat = Literal(location_dict['latitude'])
-            location_lon = Literal(location_dict['longitude'])
+        location_d_name = location_dict['name'].strip()
+        if location_d_name != '':
+            place = URIRef(to_iri(resource + location_d_name))
+            place_name = Literal(location_d_name, datatype=XSD['string'])
+            location = URIRef(to_iri(resource + location_dict['adress'].strip()))
+            location_address = Literal(location_dict['adress'].strip())
+            location_city = Literal(location_dict['city'].strip())
+            location_zip = Literal(location_dict['zipcode'].strip())
+            location_lat = Literal(location_dict['latitude'].strip())
+            location_lon = Literal(location_dict['longitude'].strip())
 
         if event_data['media']:
-            medias = [(Literal(m['url'], datatype=XSD['anyURI']), m['main'] == 'true') for m in event_data['media']]
+            medias = [(Literal(m['url'].strip(), datatype=XSD['anyURI']), m['main'].strip() == 'true') for m in event_data['media']]
 
-        urls = [Literal(url, datatype=XSD['anyURI']) for url in event_data['urls']]
+        urls = [Literal(url.strip(), datatype=XSD['anyURI']) for url in event_data['urls']]
 
         details_dict = event_data['details']
         details = []
         for lang in details_dict.iterkeys():
             detail = {}
[…]

### 2016-04-06 milestone1/convert-datasets.py
multiple graphs [mls1]

@@ -19,9 +19,11 @@ GEO = Namespace(geo)
 repo_url = "http://stardog.krw.d2s.labs.vu.nl/group6"
 
 
-def convert_dataset(path, dataset, graph):
+def convert_dataset(path, dataset, graph_uri):
     f = open(path, 'r')
     json_data = json.load(f)
+
+    graph = dataset.graph(graph_uri)
 
     for event_data in json_data:
         event = URIRef(to_iri(resource + event_data['title'].strip()))
@@ -66,6 +68,7 @@ def convert_dataset(path, dataset, graph):
             details.append(detail)
 
         
+        graph.add((event, RDF.type, VOCAB['Event']))
         graph.add((event, RDFS.label, title))
         
         if dates != []:
@@ -78,14 +81,14 @@ def convert_dataset(path, dataset, graph):
         
         if location_dict['name'] != '':
             graph.add((event, VOCAB['place'], place))
-            graph.add((place, RDFS.label, place_name))
-            graph.add((place, VOCAB['location'], location))
-            graph.add((location, RDFS.label, location_address))
-            graph.add((location, VOCAB['address'], location_address))
-            graph.add((location, VOCAB['city'], location_city))
-            graph.add((location, VOCAB['zipcode'], location_zip))
-            graph.add((location, GEO['lat'], location_lat))
-            graph.add((location, GEO['long'], location_lon))
+            dataset.add((place, RDFS.label, place_name))
+            dataset.add((place, VOCAB['location'], location))
+            dataset.add((location, RDFS.label, location_address))
+            dataset.add((location, VOCAB['address'], location_address))
+            dataset.add((location, VOCAB['city'], location_city))
+            dataset.add((location, VOCAB['zipcode'], location_zip))
+            dataset.add((location, GEO['lat'], location_lat))
+            dataset.add((location, GEO['long'], location_lon))
 
         if medias:
             for m in medias:
@@ -105,9 +108,11 @@ def convert_dataset(path, dataset, graph):
     return dataset, graph
 
 
-def convert_parking_dataset(path, dataset, graph):
+def convert_parking_dataset(path, dataset, graph_uri):
     f = open(path, 'r')
[…]

### 2016-04-06 milestone1/convert-datasets.py
fixed graphs [mls1]

@@ -202,10 +202,12 @@ dataset.bind('g6vocab', VOCAB)
 dataset, t_graph = convert_dataset(
     'data/Theater.json', dataset, URIRef(graph_uri_base + 'theaters'))
 serialize_upload('data/theaters.trig', dataset)
+dataset.remove_graph(t_graph)
 
 dataset, mg_graph = convert_dataset(
     'data/MuseaGalleries.json', dataset, URIRef(graph_uri_base + 'museums'))
 serialize_upload('data/museums.trig', dataset)
+dataset.remove_graph(mg_graph)
 
 dataset, park_graph = convert_parking_dataset(
     'data/gehandicaptenparkeerplaatsen.json', dataset, URIRef(graph_uri_base + 'parking-slots'))

### 2016-04-06 milestone1/paper/paper.tex
moved StyleFiles to root
report progress

--- 2016-04-05 milestone1/paper/paper.tex
@@
 
-\documentclass[runningheads,a4paper]{StyleFiles/llncs}
+\documentclass[runningheads,a4paper]{../../StyleFiles/llncs}
 
@@
 Has this (or something similar) been done before?
+%TODO read WHOLE section again and make it pretty
+Amsterdam is a busy city that offers a variety of events and a common problem when attending such events is that Parking Spots are often scarce.
+Specifically, for handicap people this is an issue that should not be overlooked since they require more time to commute.
+Hence, having knowledge about close parking spots is specially useful to them.
+
+However, acquiring this information is not straightforward.
+The location of venues is not associated with Parking Spot locations, and users usually have to find them themselves by means of maps or driving around.
+Solving this problem would bring benefits to attendees.
+%TODO is this novel?
+
+In this project we create a web application that serves as a unique point for finding locations of venues and parking spots related to an event.
+We decided to work with Museum Galleries and Theaters to keep the scope of the project manageable.
+To do so we convert existing datasets to RDF format and query them to get the desired results.
+
+In the following section we delve deeper into cases where our proposed solution could be applied.
+Next, we describe the datasets and continue to explain the data management process to abstract the knowledge from those datasets.
+Then, we explain the semantics in our data set and provide examples of the queries we used to build the application.
+We finalize with a demo of the application and a discussion of the work done.
 
@@
 
+As stated in the introduction, the integration of venues and parking spot locations may bring benefits to attendees.
+Our application will provide a convenient and time-saving option for attendees to find parking spots.
+Furthermore, by using our application it is guaranteed that the best parking spot will be suggested %TODO not sure about this though ...
+
+Hereby we provide three concrete use-cases where our application's benefits are to be maximized.
+
+\begin{enumerate}
+	% Planning in advance
+	\item John is in a wheelchair and wants to go to an exhibition in Van Gogh Museum Friday night.
+John likes to plan things in advance and would like to know where the parking slots closest to the theater are.
+\\
+	The day before the show, John uses our application to find such parking spots and heads to the show confidently. 
+	% Quick search once in the theater (on the fly)
+	\item Peter is rushing to get to an exhibition in Van Gogh Museum and is looking for the closest parking spots.
+He quickly browses our application and finds an area with several parking spots.
+He drives in that direction hoping to find an available spot.
+	% Event manager
+	\item Mary is an event organizer who wants to host an exhibition in a Museum next month.
+She is looking for an accessible venue so she would like to see the distribution of parking spots around the main galleries in Amsterdam.
+She uses the interactive visualization in our application to explore and choose the best venue.
+\end{enumerate}
+
 \section{Data sources}

### 2016-04-06 milestone1/paper/paper.tex
report

@@
 % first the title is needed
-\title{Data- and Systems Paper: your title here}
+\title{Data- and Systems Paper: Identifying Handicap Parking Spots for Event's Venues}
 
@@
 %
-\author{Names}
+\author{Alivanistos, Dimitris. \\ Baez, Selene. \\ Jemmett, Andrea. }
 %
-\authorrunning{Put your names here}
+\authorrunning{Alivanistos, Dimitris. \\ Baez, Selene. \\ Jemmett, Andrea.}
 % (feature abused for this document to repeat the title also on left hand pages)
@@
 % unless you accept that it will be published
-\institute{\url{first@email.nl} \and \url{second@email.nl}}
+\institute{\url{first@vu.nl} \and \url{second@vu.nl}}
 
@@
 Also describe other datasets that you might want to integrate, and even data that still needs to be found, or even created.
-We decided to integrate the Gemeente's open data about theater events, museums
-and galleries and handicap's parking slots. Those datasets are available in CSV
-or JSON formats. We chose to convert from the JSON format because it is a more
-powerful representation than CSV and because JSON and RDF formats can be easily
-mapped one to another.
+We decided to integrate the Gemeente's open data about theater events, museums and galleries and handicap's parking slots.
+Those datasets are available in CSV or JSON formats.
+We chose to convert from the JSON format because it is a more powerful representation than CSV and because JSON and RDF formats can be easily mapped one to another.
 
@@
 % TODO describe theaters dataset (fields, contained data, semantics)
+The theaters dataset contains the following fields:
+
+\begin{center}
+	\begin{tabular}{| c | c | c | c | c | c | c | c | c | c | c | c | c | c | c | c | c | c | c | c | c | c | c | c | c |}
+		\hline
+		\textbf{Trcid} & \textbf{Title} & \textbf{Shortdescription} & \textbf{Longdescription} & \textbf{Calendarsummary} & \textbf{TitleEN} & \textbf{ShortdescriptionEN} & \textbf{LongdescriptionEN} & \textbf{CalendarsummaryEN } & \textbf{Types} & \textbf{Ids} & \textbf{Locatienaam} & \textbf{City} & \textbf{Adres} & \textbf{Zipcode} & \textbf{Latitude } & \textbf{Latitude} & \textbf{Urls} & \textbf{Media} & \textbf{Thumbnail} & \textbf{Datepattern\_startdate} & \textbf{Datepattern\_enddate} & \textbf{Singledates} & \textbf{Type1} & \textbf{Lastupdated} \\ \hline
+
+		\hline
+	\end{tabular}
+\end{center}
 

### 2016-04-07 milestone1/convert-datasets.py
use external dbpedia ontology [mls1]

@@ -9,12 +9,16 @@ from SPARQLWrapper import SPARQLWrapper, JSON
 from pprint import pprint
 
 
-resource = 'http://data.krw.d2s.labs.vu.nl/group6/resource/'
+resource = 'http://data.krw.d2s.labs.vu.nl/group6/findaslot/resource/'
 RESOURCE = Namespace(resource)
-vocab = 'http://data.krw.d2s.labs.vu.nl/group6/vocab/'
+vocab = 'http://data.krw.d2s.labs.vu.nl/group6/findaslot/vocab/'
 VOCAB = Namespace(vocab)
 geo = 'http://www.w3.org/2003/01/geo/wgs84_pos#'
 GEO = Namespace(geo)
+dbo = 'http://dbpedia.org/ontology/'
+DBO = Namespace(dbo)
+dbr = 'http://dbpedia.org/resource/'
+DBR = Namespace(dbr)
 
 repo_url = "http://stardog.krw.d2s.labs.vu.nl/group6"
 
@@ -24,6 +28,7 @@ def convert_dataset(path, dataset, graph_uri):
     json_data = json.load(f)
 
     graph = dataset.graph(graph_uri)
+    country = URIRef(to_iri(dbr + 'Kingdom of the Netherlands'))
 
     for event_data in json_data:
         event = URIRef(to_iri(resource + event_data['title'].strip()))
@@ -43,12 +48,13 @@ def convert_dataset(path, dataset, graph_uri):
         if location_d_name != '':
             place = URIRef(to_iri(resource + location_d_name))
             place_name = Literal(location_d_name, datatype=XSD['string'])
-            location = URIRef(to_iri(resource + location_dict['adress'].strip()))
+            location_city_str = location_dict['city'].strip().capitalize()
+            location = URIRef(to_iri(resource + location_city_str + '/' + location_dict['adress'].strip()))
+            location_city = Literal(location_city_str)
             location_address = Literal(location_dict['adress'].strip())
-            location_city = Literal(location_dict['city'].strip())
             location_zip = Literal(location_dict['zipcode'].strip())
-            location_lat = Literal(location_dict['latitude'].strip())
-            location_lon = Literal(location_dict['longitude'].strip())
+            location_lat = Literal(float(location_dict['latitude'].replace(',', '.')))
+            location_lon = Literal(float(location_dict['longitude'].replace(',', '.')))
 
         if event_data['media']:
[…]

### 2016-04-07 milestone1/paper/paper.tex
visualization and report

@@
 \usepackage{amssymb}
+\usepackage{listings}
+\lstset{language=SQL,morekeywords={PREFIX,java,rdf,rdfs,url}}
 
@@
 	% Quick search once in the theater (on the fly)
-	\item Peter is rushing to get to an exhibition in Van Gogh Museum and is looking for the closest parking spots.
+	\item Peter broke his leg last month and his friends, as an attempt to cheer him up, invited him to come to a comedy show.
+He is quite late and is rushing to find the closest parking spots.
 He quickly browses our application and finds an area with several parking spots.
@@
 She is looking for an accessible venue so she would like to see the distribution of parking spots around the main galleries in Amsterdam.
-She uses the interactive visualization in our application to explore and choose the best venue.
+She has a list of five places in mind and uses our application to explore and choose the best venue.
 \end{enumerate}
@@
 Given the problem and use-case you have in mind, how do the examples of entailment contribute to a solution?
+Here is our vocabulary (Figure \ref{fig:ontology})
+
+\begin{figure}[h]
+	\centering
+	\includegraphics[width=1\textwidth]{img/ontology.jpg}
+	\caption{Visualization of the Ontology graph}
+	\label{fig:ontology}
+\end{figure}
 
@@
 % Give a SPARQL query that provides different answers on the basis of interpreting the knowledge graph with an RDF entailment regime as opposed to an RDFS regime, and explain why you get different answers.
+
+\begin{lstlisting}[captionpos=b, caption=SPARQL query, label=lst:sparql,
+basicstyle=\ttfamily,frame=bt]
+prefix rdf: <http://www.w3.org/1999/02/22-rdf-syntax-ns#>
+prefix owl: <http://www.w3.org/2002/07/owl#>
+prefix xsd: <http://www.w3.org/2001/XMLSchema#>
+prefix rdfs: <http://www.w3.org/2000/01/rdf-schema#>
+
+prefix : <http://data.krw.d2s.labs.vu.nl/group6/findaslot/vocab/>
+prefix data: <http://data.krw.d2s.labs.vu.nl/group6/findaslot/resource/>
+prefix geo: <http://www.w3.org/2003/01/geo/wgs84_pos#>
+prefix math: <http://www.w3.org/2005/xpath-functions/math#>
+prefix dbo: <http://dbpedia.org/ontology/>
+
+select distinct ?venue ?slot ?slat ?slong ?elat ?elong ?dist
+where {
+?eslot a :ParkingSlot .
+?eslot rdfs:label ?slot .
+?eslot dbo:location ?slocation .
+?slocation geo:lat ?slat ; geo:long ?slong .
+
+data:Podium_Mozaïek a :Venue .
+data:Podium_Mozaïek rdfs:label ?venue .
+data:Podium_Mozaïek dbo:location ?elocation .
+?elocation geo:lat ?elat ; geo:long ?elong .
+
+bind(xsd:double(?slat) * math:pi() / xsd:double(180) as ?la1) .
+bind(xsd:double(?slong) * math:pi() / xsd:double(180) as ?lo1) .
+bind(xsd:double(?elat) * math:pi() / xsd:double(180) as ?la2) .
+bind(xsd:double(?elong) * math:pi() / xsd:double(180) as ?lo2) .
+bind(?lo2 - ?lo1 as ?l) .
+bind(math:acos(math:sin(?la2)*math:sin(?la1) + math:cos(?la1)*math:cos(?la1)*math:cos(?l)) * xsd:double(6371000) as ?dist) .
+}
+order by ?dist
+
+\end{lstlisting}
 

### 2016-04-07 milestone1/paper/paper.tex
report update
smth

@@
 % unless you accept that it will be published
-\institute{\url{first@vu.nl} \and \url{second@vu.nl}}
+\institute{\url{d.alivanistos@student.vu.nl} \and \url{s.baezsantamaria@student.vu.nl} \and \url{a.jemmett@student.vu.nl}}
 
@@
 
-Hereby we provide three concrete use-cases where our application's benefits are to be maximized.
+Hereby we provide three concrete use-cases where our application's benefits are to be maximized. A general use-case diagram is provided in Figure \ref{fig:use-case}.
 
@@
 \end{enumerate}
+
+\begin{figure}[h]
+	\centering
+	\includegraphics[width=1\textwidth]{img/use-case-diagram.png}
+	\caption{Use case diagram for our web application}
+	\label{fig:use-case}
+\end{figure}
 
@@
 
+\begin{figure}[h]
+	\centering
+	\includegraphics[width=1\textwidth]{img/ontology.jpg}
+	\caption{Visualization of the Ontology graph}
+	\label{fig:ontology}
+\end{figure}
+
 \section{Semantic considerations}
@@
 Here is our vocabulary (Figure \ref{fig:ontology})
-
-\begin{figure}[h]
-	\centering
-	\includegraphics[width=1\textwidth]{img/ontology.jpg}
-	\caption{Visualization of the Ontology graph}
-	\label{fig:ontology}
-\end{figure}
 

### 2016-04-07 milestone1/paper/paper.tex
Added files via upload

--- 2016-04-07 milestone1/paper/paper.tex
@@
 \usepackage{listings}
+\usepackage{multicol}
 \lstset{language=SQL,morekeywords={PREFIX,java,rdf,rdfs,url}}
@@
 
-\subsection{Theaters Dataset}
-% TODO describe theaters dataset (fields, contained data, semantics)
-The theaters dataset contains the following fields:
+\subsection{Theaters, Museums and Galleries Dataset}
+The theaters and museums dataset contains the same features according to the JSON we used:
 
 \begin{center}
-	\begin{tabular}{| c | c | c | c | c | c | c | c | c | c | c | c | c | c | c | c | c | c | c | c | c | c | c | c | c |}
-		\hline
-		\textbf{Trcid} & \textbf{Title} & \textbf{Shortdescription} & \textbf{Longdescription} & \textbf{Calendarsummary} & \textbf{TitleEN} & \textbf{ShortdescriptionEN} & \textbf{LongdescriptionEN} & \textbf{CalendarsummaryEN } & \textbf{Types} & \textbf{Ids} & \textbf{Locatienaam} & \textbf{City} & \textbf{Adres} & \textbf{Zipcode} & \textbf{Latitude } & \textbf{Latitude} & \textbf{Urls} & \textbf{Media} & \textbf{Thumbnail} & \textbf{Datepattern\_startdate} & \textbf{Datepattern\_enddate} & \textbf{Singledates} & \textbf{Type1} & \textbf{Lastupdated} \\ \hline
-
-		\hline
-	\end{tabular}
+	\textbf{\emph{Features}}
+	\setlength{\columnsep}{6em}
+\begin{multicols}{3}
+	\begin{enumerate}
+		\item \textbf{Trcid}
+		\item \textbf{Title}
+		\item \textbf{Shortdescription}
+		\item \textbf{Longdescription}
+		\item \textbf{Calendarsummary}
+		\item \textbf{TitleEN}
+		\item \textbf{ShortdescriptionEN }
+		\item \textbf{LongdescriptionEN  }
+		\item \textbf{CalendarsummaryEN       }
+		\item \textbf{Types} 
+		\item \textbf{Ids}
+		\item \textbf{Locatienaam}
+		\item \textbf{City}
+		\item \textbf{Adres}
+		\item \textbf{Zipcode}
+		\item \textbf{Latitude}
+		\item \textbf{Longitude}
+		\item \textbf{Urls}
+		\item \textbf{Media}
+		\item \textbf{Thumbnail}
+		\item \textbf{Datepattern\_startdate}
+		\item \textbf{Datepattern\_enddate}
+		\item \textbf{Singledates}
+		\item \textbf{Type1}
+		\item \textbf{Lastupdated}			
+		\end{enumerate}
+\end{multicols}
 \end{center}
 
-\subsection{Museums and Galleries Dataset}
-% TODO describe museums and galleries dataset
-
 \subsection{Handicap's Parking Slots Dataset}
-% TODO describe this dataset
+\begin{center}
+	\textbf{\emph{Features}}
+	\setlength{\columnsep}{4em}
+	\begin{multicols}{2}
+		\begin{enumerate}
+			\item \textbf{Adres}
+			\item \textbf{Location}
+			\item \textbf{Aantal}
+			\item \textbf{Onderbord}
+			\item \textbf{Stadsdeel}	
+			\item \textbf{Locatie-info}				
+		\end{enumerate}
+	\end{multicols}
+\end{center}
 

### 2016-04-07 milestone1/paper/paper.tex
Added files via upload

@@
 \subsection{Theaters, Museums and Galleries Dataset}
-The theaters and museums dataset contains the same features according to the JSON we used:
+The theaters and museums dataset contains the main features according to the JSON we used:
 
@@
 	\textbf{\emph{Features}}
-	\setlength{\columnsep}{6em}
-\begin{multicols}{3}
+\begin{multicols}{2}
 	\begin{enumerate}
@@
 		\item \textbf{Title}
-		\item \textbf{Shortdescription}
-		\item \textbf{Longdescription}
-		\item \textbf{Calendarsummary}
-		\item \textbf{TitleEN}
-		\item \textbf{ShortdescriptionEN }
-		\item \textbf{LongdescriptionEN  }
-		\item \textbf{CalendarsummaryEN       }
-		\item \textbf{Types} 
-		\item \textbf{Ids}
-		\item \textbf{Locatienaam}
-		\item \textbf{City}
-		\item \textbf{Adres}
-		\item \textbf{Zipcode}
-		\item \textbf{Latitude}
-		\item \textbf{Longitude}
-		\item \textbf{Urls}
-		\item \textbf{Media}
-		\item \textbf{Thumbnail}
-		\item \textbf{Datepattern\_startdate}
-		\item \textbf{Datepattern\_enddate}
-		\item \textbf{Singledates}
-		\item \textbf{Type1}
+		\item \textbf{Details *}
+		\item \textbf{Types *}
+		\item \textbf{Location *}
+		\item \textbf{Urls *}
+		\item \textbf{Media *}
+		\item \textbf{Dates}
 		\item \textbf{Lastupdated}
+		\item \textbf{Eigenschappen *} 
 		\end{enumerate}
@@
 \end{center}
+
+The main features (*) in the JSON format that contain sub-features.
+\renewcommand{\labelitemi}{$\bullet$}
+\renewcommand{\labelitemii}{$\cdot$}
+\renewcommand{\labelitemiii}{$\diamond$}
+\renewcommand{\labelitemiv}{$\ast$}
+\begin{multicols}{2}
+	\begin{itemize}
+		\item \textit{Details}\itemsep2pt
+		\begin{itemize}\itemsep1pt
+			\item language
+			\item title
+			\item calendarsummary
+			\item shortdescription
+			\item longdescription
+		\end{itemize}
+		\item \textit{Types}
+		\begin{itemize}\itemsep1pt
+			\item type
+			\item catid
+		\end{itemize}
+		\item \textit{Location}
+		\begin{itemize}
+			\item name
+			\item city
+			\item address
+			\item zipcode
+			\item latitude
+			\item longitude
+		\end{itemize}
+		\item \textit{Media}
+		\begin{itemize}
+			\item url
+			\item main
+		\end{itemize}
+		\item \textit{Eigenschappen}
+		\begin{itemize}
+			\item Catid
+			\item Value
+			\item CategoryArea
+			\item Category
+		\end{itemize}
+	\end{itemize}
+\end{multicols}
 

### 2016-04-07 milestone1/app/server.py
started web app skeleton [mls1]

@@ -1,0 +1,45 @@
+#!/usr/bin/env python
+
+from flask import Flask, render_template, url_for, request, jsonify
+from flask.ext.assets import Environment, Bundle
+from SPARQLWrapper import SPARQLWrapper, RDF, JSON
+import requests
+
+
+# setup app
+app = Flask(__name__)
+assets = Environment(app)
+
+# setup frontend code compilers
+coffee = Bundle('coffee/**/*', 'coffee/main.coffee',
+            filters='coffeescript')
+js = Bundle('components/jquery/dist/jquery.js',
+            'components/angular/angular.js',
+            'components/angular-bootstrap/ui-bootstrap.js',
+            'components/angular-bootstrap/ui-bootstrap-tpls.js',
+            'components/angular-ui-router/release/angular-ui-router.js',
+            filters='jsmin')
+js_all = Bundle(js, coffee,
+            filters='jsmin' if app.debug else None,
+            output='gen/client.js')
+assets.register('js_all', js_all)
+
+less = Bundle('less/style.less',
+            filters='less',
+            output='gen/style.css')
+css_all = Bundle(less, filters='cssmin' if app.debug else None, output='gen/style.css')
+assets.register('styles', css_all)
+
+
+REPOSITORY = 'http://stardog.krw.d2s.labs.vu.nl/group6'
+
+
+@app.route('/')
+def home():
+    app.logger.debug('You arrived at ' + url_for('home'))
+    return render_template('index.html')
+
+
+if __name__ == '__main__':
+    app.debug = True
+    app.run()

### 2016-04-07 milestone1/paper/paper.tex
building knowledge section

@@
 \usepackage{multicol}
+\usepackage{hyperref}
 \lstset{language=SQL,morekeywords={PREFIX,java,rdf,rdfs,url}}
@@
 \begin{abstract}
-The abstract should summarize the contents of the paper and should
-contain at least 70 and at most 150 words. It should be written using the
-\emph{abstract} environment.
+	%TODO update before submitting
+	This project realizes the integration of three different datasets related to the city of Amsterdam.
+It aims to provide support for handicap people who attend events in crowded or unknown neighborhoods.
+	We create an RDF database, using the OWL ontology, from public JSON files in order to model the data integration.
+We query such database in order to meet the needs of the proposed potential users.
+Finally, a simple web application was created to serve as front end for the functionality of the project.
+% should contain at least 70 and at most 150 words. It should be written using the \emph{abstract} environment.
 \end{abstract}
@@
 As stated in the introduction, the integration of venues and parking spot locations may bring benefits to attendees.
-Our application will provide a convenient and time-saving option for attendees to find parking spots.
-Furthermore, by using our application it is guaranteed that the best parking spot will be suggested %TODO not sure about this though ...
+Our application provides with a convenient and time-saving option for attendees to find parking spots.
+Furthermore, by using our application it is guaranteed that the best parking spot will be suggested, and enough options will be provided in case best matches are not available for parking at the moment of consultation.
 
-Hereby we provide three concrete use-cases where our application's benefits are to be maximized.
+Hereby we provide three concrete use-cases, by describing three different personas, where our application's benefits are to be maximized.
+A general use case diagram is shown in Figure \ref{fig:use-case}.
 
@@
 	% Event manager
-	\item Mary is an event organizer who wants to host an exhibition in a Museum next month.
+	\item Mary is an event organizer who wants to host an exhibition in a museum next month.
 She is looking for an accessible venue so she would like to see the distribution of parking spots around the main galleries in Amsterdam.
@@
 \end{enumerate}
+
+\begin{figure}[ht]
+	\centering
+	\includegraphics[width=1\textwidth]{img/use-case-diagram.png}
+	\caption{Use case diagram showing how potential users can use the application created in this project.}
+	\label{fig:use-case}
+\end{figure}
 
@@
 Also describe other datasets that you might want to integrate, and even data that still needs to be found, or even created.
-We decided to integrate the Gemeente's open data about theater events, museums and galleries and handicap's parking slots.
+In order to meet the needs in the above use cases we decided to integrate the Gemeente's open data about theaters, museums and galleries events along with the handicap's parking slots data.
 Those datasets are available in CSV or JSON formats.
@@
 \subsection{Theaters, Museums and Galleries Dataset}
-The theaters and museums dataset contains the main features according to the JSON we used:
+The Theaters and the Museums and Galleries datasets contain information about events happening in these types of venues. The datasets integrate easily since the both share the following main features:
 
@@
 
-The main features (*) in the JSON format that contain sub-features.
+Some of the main features (as shown by *) in the JSON format contain sub-features with more specific information. Those are:
+
 \renewcommand{\labelitemi}{$\bullet$}
@@
 \subsection{Handicap's Parking Slots Dataset}
+The Handicap's Parking Slots dataset, as its name states, contains information about the location of parking slots reserved for handicap people, around the city of Amsterdam.
+Each parking slot is described by following main features:
+
 \begin{center}
@@
 You might wish to add subsections discussing conceptual and technical problems in this process.
+In order to model the data properly we created a vocabulary which describes the classes and properties of the application ontology.
+We combined self defined ontologies with external ontologies such as dbpedia and geolocation.
+%TODO add citations to these
+
+A diagram showing for the modeled vocabulary is shown in Figure \ref{fig:vocabulary}
+
+\begin{figure}[ht]
+	\centering
+	\includegraphics[width=1\textwidth]{img/vocab-graph.jpg}
+	\caption{Visualization of the Ontology graph}
+	\label{fig:vocabulary}
+\end{figure}
+
+To populate the database with instances, the JSON files were read and transformed into RDF triples using a python script.
+The database is stored in \href{http://stardog.krw.d2s.labs.vu.nl/#/databases/group6}{this} Stardog server
+
+We created three named graphs: \href{http://data.krw.d2s.labs.vu.nl/doc/group6/findaslot/resource/findaslot/theaters}{Theaters}, \href{http://data.krw.d2s.labs.vu.nl/doc/group6/findaslot/resource/findaslot/museums}{Museums} and \href{http://data.krw.d2s.labs.vu.nl/doc/group6/findaslot/resource/findaslot/parking-slots}{Parking slots}.
 
@@
 Given the problem and use-case you have in mind, how do the examples of entailment contribute to a solution?
-Here is our vocabulary (Figure \ref{fig:ontology})
-
-\begin{figure}[h]
-	\centering
-	\includegraphics[width=1\textwidth]{img/ontology.jpg}
-	\caption{Visualization of the Ontology graph}
-	\label{fig:ontology}
-\end{figure}
+Event is linked to a venue. Venue and parking spots are linked to locations
+John knows the venue
+Peter knows the event
 
@@
 bind(?lo2 - ?lo1 as ?l) .
-bind(math:acos(math:sin(?la2)*math:sin(?la1) + math:cos(?la1)*math:cos(?la1)*math:cos(?l)) * xsd:double(6371000) as ?dist) .
+bind(math:acos(math:sin(?la2)*math:sin(?la1) 
++ math:cos(?la1)*math:cos(?la1)*math:cos(?l)) * xsd:double(6371000) as ?dist) .
 }

### 2016-04-08 milestone1/app/server.py
show venues in web app [mls1]

@@ -1,14 +1,15 @@
 #!/usr/bin/env python
 
-from flask import Flask, render_template, url_for, request, jsonify
+import json
+from flask import Flask, render_template, url_for, request, jsonify, abort
 from flask.ext.assets import Environment, Bundle
-from SPARQLWrapper import SPARQLWrapper, RDF, JSON
-import requests
+from services.sparql import SPARQL
 
 
 # setup app
 app = Flask(__name__)
 assets = Environment(app)
+sparql = SPARQL(app)
 
 # setup frontend code compilers
 coffee = Bundle('coffee/**/*', 'coffee/main.coffee',
@@ -31,13 +32,19 @@ css_all = Bundle(less, filters='cssmin' if app.debug else None, output='gen/styl
 assets.register('styles', css_all)
 
 
-REPOSITORY = 'http://stardog.krw.d2s.labs.vu.nl/group6'
-
-
 @app.route('/')
 def home():
     app.logger.debug('You arrived at ' + url_for('home'))
     return render_template('index.html')
+
+
+@app.route('/venues', methods=['GET'])
+def venues():
+    venues = sparql.venues()
+    if venues:
+        return jsonify({ 'data': venues})
+    else:
+        abort(500)
 
 
 if __name__ == '__main__':

### 2016-04-08 milestone1/app/services/sparql.py

@@ -1,0 +1,63 @@
+from SPARQLWrapper import SPARQLWrapper, RDF, JSON
+import requests
+
+
+class SPARQL(object):
+    def __init__(self, app):
+        super(SPARQL, self).__init__()
+        self._app = app
+        self.REPOSITORY = 'http://stardog.krw.d2s.labs.vu.nl/group6'
+        self._sparql = SPARQLWrapper(self.REPOSITORY + '/query')
+
+        self._sparql.addParameter('reasoning','true')
+
+    def _query(self, query, format='JSON'):
+        self._sparql.setQuery(query)
+        self._app.logger.debug('Running SPARQL query ' + query)
+
+        if format == 'RDF':
+            self._sparql.setReturnFormat(RDF)
+        else:
+            self._sparql.setReturnFormat(JSON)
+            self._sparql.addParameter('Accept', 'application/sparql-results+json')
+
+        try:
+            response = self._sparql.query().convert()
+            self._app.logger.debug('Got response!')
+            # self._app.logger.debug(response)
+
+            if format == 'RDF':
+                return response.serialize(format='turtle')
+            else:
+                return response
+        except Exception as e:
+            self._app.logger.error('Something went wrong')
+            print e
+            return None
+
+    def venues(self, format='JSON'):
+        query = """
+        prefix rdf: <http://www.w3.org/1999/02/22-rdf-syntax-ns#>
+        prefix owl: <http://www.w3.org/2002/07/owl#>
+        prefix xsd: <http://www.w3.org/2001/XMLSchema#>
+        prefix rdfs: <http://www.w3.org/2000/01/rdf-schema#>
+
+        prefix : <http://data.krw.d2s.labs.vu.nl/group6/findaslot/vocab/>
+        prefix dbo: <http://dbpedia.org/ontology/>
+
+        select distinct ?evenue ?venue
+        where { 
+            ?evenue a :Venue .
+            ?evenue rdfs:label ?venue .
+        }
+        """
+        response = self._query(query, format)
+        if format == 'JSON':
+            bindings = response['results']['bindings']
+            return map(lambda binding: {
+                'name': binding['venue']['value'],
+                'href': binding['evenue']['value']
+            }, bindings)
+        else:
+            return response
+

### 2016-04-08 milestone1/app/server.py
interface frontend with datastore [mls1]

@@ -12,7 +12,7 @@ assets = Environment(app)
 sparql = SPARQL(app)
 
 # setup frontend code compilers
-coffee = Bundle('coffee/**/*', 'coffee/main.coffee',
+coffee = Bundle('coffee/app.coffee', 'coffee/**/*.coffee',
             filters='coffeescript')
 js = Bundle('components/jquery/dist/jquery.js',
             'components/angular/angular.js',

### 2016-04-08 milestone1/app/server.py
loooots of stuff [mls1]

@@ -1,6 +1,5 @@
 #!/usr/bin/env python
 
-import json
 from flask import Flask, render_template, url_for, request, jsonify, abort
 from flask.ext.assets import Environment, Bundle
 from services.sparql import SPARQL
@@ -40,9 +39,13 @@ def home():
 
 @app.route('/venues', methods=['GET'])
 def venues():
-    venues = sparql.venues()
-    if venues:
-        return jsonify({ 'data': venues})
+    name = request.args.get('name')
+    if name:
+        data = sparql.venue(name)
+    else:
+        data = sparql.venues()
+    if data:
+        return jsonify({ 'data': data})
     else:
         abort(500)
 

### 2016-04-08 milestone1/app/services/sparql.py

@@ -2,7 +2,20 @@ from SPARQLWrapper import SPARQLWrapper, RDF, JSON
 import requests
 
 
+PREFIXES = """
+prefix rdf: <http://www.w3.org/1999/02/22-rdf-syntax-ns#>
+prefix owl: <http://www.w3.org/2002/07/owl#>
+prefix xsd: <http://www.w3.org/2001/XMLSchema#>
+prefix rdfs: <http://www.w3.org/2000/01/rdf-schema#>
+
+prefix : <http://data.krw.d2s.labs.vu.nl/group6/findaslot/vocab/>
+prefix data: <http://data.krw.d2s.labs.vu.nl/group6/findaslot/resource/>
+prefix dbo: <http://dbpedia.org/ontology/>
+"""
+
+
 class SPARQL(object):
+
     def __init__(self, app):
         super(SPARQL, self).__init__()
         self._app = app
@@ -10,6 +23,7 @@ class SPARQL(object):
         self._sparql = SPARQLWrapper(self.REPOSITORY + '/query')
 
         self._sparql.addParameter('reasoning','true')
+
 
     def _query(self, query, format='JSON'):
         self._sparql.setQuery(query)
@@ -26,38 +40,85 @@ class SPARQL(object):
             self._app.logger.debug('Got response!')
             # self._app.logger.debug(response)
 
-            if format == 'RDF':
-                return response.serialize(format='turtle')
-            else:
-                return response
+            return response
         except Exception as e:
             self._app.logger.error('Something went wrong')
             print e
             return None
 
-    def venues(self, format='JSON'):
-        query = """
-        prefix rdf: <http://www.w3.org/1999/02/22-rdf-syntax-ns#>
-        prefix owl: <http://www.w3.org/2002/07/owl#>
-        prefix xsd: <http://www.w3.org/2001/XMLSchema#>
-        prefix rdfs: <http://www.w3.org/2000/01/rdf-schema#>
 
-        prefix : <http://data.krw.d2s.labs.vu.nl/group6/findaslot/vocab/>
-        prefix dbo: <http://dbpedia.org/ontology/>
-
-        select distinct ?evenue ?venue
-        where { 
-            ?evenue a :Venue .
-            ?evenue rdfs:label ?venue .
-        }
-        """
-        response = self._query(query, format)
+    def _deserialize_response(self, response, props=None, format='JSON'):
         if format == 'JSON':
-            bindings = response['results']['bindings']
-            return map(lambda binding: {
-                'name': binding['venue']['value'],
[…]

### 2016-04-08 milestone1/app/services/sparql.py
limit query & change table [mls1]

@@ -85,11 +85,12 @@ class SPARQL(object):
         prefix geo: <http://www.w3.org/2003/01/geo/wgs84_pos#>
         prefix math: <http://www.w3.org/2005/xpath-functions/math#>
 
-        select distinct ?venue ?eslot ?saddr ?scity ?slat ?slong ?eaddr ?ecity ?elat ?elong ?dist
+        select distinct ?venue ?eslot ?saddr ?scity ?slat ?slong ?squan ?eaddr ?ecity ?elat ?elong ?dist
         where {{
           ?eslot a :ParkingSlot ;
             rdfs:label ?slot ;
-            dbo:location ?slocation .
+            dbo:location ?slocation ;
+            :quantity ?squan .
           ?slocation geo:lat ?slat ;
             geo:long ?slong ;
             dbo:city ?scity ;
@@ -112,13 +113,12 @@ class SPARQL(object):
           bind(math:acos(math:sin(?la2)*math:sin(?la1) + math:cos(?la1)*math:cos(?la1)*math:cos(?l)) * xsd:double(6371000) as ?dist) .
         }}
         order by ?dist
-        limit 100
+        limit 20
         """.format(PREFIXES, name)
 
         response = self._query(query, format=format)
-        print response['results']['bindings']
         props = [('venue', 'venue'), ('slat', 'slot_latitude'), ('scity', 'slot_city'),
             ('slong', 'slot_longitude'), ('saddr', 'slot_address'), ('eaddr', 'venue_address'),
             ('elat', 'venue_latitude'), ('elong', 'venue_longitude'),
-            ('ecity', 'venue_city'), ('dist', 'distance')]
+            ('ecity', 'venue_city'), ('squan', 'slot_quantity'), ('dist', 'distance')]
         return self._deserialize_response(response, props=props, format=format)

### 2016-04-08 milestone1/paper/paper.tex
queries and vocab description

@@
 Specifically, for handicap people this is an issue that should not be overlooked since they require more time to commute.
-Hence, having knowledge about close parking spots is specially useful to them.
+Hence, having knowledge about close parking slots is specially useful to them.
 
@@
 
-In this project we create a web application that serves as a unique point for finding locations of venues and parking spots related to an event.
+In this project we create a web application that serves as a unique point for finding locations of venues and parking slots related to an event.
 We decided to work with Museum Galleries and Theaters to keep the scope of the project manageable.
@@
 Next, we describe the datasets and continue to explain the data management process to abstract the knowledge from those datasets.
-Then, we explain the semantics in our data set and provide examples of the queries we used to build the application.
+Then, we explain the semantics in our dataset and provide examples of the queries we used to build the application.
 We finalize with a demo of the application and a discussion of the work done.
@@
 
-As stated in the introduction, the integration of venues and parking spot locations may bring benefits to attendees.
-Our application provides with a convenient and time-saving option for attendees to find parking spots.
-Furthermore, by using our application it is guaranteed that the best parking spot will be suggested, and enough options will be provided in case best matches are not available for parking at the moment of consultation.
+As stated in the introduction, the integration of venues and parking slot locations may bring benefits to attendees.
+Our application provides with a convenient and time-saving option for attendees to find parking slots.
+Furthermore, by using our application it is guaranteed that the best parking slot will be suggested, and enough options will be provided in case best matches are not available for parking at the moment of consultation.
 
@@
 \\
-	The day before the show, John uses our application to find such parking spots and heads to the show confidently. 
+	The day before the show, John uses our application to find such parking slots and heads to the show confidently. 
 	% Quick search once in the theater (on the fly)
-	\item Peter broke his leg last month and his friends, as an attempt to cheer him up, invited him to come to a comedy show.
-He is quite late and is rushing to find the closest parking spots.
-He quickly browses our application and finds an area with several parking spots.
-He drives in that direction hoping to find an available spot.
+	\item Peter broke his leg last month and his friends, as an attempt to cheer him up, invited him to come to a comedy show at the Comedy Cafe.
+He is quite late and is rushing to find the closest parking slots.
+He quickly browses our application and finds an area with several parking slots.
+He drives in that direction hoping to find an available slot.
 	% Event manager
 	\item Mary is an event organizer who wants to host an exhibition in a museum next month.
-She is looking for an accessible venue so she would like to see the distribution of parking spots around the main galleries in Amsterdam.
+She is looking for an accessible venue so she would like to see the distribution of parking slots around the main galleries in Amsterdam.
 She has a list of five places in mind and uses our application to explore and choose the best venue.
@@
 We combined self defined ontologies with external ontologies such as dbpedia and geolocation.
-%TODO add citations to these
+A diagram showing for the modeled vocabulary is shown in Figure \ref{fig:vocabulary}.
 
-A diagram showing for the modeled vocabulary is shown in Figure \ref{fig:vocabulary}
+We created four classes: Event, Venue, Parking Slot and Location, of which the first three were defined by us and the last one was defined as a subclass of dbepedia's Location class.
+The Theaters and Museums and Galleries datasets were turned into Events containing Venues and Locations, while the Parking Slots dataset turned into Parking Slots with Locations.
+As shown, the common factor integrating the data is the Location class.
 
-\begin{figure}[ht]
+\begin{figure}[h]
 	\centering
@@
 
-To populate the database with instances, the JSON files were read and transformed into RDF triples using a python script.
+To populate the database with instances, the JSON files were read and transformed into RDF triples using a python script. A sample instance is shown in Figure \ref{fig:instance}
+
+\begin{figure}[h]
+	\centering
+	\includegraphics[width=1\textwidth]{img/vocab-graph.jpg}
+	\caption{Visualization of the Ontology graph}
+	\label{fig:instance}
+\end{figure}
+
 The database is stored in \href{http://stardog.krw.d2s.labs.vu.nl/#/databases/group6}{this} Stardog server
@@
 Given the problem and use-case you have in mind, how do the examples of entailment contribute to a solution?
-Event is linked to a venue. Venue and parking spots are linked to locations
+Event is linked to a venue. Venue and parking slots are linked to locations
 John knows the venue

### 2016-04-09 milestone1/paper/paper.tex
Entailment part

@@
 \usepackage{url}
-\usepackage{graphicx}
-\usepackage{amssymb}	
+\usepackage{graphicx, colortbl}
+\usepackage{amsmath,amssymb}	
 \usepackage{listings}
@@
 	\centering
-	\includegraphics[width=1\textwidth]{img/use-case-diagram.png}
+	\includegraphics[width=.7\textwidth]{img/use-case-diagram.png}
 	\caption{Use case diagram showing how potential users can use the application created in this project.}
@@
 \subsection{Theaters, Museums and Galleries Dataset}
-The Theaters and the Museums and Galleries datasets contain information about events happening in these types of venues. The datasets integrate easily since the both share the following main features:
+The Theaters and the Museums and Galleries datasets contain information about events happening in these types of venues, as well as the details of the location of the venues.
+The datasets are comparable since the both share the following main features:
 
@@
 We created four classes: Event, Venue, Parking Slot and Location, of which the first three were defined by us and the last one was defined as a subclass of dbepedia's Location class.
-The Theaters and Museums and Galleries datasets were turned into Events containing Venues and Locations, while the Parking Slots dataset turned into Parking Slots with Locations.
+The Theaters and Museums and Galleries datasets were turned into Events linked to Venues, and Venues linked Locations, while the Parking Slots dataset turned into Parking Slots linked to Locations.
 As shown, the common factor integrating the data is the Location class.
@@
 	\centering
-	\includegraphics[width=1\textwidth]{img/vocab-graph.jpg}
+	\includegraphics[width=.7\textwidth]{img/vocab-graph.jpg}
 	\caption{Visualization of the Ontology graph}
@@
 
-To populate the database with instances, the JSON files were read and transformed into RDF triples using a python script. A sample instance is shown in Figure \ref{fig:instance}
+To populate the database with instances, the JSON files were read and transformed into RDF triples using a python script. A sample instance is shown in Figure \ref{fig:instance}.
 
@@
 	\centering
-	\includegraphics[width=1\textwidth]{img/vocab-graph.jpg}
-	\caption{Visualization of the Ontology graph}
+	\includegraphics[width=1\textwidth]{img/knowledge-graph-example.png}
+	\caption{Sample instance for a Venue "Galerie Sous-Terre" with specific property Location}
 	\label{fig:instance}
@@
 
-The database is stored in \href{http://stardog.krw.d2s.labs.vu.nl/#/databases/group6}{this} Stardog server
+The database is stored in \href{http://stardog.krw.d2s.labs.vu.nl/#/databases/group6}{this} Stardog server and contains around 17 000 triples.
 
-We created three named graphs: \href{http://data.krw.d2s.labs.vu.nl/doc/group6/findaslot/resource/findaslot/theaters}{Theaters}, \href{http://data.krw.d2s.labs.vu.nl/doc/group6/findaslot/resource/findaslot/museums}{Museums} and \href{http://data.krw.d2s.labs.vu.nl/doc/group6/findaslot/resource/findaslot/parking-slots}{Parking slots}.
+%We created three named graphs: \href{http://data.krw.d2s.labs.vu.nl/doc/group6/findaslot/resource/findaslot/theaters}{Theaters}, \href{http://data.krw.d2s.labs.vu.nl/doc/group6/findaslot/resource/findaslot/museums}{Museums} and \href{http://data.krw.d2s.labs.vu.nl/doc/group6/findaslot/resource/findaslot/parking-slots}{Parking slots}.
 
@@
 Given the problem and use-case you have in mind, how do the examples of entailment contribute to a solution?
-Event is linked to a venue. Venue and parking slots are linked to locations
-John knows the venue
-Peter knows the event
+In our use cases, the main goal if for a user to find a parking slots based on the event they want to attend.
+To do so, we use the common property location.However, the location of an event is not explicit, so we need to infer it.
+
+Hereby we only consider the subgraph containing Events, Venues and Locations to illustrate how entailment enriches our knowledge.
 
@@
 % Give a small graph G' which is entailed by your subgraph G. Feel free to use the same G' that you want to use in your SPARQL query later. Explain why G' is entailed (this is really simple).
+We asserted that Events take place in a Venue, and we also asserted that Venues have a Location. Thus it follows that Events happen in a Location.
+
+The logical entailment rules are shown in the next argument:
+
+\begin{center}
+	\begin{tabular}{c@{\,}l@{}} 
+  	& \textit{:Event 		:venue 				?$o_1$} \\
+  	& \textit{?$o_1$ 		rdfs:type 			:Venue} \\   
+  	& \textit{:Venue 		:location 			?$o_2$} \\ 
+  	& \textit{?$o_2$ 		rdfs:type 			:Location} \\ 
+  	& \textit{:Location		rdfs:subClassOf 	dbo:Location} \\
+  	  	\arrayrulecolor{blue} \cline{2-2}
+  	$\therefore$         
+  	& \textit{:Event 		:location 				?$o_2$} \\
+  	\end{tabular}
+\end{center}
 
@@
 % Give a SPARQL query that provides different answers on the basis of interpreting the knowledge graph with an RDF entailment regime as opposed to an RDFS regime, and explain why you get different answers.
+The RDF schema would not be sufficient for our application to provide any results when a user knows the Event name but not the Venue.
 
-\begin{lstlisting}[captionpos=b, caption=SPARQL query, label=lst:sparql,
+RDFS provides us with a way to link Events and Locations.
+Thus, we can query Parking Slots that are related to that specific Location.
+We do this by retrieving all Parking Slots Locations and doing a geometrical comparison to the required Event Location.
+The query is shown in the Appendices.
+
+% What is the relation between this fact in terms of model checking and reasoning?
+
+% Investigate and discuss whether there are interesting cases of entailment in your own data.
+
+\section{Discussion}
+% Here you summarize the preceding sections, describe the lessons learnt and discuss future work.
+% Present a screenshot of a mock-up or working (preferred!) version of your system an describe what it does.
+% Argue why the preceding sections show that your solution (partially) solves the problem you introduced in the introduction.
+In this work we successfully transformed public data from the Amsterdam Municipality into and RDF schema.
+Furthermore, we created a model that enables us to integrate two different datasets: Theater and Museum and Galleries events, and parking Slots.
+Thanks to the power of RDFS we entail implicit knowledge about database, which allows us to query it and obtain useful information for the use cases explained in Section 2.
+
+Our solution is capable of retrieving Parking Slots nearby a location.
+It saves time to the user since he does not need to know the location of the Venue and can go directly from knowing the event name to a convenient spot to park his car.
+
+The web application may be improved by provided extended support. New queries may be added. %TODO finish this
+
+\bibliographystyle{plain}
+\bibliography{bibliography}
+
+\newpage
+\appendix
+\section{Prefixes used}
+
+$rdf: <http://www.w3.org/1999/02/22-rdf-syntax-ns>$ \\
+$owl: <http://www.w3.org/2002/07/owl>$ \\
+$xsd: <http://www.w3.org/2001/XMLSchema>$ \\
+$rdfs: <http://www.w3.org/2000/01/rdf-schema>$ \\
+$: <http://data.krw.d2s.labs.vu.nl/group6/findaslot/vocab/>$ \\
+$data: <http://data.krw.d2s.labs.vu.nl/group6/findaslot/resource/>$ \\
+$geo: <http://www.w3.org/2003/01/geo/wgs84\_pos>$ \\
+$math: <http://www.w3.org/2005/xpath-functions/math>$ \\
+$dbo: <http://dbpedia.org/ontology/>$
+
+\section{SQL Queries}
+
+\begin{lstlisting}[captionpos=b, caption=SPARQL query for getting parking spots close to Podium Mozaiek (sorted by distance), label=lst:sparql,
 basicstyle=\ttfamily,frame=bt]
-prefix rdf: <http://www.w3.org/1999/02/22-rdf-syntax-ns#>
-prefix owl: <http://www.w3.org/2002/07/owl#>
-prefix xsd: <http://www.w3.org/2001/XMLSchema#>
-prefix rdfs: <http://www.w3.org/2000/01/rdf-schema#>
-
-prefix : <http://data.krw.d2s.labs.vu.nl/group6/findaslot/vocab/>
-prefix data: <http://data.krw.d2s.labs.vu.nl/group6/findaslot/resource/>
-prefix geo: <http://www.w3.org/2003/01/geo/wgs84_pos#>
-prefix math: <http://www.w3.org/2005/xpath-functions/math#>
-prefix dbo: <http://dbpedia.org/ontology/>
 
@@
 bind(math:acos(math:sin(?la2)*math:sin(?la1) 
-+ math:cos(?la1)*math:cos(?la1)*math:cos(?l)) * xsd:double(6371000) as ?dist) .
++ math:cos(?la1)*math:cos(?la1)*math:cos(?l)) 
+* xsd:double(6371000) as ?dist) .
 }
@@
 
-% What is the relation between this fact in terms of model checking and reasoning?
-
-% Investigate and discuss whether there are interesting cases of entailment in your own data.
-
-\section{Discussion}
-% Here you summarize the preceding sections, describe the lessons learnt and discuss future work.
-% Present a screenshot of a mock-up or working (preferred!) version of your system an describe what it does.
-% Argue why the preceding sections show that your solution (partially) solves the problem you introduced in the introduction.
-
-\bibliographystyle{plain}
-\bibliography{bibliography}
-
 \end{document}

### 2016-04-09 milestone1/paper/paper.tex
added app screenshots [mls1]
added rdfs entailment figure [mls1]

@@
 \usepackage{hyperref}
+\usepackage{caption, subcaption}
 \lstset{language=SQL,morekeywords={PREFIX,java,rdf,rdfs,url}}
@@
 
-The logical entailment rules are shown in the next argument:
+\begin{figure}[h]
+	\centering
+	\includegraphics[width=1\textwidth]{img/ontology-classes.png}
+	\caption{RDFS entailment for our ontology. The Protege convention is adopted
+	for symbols and colors: blue relations represent subclassing and yellow and
+	orange ones represent domain and range relations.}
+	\label{fig:rdfs-entailment}
+\end{figure}
+
+The logical entailment rules are shown in the next argument while a more
+complete picture is shown in Figure \ref{rig:rdfs-entailment}:
 
@@
 % Investigate and discuss whether there are interesting cases of entailment in your own data.
+
+\begin{figure}
+	\centering
+	\begin{subfigure}[b]{.4\textwidth}
+		\includegraphics[width=\textwidth]{img/app-venues.png}
+		\caption{Venues shown by the Web application.}
+		\label{fig:app-venues}
+	\end{subfigure}
+	\qquad
+	\begin{subfigure}[b]{.4\textwidth}
+		\includegraphics[width=\textwidth]{img/app-slots.png}
+		\caption{Parking slots associated with a venue.}
+		\label{fig:app-slots}
+	\end{subfigure}
+	\caption{Screenshots from the Web application.}
+	\label{fig:app}
+\end{figure}
 
@@
 
-\section{SQL Queries}
+\section{SPARQL Queries}
 

### 2016-04-09 milestone1/paper/paper.tex
added web app discussion [mls1]

@@
 
-The web application may be improved by provided extended support. New queries may be added. %TODO finish this
+The Web application may be improved by provided extended support. Screenshots of
+the application are shown in Figure \ref{fig:app}. First the user is presented with
+the list of venues (Figure \ref{fig:app-venues}). By clicking on a row of the table
+the user is presented with the contents of Figure \ref{fig:app-slots}. This page
+shows a list of 20 parking slots sorted by distance from the queried venue.
+
+We developed the queries based on geographical distance (using decimal latitude
+and longitude) using a mathematical formula. This may result in numerical errors
+and therefore wrong results. An immediate improvement of the system would be to
+use Stardog's support for geospatial queries. Then querying for geospatial
+relations like \texttt{geof:relate}, \texttt{geof:distance},
+\texttt{geof:within}, \texttt{geof:nearby} and
+\texttt{geof:area}\footnote{The \texttt{geof} namespace defines geospatial
+functions at the URL \url{http://www.opengis.net/def/function/geosparql/}}.
 

### 2016-04-09 milestone1/paper/paper.tex
Done

@@
 \begin{abstract}
-	%TODO update before submitting
 	This project realizes the integration of three different datasets related to the city of Amsterdam.
 It aims to provide support for handicap people who attend events in crowded or unknown neighborhoods.
-	We create an RDF database, using the OWL ontology, from public JSON files in order to model the data integration.
+	We create an RDF model, using the OWL ontology, in order to model the data integration, and generate a database from public JSON files.
 We query such database in order to meet the needs of the proposed potential users.
@@
 Has this (or something similar) been done before?
-%TODO read WHOLE section again and make it pretty
-Amsterdam is a busy city that offers a variety of events and a common problem when attending such events is that Parking Spots are often scarce.
-Specifically, for handicap people this is an issue that should not be overlooked since they require more time to commute.
+Amsterdam is a busy city that offers a variety of events and a common problem when attending such events is that parking spots are often scarce.
+Specifically, for handicap people this is an issue that should not be overlooked since they require more time to travel to and from events venues.
 Hence, having knowledge about close parking slots is specially useful to them.
@@
 However, acquiring this information is not straightforward.
-The location of venues is not associated with Parking Spot locations, and users usually have to find them themselves by means of maps or driving around.
+To the best of our knowledge, currently the location of venues is not associated with parking spot locations.
+Users usually have to find them themselves by means of maps, which may be confusing, or driving around, which is time consuming.
 Solving this problem would bring benefits to attendees.
-%TODO is this novel?
 
 In this project we create a web application that serves as a unique point for finding locations of venues and parking slots related to an event.
-We decided to work with Museum Galleries and Theaters to keep the scope of the project manageable.
-To do so we convert existing datasets to RDF format and query them to get the desired results.
+We decided to work with Museum Galleries and Theaters to keep the scope of the project manageable, but the knowledge model can be applied to other types of venues as well.
+To do the integration we convert existing datasets to RDF format and query them to get the desired results.
 
 In the following section we delve deeper into cases where our proposed solution could be applied.
-Next, we describe the datasets and continue to explain the data management process to abstract the knowledge from those datasets.
-Then, we explain the semantics in our dataset and provide examples of the queries we used to build the application.
-We finalize with a demo of the application and a discussion of the work done.
+Next, we describe the datasets and continue to explain the data management process to abstract knowledge from those datasets.
+Later on we explain the semantics in our dataset and provide examples of the queries we used to build the application.
+We finalize with screen shots of the working application and a discussion of the work done.
 
@@
 
-As stated in the introduction, the integration of venues and parking slot locations may bring benefits to attendees.
+As stated in the introduction, the integration of venues and parking slot locations may bring benefits to event attendees.
 Our application provides with a convenient and time-saving option for attendees to find parking slots.
@@
 	\item Peter broke his leg last month and his friends, as an attempt to cheer him up, invited him to come to a comedy show at the Comedy Cafe.
-He is quite late and is rushing to find the closest parking slots.
+He is quite late and he is rushing to find the closest parking slots.
 He quickly browses our application and finds an area with several parking slots.
@@
 	\centering
-	\includegraphics[width=.7\textwidth]{img/use-case-diagram.png}
-	\caption{Use case diagram showing how potential users can use the application created in this project.}
+	\includegraphics[width=.75\textwidth]{img/use-case-diagram.png}
+	\caption{Use case diagram showing potential uses of the application created in this project.}
 	\label{fig:use-case}
@@
 Also describe other datasets that you might want to integrate, and even data that still needs to be found, or even created.
-In order to meet the needs in the above use cases we decided to integrate the Gemeente's open data about theaters, museums and galleries events along with the handicap's parking slots data.
+In order to meet the needs in the above use cases we decided to integrate public data published by the Municipality of Amsterdam.
+The chosen datasets relate to theaters, museums and galleries events along with the handicap's parking slots data.
 Those datasets are available in CSV or JSON formats.
-We chose to convert from the JSON format because it is a more powerful representation than CSV and because JSON and RDF formats can be easily mapped one to another.
+We made decision to convert from the JSON format because it is a more powerful representation than CSV and because JSON and RDF formats can be easily mapped one to another.
 
@@
 In order to model the data properly we created a vocabulary which describes the classes and properties of the application ontology.
-We combined self defined ontologies with external ontologies such as dbpedia and geolocation.
+We combined self defined ontologies with external ontologies such as \texttt{dbepedia} \footnote{The \texttt{dbepedia} namespace is defined at \url{http://dbpedia.org/ontology/}} and \texttt{geo} \footnote{The \texttt{geo} namespace is defined at \url{http://www.w3.org/2003/01/geo/wgs84_pos}}.
 A diagram showing for the modeled vocabulary is shown in Figure \ref{fig:vocabulary}.
-
-We created four classes: Event, Venue, Parking Slot and Location, of which the first three were defined by us and the last one was defined as a subclass of dbepedia's Location class.
-The Theaters and Museums and Galleries datasets were turned into Events linked to Venues, and Venues linked Locations, while the Parking Slots dataset turned into Parking Slots linked to Locations.
-As shown, the common factor integrating the data is the Location class.
 
@@
 \end{figure}
+
+We created four classes: Event, Venue, Parking Slot and Location, of which the first three were defined by us and the last one was defined as a subclass of \texttt{dbepedia}'s Location class.
+The Theaters and Museums and Galleries datasets were turned into Events linked to Venues, and Venues linked Locations, while the Parking Slots dataset turned into Parking Slots linked to Locations.
+As shown, the common factor integrating the data is the Location class.
 
@@
 
-The database is stored in \href{http://stardog.krw.d2s.labs.vu.nl/#/databases/group6}{this} Stardog server and contains around 17 000 triples.
-
-%We created three named graphs: \href{http://data.krw.d2s.labs.vu.nl/doc/group6/findaslot/resource/findaslot/theaters}{Theaters}, \href{http://data.krw.d2s.labs.vu.nl/doc/group6/findaslot/resource/findaslot/museums}{Museums} and \href{http://data.krw.d2s.labs.vu.nl/doc/group6/findaslot/resource/findaslot/parking-slots}{Parking slots}.
+The database is stored in \href{http://stardog.krw.d2s.labs.vu.nl/#/databases/group6}{this} Stardog server and contains around 17 000 triples and three named graphs: \href{http://data.krw.d2s.labs.vu.nl/doc/group6/findaslot/resource/findaslot/theaters}{Theaters}, \href{http://data.krw.d2s.labs.vu.nl/doc/group6/findaslot/resource/findaslot/museums}{Museums} and \href{http://data.krw.d2s.labs.vu.nl/doc/group6/findaslot/resource/findaslot/parking-slots}{Parking slots}.
 
@@
 Given the problem and use-case you have in mind, how do the examples of entailment contribute to a solution?
-In our use cases, the main goal if for a user to find a parking slots based on the event they want to attend.
-To do so, we use the common property location.However, the location of an event is not explicit, so we need to infer it.
+In our use cases, the main goal for a user to find a parking slots based on the event they want to attend.
+To do so, we use the common property location.
+However, the location of an event is not explicit, so we need to infer it.
 
-Hereby we only consider the subgraph containing Events, Venues and Locations to illustrate how entailment enriches our knowledge.
+Hereby we only consider the subgraph $G$ containing Events, Venues and Locations to illustrate how the entailment of a graph $G'$ enriches our knowledge about the relations among the classes.
 
@@
 % Give a small graph G' which is entailed by your subgraph G. Feel free to use the same G' that you want to use in your SPARQL query later. Explain why G' is entailed (this is really simple).
-We asserted that Events take place in a Venue, and we also asserted that Venues have a Location. Thus it follows that Events happen in a Location.
+A complete picture of the RDFS semantics in our ontology is shown in Figure \ref{fig:rdfs-entailment}.
 
@@
 
-The logical entailment rules are shown in the next argument while a more
-complete picture is shown in Figure \ref{rig:rdfs-entailment}:
+From this picture we see two main entailment consequences.
+Firstly, that Location is a subclass of owl:Thing.
+Secondly, and most interestingly, there is a relation between Event and Location.
+We describe the latter in the following argument:
 
@@
 \end{center}
+
+In simple words, the above states that since we asserted that Events take place in a Venue, and we also asserted that Venues have a Location, thus it follows that Events happen in a Location.
+It is simple for us to see that the last statement is true and valuable in terms of building our application.
 
@@
 % Investigate and discuss whether there are interesting cases of entailment in your own data.
+
+\section{Discussion}
+% Here you summarize the preceding sections, describe the lessons learnt and discuss future work.
+% Present a screenshot of a mock-up or working (preferred!) version of your system an describe what it does.
+% Argue why the preceding sections show that your solution (partially) solves the problem you introduced in the introduction.
+In this work we successfully transformed public data from the Amsterdam Municipality into and RDF schema.
+Furthermore, we created a model that enables us to integrate two different datasets: Theater and Museum and Galleries events, and parking Slots.
+Thanks to the power of RDFS we entail implicit knowledge about database, which allows us to query it and obtain useful information for the use cases explained in Section 2.
+
+Our solution is capable of retrieving Parking Slots nearby a Venue.
+It saves time to the user since he/she does not need to know the location of the Venue and can go directly from knowing the event name to a convenient spot to park his/her car.
 
@@
 
-\section{Discussion}
-% Here you summarize the preceding sections, describe the lessons learnt and discuss future work.
-% Present a screenshot of a mock-up or working (preferred!) version of your system an describe what it does.
-% Argue why the preceding sections show that your solution (partially) solves the problem you introduced in the introduction.
-In this work we successfully transformed public data from the Amsterdam Municipality into and RDF schema.
-Furthermore, we created a model that enables us to integrate two different datasets: Theater and Museum and Galleries events, and parking Slots.
-Thanks to the power of RDFS we entail implicit knowledge about database, which allows us to query it and obtain useful information for the use cases explained in Section 2.
+Screen shots of the working application are shown in Figure \ref{fig:app}.
+First the user is presented with the list of venues (Figure \ref{fig:app-venues}).
+By clicking on a row of the table the user is presented with the contents of Figure \ref{fig:app-slots}.
+This page shows a list of 20 parking slots sorted by distance from the queried venue.
 
-Our solution is capable of retrieving Parking Slots nearby a location.
-It saves time to the user since he does not need to know the location of the Venue and can go directly from knowing the event name to a convenient spot to park his car.
-
-The Web application may be improved by provided extended support. Screenshots of
-the application are shown in Figure \ref{fig:app}. First the user is presented with
-the list of venues (Figure \ref{fig:app-venues}). By clicking on a row of the table
-the user is presented with the contents of Figure \ref{fig:app-slots}. This page
-shows a list of 20 parking slots sorted by distance from the queried venue.
-
-We developed the queries based on geographical distance (using decimal latitude
-and longitude) using a mathematical formula. This may result in numerical errors
-and therefore wrong results. An immediate improvement of the system would be to
+As a final thought for future work, we recognize the Web application may be improved to provide extended support.
+Other types of venues could be included, which can be done by transforming additional datasets, and more interesting queries could be done.
+For example, we developed the queries based on geographical distance (using decimal latitude and longitude) using a mathematical formula.
+This may result in numerical errors and therefore wrong results.
+An immediate improvement of the system would be to
 use Stardog's support for geospatial queries. Then querying for geospatial
@@
 \texttt{geof:within}, \texttt{geof:nearby} and
-\texttt{geof:area}\footnote{The \texttt{geof} namespace defines geospatial
+\texttt{geof:area} \footnote{The \texttt{geof} namespace defines geospatial
 functions at the URL \url{http://www.opengis.net/def/function/geosparql/}}.
-
-\bibliographystyle{plain}
-\bibliography{bibliography}
 
@@
 \appendix
-\section{Prefixes used}
+\section{Prefixes and namespaces}
+\begin{lstlisting}[captionpos=b, caption=Prefixes for the namespaces used in this project, label=lst:sparql,
+basicstyle=\ttfamily\small,frame=bt]
 
-$rdf: <http://www.w3.org/1999/02/22-rdf-syntax-ns>$ \\
-$owl: <http://www.w3.org/2002/07/owl>$ \\
-$xsd: <http://www.w3.org/2001/XMLSchema>$ \\
-$rdfs: <http://www.w3.org/2000/01/rdf-schema>$ \\
-$: <http://data.krw.d2s.labs.vu.nl/group6/findaslot/vocab/>$ \\
-$data: <http://data.krw.d2s.labs.vu.nl/group6/findaslot/resource/>$ \\
-$geo: <http://www.w3.org/2003/01/geo/wgs84\_pos>$ \\
-$math: <http://www.w3.org/2005/xpath-functions/math>$ \\
-$dbo: <http://dbpedia.org/ontology/>$
+rdf: <http://www.w3.org/1999/02/22-rdf-syntax-ns#>
+owl: <http://www.w3.org/2002/07/owl#>
+xsd: <http://www.w3.org/2001/XMLSchema#>
+rdfs: <http://www.w3.org/2000/01/rdf-schema#>
+
+: <http://data.krw.d2s.labs.vu.nl/group6/findaslot/vocab/>
+data: <http://data.krw.d2s.labs.vu.nl/group6/findaslot/resource/>
+geo: <http://www.w3.org/2003/01/geo/wgs84_pos#>
+math: <http://www.w3.org/2005/xpath-functions/math#>
+dbo: <http://dbpedia.org/ontology/>
+\end{lstlisting}
 
@@
 \begin{lstlisting}[captionpos=b, caption=SPARQL query for getting parking spots close to Podium Mozaiek (sorted by distance), label=lst:sparql,
-basicstyle=\ttfamily,frame=bt]
+basicstyle=\ttfamily\small,frame=bt]
 

### 2016-04-20 milestone2/paper/paper.tex
Brainstorm about requirements for ontology

%%%%%%%%%%%%%%%%%%%%%%% file moduleX_template.tex %%%%%%%%%%%%%%%%%
%
%
% This is a template for creating your papers for the course KRW
% It is based on the standard Latex template for Springer publications
% but contains a suggestion for the structure and some content of the
% paper.
%
% Please adapt this document wherever needed.
%
% For more information about the required Latex Style check the document
% typeinst.pdf in the StyleFiles directory.
%
%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%

\documentclass[runningheads,a4paper]{../../StyleFiles/llncs}

\usepackage{url}
\usepackage{graphicx}
\usepackage{amssymb}

\newcommand{\keywords}[1]{\par\addvspace\baselineskip
\noindent\keywordname\enspace\ignorespaces#1}

\begin{document}

\mainmatter  % start of an individual contribution

% first the title is needed
\title{Data- and Ontology Paper: Quality Ontology for Parking Spots around Venues in Amsterdam}

% a short form should be given in case it is too long for the running head
\titlerunning{Data- and Ontology Paper}

% the name(s) of the author(s) follow(s) next
%
% NB: Chinese authors should write their first names(s) in front of
% their surnames. This ensures that the names appear correctly in
% the running heads and the author index.
%
\author{Alivanistos, Dimitris. \\ Baez, Selene. \\ Jemmett, Andrea. }
%
\authorrunning{Alivanistos, Dimitris. \\ Baez, Selene. \\ Jemmett, Andrea.}
% (feature abused for this document to repeat the title also on left hand pages)

% the affiliations are given next; don't give your e-mail address
% unless you accept that it will be published
\institute{\url{d.alivanistos@student.vu.nl} \and \url{s.baezsantamaria@student.vu.nl} \and \url{a.jemmett@student.vu.nl}}

\maketitle

\begin{abstract}
The abstract should summarize the contents of the paper and should
contain at least 70 and at most 150 words. It should be written using the
\emph{abstract} environment.
\end{abstract}

\section{Section 1 - Introduction}
\textit{Introduce the sections that follow. What is the core contribution of this paper, and why is that interesting? It is useful to start with a use case (practical/theoretical), and then explain how your ontology (will) solve(s) that problem by means of KR technology. Why is this novel? Has this (or something similar) been done before?}

- Information about handicap parking spots in Amsterdam is not well organized. Datasets exists and are available to the public but they are not well structures in a human readable manner.

- We focus on a particular usage of such parking spots, those linked to events happening in the city of Amsterdam.

- Our ontology organizes the events and venues into subtypes. This brings clarity for users who have special interest. (E.g. Toribio is only interested in theater plays. He is in a wheelchair and needs accessible parking spots to go to Theaters when he selects a play to watch).

- Our ontology has organized knowledge about addresses. It treats Streets and Postal codes as entities. Thus, a postal code is related to a set of events, a set of venues, and a set of parking spots. (E.g. Chachita has appointments once every week at the Femme Amsterdam Hospital. She would like to look for events nearby to attend after her sessions.)
(NOTE: important entailment here!!!! if we know a venue is in a postal code, all events related to the venue must be related to the same postal code.)

\section{Section 2 - Use Case and Requirements}
\textit{Describe the use-case you have in mind that motivates the need for the ontology. This could be the original use case from milestone 1, but then you should explain why the schema you defined previously falls short. What requirements should the ontology meet? What is its intended scope.}
\subsection{Previous use cases}
\begin{enumerate}
	% Planning in advance
	\item John is in a wheelchair and wants to go to an exhibition in Van Gogh Museum Friday night. John likes to plan things in advance and would like to know where the parking slots closest to the theater are. \\
	The day before the show, John uses our application to find such parking slots and heads to the show confidently. 
	% Quick search once in the theater (on the fly)
	\item Peter broke his leg last month and his friends, as an attempt to cheer him up, invited him to come to a comedy show at the Comedy Cafe. He is quite late and he is rushing to find the closest parking slots. He quickly browses our application and finds an area with several parking slots. He drives in that direction hoping to find an available slot. 
	% Event manager
	\item Mary is an event organizer who wants to host an exhibition in a museum next month. She is looking for an accessible venue so she would like to see the distribution of parking slots around the main galleries in Amsterdam. She has a list of five places in mind and uses our application to explore and choose the best venue.
\end{enumerate}

\textbf{Why the previous schema falls short?}

- John and Peter have to go through a long list of events till they find the exhibition or show they are attending. A new ontology that subdivides events into types helps him navigate the data more easily.

\section{Section 3 - Related Work}
What other ontologies did you find that cover a similar domain. To what extent can they be reused. Have others (e.g. other students) developed similar datasets/ontologies that feed/meet your requirements, where do they fall short? Papers to look for are published at eg. ISWC, ESWC, EKAW and FOIS, or the Journal of Web Semantics, and the Semantic Web Journal.

\section{Section 4 - Methodology}
Describe the methodology you followed for constructing the ontology. How did you guarantee that the ontology meets the needs and requirements of the use case? Have you used any existing design patterns, partial ontologies, competency questions etc.

\section{Section 5 - The Ontology}
Systematically describe the ontology and highlight the (interesting) design choices you had to make. Were there things you wanted to represent but couldn't given the limitations on the KR language?\footnote{If you do not encounter any limitations, you should be more ambitious about the model!} How did you work around these limitations? (integrity constraints, additional rules?) Describe how the ontology meets the 5 star model for Linked Vocabulary Use.

\section{Section 6 - The Dataset}
Describe how you recasted the dataset(s) of the previous assignment to the new ontology (perhaps you found other datasets that you want to add). What did it take to do this? What metadata have you published alongside the dataset, and how did you generate it? (Provenance, VOID, etc.) Describe how your data meeds the 5 star model for Linked Data.

\section{Section 7 - Evaluation}
Evaluate the ontology and dataset with respect to each other (does the ontology really sanction only the intended inference) and with respect to the requirements and use case (extend your application?!). You may want to analyze the ontology using some quality criteria from the literature.

\section{Discussion}
Here you summarize the preceding sections, describe the lessons learnt and discuss future work.

\bibliographystyle{plain}
\bibliography{mybib}

\end{document}

### 2016-04-21 milestone2/paper/paper.tex
More report

@@
 
+%TODO: is this novel? Website for accesible amsterdam does not have anything similar.
+
 \section{Section 2 - Use Case and Requirements}
@@
 
+New use cases explained in the introduction.
+
 \section{Section 3 - Related Work}
-What other ontologies did you find that cover a similar domain.
+\textit{What other ontologies did you find that cover a similar domain.
 To what extent can they be reused.
@@
 Papers to look for are published at eg.
-ISWC, ESWC, EKAW and FOIS, or the Journal of Web Semantics, and the Semantic Web Journal.
+ISWC, ESWC, EKAW and FOIS, or the Journal of Web Semantics, and the Semantic Web Journal.}
+
+ - Ontology for smart cities: \cite{komninos2015smart}
 

### 2016-04-22 milestone1/convert-datasets.py
folder refactoring

@@ -22,6 +22,9 @@ DBR = Namespace(dbr)
 
 repo_url = "http://stardog.krw.d2s.labs.vu.nl/group6"
 
+SOURCE_DATA_DIR = '../source_datasets/'
+OUTPUT_DIR = 'data/'
+
 
 def convert_dataset(path, dataset, graph_uri):
     f = open(path, 'r')
@@ -33,7 +36,7 @@ def convert_dataset(path, dataset, graph_uri):
     for event_data in json_data:
         event = URIRef(to_iri(resource + event_data['title'].strip()))
         title = Literal(event_data['title'].strip(), datatype=XSD['string'])
-        
+
         dates = event_data['dates']
         if dates != []:
             single_dates = [Literal(datetime.strptime(d, '%d-%m-%Y').date())
@@ -73,10 +76,10 @@ def convert_dataset(path, dataset, graph_uri):
                 detail['short_description'] = Literal(details_dict[lang]['shortdescription'].strip(), lang=lang)
             details.append(detail)
 
-        
+
         graph.add((event, RDF.type, VOCAB['Event']))
         graph.add((event, RDFS.label, title))
-        
+
         if dates != []:
             for single_date in single_dates:
                 graph.add((event, VOCAB['single_date'],  single_date))
@@ -84,7 +87,7 @@ def convert_dataset(path, dataset, graph_uri):
                 graph.add((event, VOCAB['start_date'], start_date))
             if end_date:
                 graph.add((event, VOCAB['end_date'], end_date))
-        
+
         if location_dict['name'] != '':
             graph.add((event, VOCAB['venue'], place))
             dataset.add((place, RDF.type, VOCAB['Venue']))
@@ -127,27 +130,27 @@ def convert_parking_dataset(path, dataset, graph_uri):
 
     for data in json_data['gehandicaptenparkeerplaatsen']:
         slot_data = data['node']
-        
+
         data_address = slot_data['Adres'].strip()
         if data_address == '':
             continue
         slot = URIRef(to_iri(resource + data_address))
-        
+
         slot_loc = URIRef(to_iri(resource + 'Amsterdam/' + data_address))
         slot_loc_address = Literal(data_address)
-        
+
         data_quantity = slot_data['Aantal'].strip()
[…]

### 2016-04-22 milestone2/convert-datasets.py
started uploading second version of dataset

@@ -1,0 +1,248 @@
+#!/usr/bin/env python
+
+import json
+from datetime import datetime
+from rdflib import Dataset, URIRef, Literal, Namespace, RDF, RDFS, OWL, XSD
+from iribaker import to_iri
+import requests
+from SPARQLWrapper import SPARQLWrapper, JSON
+from pprint import pprint
+
+
+resource = 'http://data.krw.d2s.labs.vu.nl/group6/findaslot/resource/'
+RESOURCE = Namespace(resource)
+vocab = 'http://data.krw.d2s.labs.vu.nl/group6/findaslot/vocab/'
+VOCAB = Namespace(vocab)
+geo = 'http://www.w3.org/2003/01/geo/wgs84_pos#'
+GEO = Namespace(geo)
+dbo = 'http://dbpedia.org/ontology/'
+DBO = Namespace(dbo)
+dbr = 'http://dbpedia.org/resource/'
+DBR = Namespace(dbr)
+
+repo_url = "http://stardog.krw.d2s.labs.vu.nl/group6"
+
+VOCAB_FILE = 'vocab_v2.ttl'
+SOURCE_DATA_DIR = '../source_datasets/'
+OUTPUT_DIR = 'data/'
+
+
+def convert_dataset(path, dataset, graph_uri, museums=True):
+    f = open(path, 'r')
+    json_data = json.load(f)
+
+    graph = dataset.graph(graph_uri)
+    country = URIRef(to_iri(dbr + 'Kingdom of the Netherlands'))
+
+    for event_data in json_data:
+        event = URIRef(to_iri(resource + event_data['title'].strip()))
+        title = Literal(event_data['title'].strip(), datatype=XSD['string'])
+
+        dates = event_data['dates']
+        if dates != []:
+            single_dates = [Literal(datetime.strptime(d, '%d-%m-%Y').date())
+                for d in dates['singles']] if dates.has_key('singles') else []
+            start_date = Literal(datetime.strptime(dates['startdate'], '%d-%m-%Y').date()) \
+                if dates.has_key('startdate') else None
+            end_date = Literal(datetime.strptime(dates['enddate'], '%d-%m-%Y').date()) \
+                if dates.has_key('enddate') and dates['enddate'] != '' else None
+
+        location_dict = event_data['location']
+        location_d_name = location_dict['name'].strip()
+        if location_d_name != '':
+            place = URIRef(to_iri(resource + location_d_name))
[…]

### 2016-04-23 milestone2/paper/paper.tex
Added Labels to vocab and described vocab in report

@@
 \usepackage{amssymb}
+\usepackage{listings}
 
@@
 % first the title is needed
-\title{Data- and Ontology Paper: Quality Ontology for Parking Spots around Venues in Amsterdam}
+\title{Data- and Ontology Paper: Quality Ontology for Handicap Parking Spots around Venues in Amsterdam}
 
@@
 
+\subsection{Requiremnts}
+
+\begin{enumerate}
+	\item Search subset of events
+	\item Detailed location information
+	\item Detailed information about Parking Slots
+\end{enumerate}
+
 \section{Section 3 - Related Work}
@@
 \section{Section 4 - Methodology}
-Describe the methodology you followed for constructing the ontology.
+\textit{Describe the methodology you followed for constructing the ontology.
 How did you guarantee that the ontology meets the needs and requirements of the use case?
-Have you used any existing design patterns, partial ontologies, competency questions etc.
+Have you used any existing design patterns, partial ontologies, competency questions etc.}
+
+- Use of Protégé
+
+- Iterative process.
+
+- Subclasses, cardinality, object Properties
+
+- Extensive use of powerful ontologies like dbo. Use of equivalence between dbo:Place and dbo:Location
 
 \section{Section 5 - The Ontology}
-Systematically describe the ontology and highlight the (interesting) design choices you had to make.
+\textit{Systematically describe the ontology and highlight the (interesting) design choices you had to make.
 Were there things you wanted to represent but couldn't given the limitations on the KR language?\footnote{If you do not encounter any limitations, you should be more ambitious about the model!} How did you work around these limitations?
-(integrity constraints, additional rules?) Describe how the ontology meets the 5 star model for Linked Vocabulary Use.
+(integrity constraints, additional rules?) Describe how the ontology meets the 5 star model for Linked Vocabulary Use.}
+
+%TODO insert image
+\begin{figure}[h]
+	\centering
+	\includegraphics[width=.7\textwidth]{img/ontology.png}
+	\caption{Visualization of the Ontology graph}
+	\label{fig:ontology}
+\end{figure}
+
+\subsection{Entities}
+- Now we have subclasses for each of the main type of classes we had before
+
+- Events: into Plays and Exhibitions
+- Venues into Theatres and Museums
+- Parking Slot into Small Medium and Large
+
+- First two distinctions come from the datasets themselves. The third one we created based on size. Parking Slot has datatype property quantity, which serves a a classifier
+
+\begin{lstlisting}[captionpos=b, caption=Definition of Large Slot a subclass of Parking Slot, label=lst:sparql, basicstyle=\ttfamily\small,frame=bt]
+(dbo:location exactly 1 Location)
+and (info exactly 1 xsd:string)
+and (quantity exactly 1 xsd:unsignedInt)
+\end{lstlisting}
+
+- Our Location class extends dbo:Location class in the use of Borough
+
+\subsection{Properties}
+
+- Restrictions on datatype properties. Cardinalities are explicit, so that they reflect that an Event has only one Venue, for example
+
+- Introduce 'Event venue' which has subproperties 'Exhibition Venue' and 'Play Venue' depending on their range. Also introduce its inverse 'Venue Events'
+
+- We create a subproperty of dbo:location to be 'venue location'. We restrict dbo:location to have domain Parking Slots while 'venue location' has domain Venues. Both have Location as range.
+
+- Properties for Borough, City and Country
 

### 2016-04-23 milestone2/convert-datasets.py
fixed some errors in vocab

@@ -54,7 +54,7 @@ def convert_dataset(path, dataset, graph_uri, museums=True):
             place_name = Literal(location_d_name, datatype=XSD['string'])
             location_city_str = location_dict['city'].strip().capitalize()
             location = URIRef(to_iri(resource + location_city_str + '/' + location_dict['adress'].strip()))
-            location_city = Literal(location_city_str)
+            location_city = URIRef(to_iri(dbr + location_city_str))
             location_address = Literal(location_dict['adress'].strip())
             location_zip = Literal(location_dict['zipcode'].strip())
             location_lat = Literal(float(location_dict['latitude'].replace(',', '.')))
@@ -148,7 +148,7 @@ def convert_parking_dataset(path, dataset, graph_uri):
 
         data_info = slot_data['Locatie-info']
         slot_info = Literal(data_info) if data_info != '' else None
-        slot_loc_borough = Literal(slot_data['Stadsdeel'].strip())
+        slot_loc_borough = URIRef(to_iri(resource + 'Amsterdam/' + slot_data['Stadsdeel'].strip()))
 
         slot_coordinates = json.loads(slot_data['locatie'].strip())
         slot_loc_lat = Literal(float(slot_coordinates['coordinates'][1]))
@@ -168,6 +168,7 @@ def convert_parking_dataset(path, dataset, graph_uri):
         dataset.add((slot_loc, DBO['address'], slot_loc_address))
         dataset.add((slot_loc, DBO['city'], city))
         dataset.add((slot_loc, DBO['country'], country))
+        dataset.add((slot_loc_borough, RDF.type, VOCAB['Borough']))
         dataset.add((slot_loc, VOCAB['borough'], slot_loc_borough))
         dataset.add((slot_loc, GEO['lat'], slot_loc_lat))
         dataset.add((slot_loc, GEO['long'], slot_loc_long))

### 2016-04-23 milestone2/convert-datasets.py
fixed some more inconsistencies

@@ -96,7 +96,7 @@ def convert_dataset(path, dataset, graph_uri, museums=True):
                 graph.add((event, VOCAB['playVenue'], place))
             dataset.add((place, RDF.type, VOCAB['Venue']))
             dataset.add((place, RDFS.label, place_name))
-            dataset.add((place, DBO['location'], location))
+            dataset.add((place, VOCAB['venueLocation'], location))
             dataset.add((location, RDF.type, VOCAB['Location']))
             dataset.add((location, RDFS.label, location_address))
             dataset.add((location, DBO['address'], location_address))
@@ -161,7 +161,7 @@ def convert_parking_dataset(path, dataset, graph_uri):
             graph.add((slot, VOCAB['quantity'], slot_quantity))
         if slot_info:
             graph.add((slot, VOCAB['info'], slot_info))
-        graph.add((slot, DBO['location'], slot_loc))
+        graph.add((slot, VOCAB['slotLocation'], slot_loc))
 
         dataset.add((slot_loc, RDF.type, VOCAB['Location']))
         dataset.add((slot_loc, RDFS.label, slot_loc_address))

### 2016-04-23 milestone2/paper/paper.tex
More outline, more stuff

@@
 \usepackage{listings}
+\lstset{language=SQL,morekeywords={and, some, exactly}}
 
@@
 
-\section{Section 1 - Introduction}
-\textit{Introduce the sections that follow.
-What is the core contribution of this paper, and why is that interesting?
-It is useful to start with a use case (practical/theoretical), and then explain how your ontology (will) solve(s) that problem by means of KR technology.
-Why is this novel?
-Has this (or something similar) been done before?}
+\section{Introduction}
+Amsterdam, a busy and tourist city as it is, offers a variety of events throughout the year.
+As such, a relevant topic related to the previous is the accessibility the city provides for handicap people to attend such events.
+In particular, this project focuses on providing these users with a way to find Parking Slots when attending events in different venues in Amsterdam.
 
-- Information about handicap parking spots in Amsterdam is not well organized. Datasets exists and are available to the public but they are not well structures in a human readable manner.
+Though information about handicap parking slots in Amsterdam is public through the Municipality, the datasets are not structured in a human readable manner.
+Moreover, the link to venues and events is not well organized and has not been addressed in a user-friendly manner.
+To the extent of our knowledge, the application that gets closest to this description is the official website for Accessibility in Amsterdam, which still fails to provide with an easily searchable tool for finding handicap parking slots given an Event and/or Venue.
+%TODO link to download datasets and to website.
 
-- We focus on a particular usage of such parking spots, those linked to events happening in the city of Amsterdam.
+This paper is an extension of the previous paper on Milestone 1, where we set up the project to solve the aforementioned problem, linking datasets from events at Theatres, and Museums and Galleries, to the Handicap Parking Slots dataset.
+In this paper the overall goal is to improve on the knowledge graph created for the application by creating an ontology that is formal yet intuitive for its potential users.
 
-- Our ontology organizes the events and venues into subtypes.
-This brings clarity for users who have special interest.
-(E.g.
-Toribio is only interested in theater plays.
-He is in a wheelchair and needs accessible parking spots to go to Theaters when he selects a play to watch).
-
-- Our ontology has organized knowledge about addresses.
-It treats Streets and Postal codes as entities.
-Thus, a postal code is related to a set of events, a set of venues, and a set of parking spots.
-(E.g.
-Chachita has appointments once every week at the Femme Amsterdam Hospital.
-She would like to look for events nearby to attend after her sessions.)
-(NOTE: important entailment here!!!! if we know a venue is in a postal code, all events related to the venue must be related to the same postal code.)
-
-%TODO: is this novel? Website for accesible amsterdam does not have anything similar.
+In the following section we further motivate the paper by providing concrete use cases that lead to a list of higher level requirements to be fulfilled by our project.
+Later, we describe an inspiration paper that guided us through the design of our ontology.
+We continue to describe our ontology, highlighting the major improvements from the knowledge graph in Milestone 1, followed up by evaluating the proposed ontology.
+Finally, some discussion provides with insights regarding the main contributions and future improvements on this project.
 
 \section{Section 2 - Use Case and Requirements}
-\textit{Describe the use-case you have in mind that motivates the need for the ontology.
+%\textit{Describe the use-case you have in mind that motivates the need for the ontology.
 This could be the original use case from milestone 1, but then you should explain why the schema you defined previously falls short.
@@
 What is its intended scope.}
+In order to better illustrate the motivation for this project we look back to the use cases from Milestone 1 to evaluate how well the current knowledge graph meets their needs.
+Next, we ambitiously create a couple more use cases to extend the potential uses of the application.
+We finalize by providing with a list of three specific requirements an ontology must meet to satisfy the users needs.
+
 \subsection{Previous use cases}
@@
 \textbf{Why the previous schema falls short?}
-
-- John and Peter have to go through a long list of events till they find the exhibition or show they are attending.
+John and Peter have to go through a long list of events till they find the exhibition or show they are attending.
 A new ontology that subdivides events into types helps him navigate the data more easily.
 
-New use cases explained in the introduction.
-
-\subsection{Requiremnts}
+\subsection{New use cases}
 
 \begin{enumerate}
-	\item Search subset of events
+	% Search by interest
+	\item Toribio is only interested in theatre plays. He is in a wheelchair and needs accessible parking spots to go to Theatres when he selects a play to watch. 
+	% Search by area
+	\item Chachita has appointments once every week at the Femme Amsterdam Hospital. She would like to look for events nearby to attend after her sessions. 
+\end{enumerate}
+
+\subsection{Requirements}
+
+\begin{enumerate}
+	\item Search by interest
 	\item Detailed location information
-	\item Detailed information about Parking Slots
+	\item Detailed information about Parking Slots (size)
 \end{enumerate}
@@
 
- - Ontology for smart cities: \cite{komninos2015smart}
+- Ontology for smart cities: \cite{komninos2015smart}. Heavily inspired by this paper for ontology design.
+
+- Our ontology fits in the broader schema of theirs. Specific for Handicap Parking Slots, Venues and Events.
 
@@
 
-\begin{lstlisting}[captionpos=b, caption=Definition of Large Slot a subclass of Parking Slot, label=lst:sparql, basicstyle=\ttfamily\small,frame=bt]
+\begin{lstlisting}[captionpos=b, caption=Definition of Large Slot a subclass of Parking Slot, label=lst:owl, basicstyle=\ttfamily\small,frame=bt]
 (dbo:location exactly 1 Location)
@@
 \section{Section 6 - The Dataset}
-Describe how you recasted the dataset(s) of the previous assignment to the new ontology (perhaps you found other datasets that you want to add).
+\textit{Describe how you recasted the dataset(s) of the previous assignment to the new ontology (perhaps you found other datasets that you want to add).
 What did it take to do this?
 What metadata have you published alongside the dataset, and how did you generate it?
-(Provenance, VOID, etc.) Describe how your data meeds the 5 star model for Linked Data.
+(Provenance, VOID, etc.) Describe how your data meeds the 5 star model for Linked Data.}
 
 \section{Section 7 - Evaluation}
-Evaluate the ontology and dataset with respect to each other (does the ontology really sanction only the intended inference) and with respect to the requirements and use case (extend your application?!).
-You may want to analyze the ontology using some quality criteria from the literature.
+\textit{Evaluate the ontology and dataset with respect to each other (does the ontology really sanction only the intended inference) and with respect to the requirements and use case (extend your application?!).
+You may want to analyze the ontology using some quality criteria from the literature.}
+
+\subsection{Comparison with the dataset}
+%TODO insert queries
+
+\subsection{Comparison with requirements}
+\begin{enumerate}
+	\item Search by interests: Initial division of events and Venues by personal interest.
+	\item Detailed location information: Ability to search for Venues and Parking Slots in same Borough is simple.
+	\item Detailed information about Parking Slots: Size is explicit
+\end{enumerate}
+
+- Our ontology organizes the events and venues into subtypes. This brings clarity for users who have special interest.
+
+- Our ontology has organized knowledge about addresses. It treats cities and boroughs as entities. Thus, a borough is related to a set of events, a set of venues, and a set of parking spots.
+
+\subsection{Evaluate according to five stars}
+- Use of other ontologies
 
 \section{Discussion}
-Here you summarize the preceding sections, describe the lessons learnt and discuss future work.
+\textit{Here you summarize the preceding sections, describe the lessons learnt and discuss future work.}
 

### 2016-04-23 milestone2/paper/paper.tex
use cases and requirements

@@
 	\item John is in a wheelchair and wants to go to an exhibition in Van Gogh Museum Friday night.
-John likes to plan things in advance and would like to know where the parking slots closest to the theater are.
-\\
-	The day before the show, John uses our application to find such parking slots and heads to the show confidently. 
+The day before the show, John uses our application to find the parking slots closest to the museum and heads to the show confidently.
 	% Quick search once in the theater (on the fly)
 	\item Peter broke his leg last month and his friends, as an attempt to cheer him up, invited him to come to a comedy show at the Comedy Cafe.
-He is quite late and he is rushing to find the closest parking slots.
-He quickly browses our application and finds an area with several parking slots.
+He is quite late and quickly browses our application and finds an area with several parking slots.
 He drives in that direction hoping to find an available slot.
@@
 
-\textbf{Why the previous schema falls short?}
-John and Peter have to go through a long list of events till they find the exhibition or show they are attending.
-A new ontology that subdivides events into types helps him navigate the data more easily.
+\subsubsection{Reflection on previous knowledge graph} 
+In the previous Milestone we showed that our application successfully integrates the Events and Handicap Parking Slots datasets, thus allowing users to look for parking slots close to venues in a time-saving way.
+However, some of the needs expressed in the previous use cases can be better met.
+For example, currently John and Peter would have to browse through a long list of events till they find the exhibition or show they are attending.
+A better ontology that subdivides events into types could help them navigate the data more easily.
+
+Furthermore, another notable shortcoming is that parking slots are only sorted in terms of distance to venues, ignoring other relevant facts like its size.
+For example, Peter might want to head to a close, yet large parking slot in order to increase its chances to find an available spot.
+Similarly, Mary might want to have information about the capacity of the parking slots depending on the size of the event she is planning.
 
 \subsection{New use cases}
-
 \begin{enumerate}
@@
 \subsection{Requirements}
+Given the above, we abstract the presented needs into a high level set of requirements.
+To keep the project within a manageable scope, we limit the requirements to three items, summarized in the following list.
 
@@
 	\item Search by interest
+	\item Detailed information about Parking Slots (size)
 	\item Detailed location information
-	\item Detailed information about Parking Slots (size)
 \end{enumerate}
@@
 
-- Our ontology organizes the events and venues into subtypes. This brings clarity for users who have special interest.
-
-- Our ontology has organized knowledge about addresses. It treats cities and boroughs as entities. Thus, a borough is related to a set of events, a set of venues, and a set of parking spots.
-
 \subsection{Evaluate according to five stars}
-- Use of other ontologies
+- Usage of other ontologies like dbo and geo
+- Metadata ?
 

### 2016-04-23 milestone2/convert-datasets.py
fixed all inconsistencies!

@@ -144,7 +144,7 @@ def convert_parking_dataset(path, dataset, graph_uri):
         slot_loc_address = Literal(data_address)
 
         data_quantity = slot_data['Aantal'].strip()
-        slot_quantity = Literal(int(data_quantity)) if data_quantity != '' else None
+        slot_quantity = Literal(int(data_quantity), datatype=XSD['unsignedInt']) if data_quantity != '' else None
 
         data_info = slot_data['Locatie-info']
         slot_info = Literal(data_info) if data_info != '' else None

### 2016-04-23 milestone2/convert-datasets.py
generate VoID metadata

@@ -2,7 +2,7 @@
 
 import json
 from datetime import datetime
-from rdflib import Dataset, URIRef, Literal, Namespace, RDF, RDFS, OWL, XSD
+from rdflib import Dataset, Graph, URIRef, Literal, Namespace, RDF, RDFS, OWL, XSD
 from iribaker import to_iri
 import requests
 from SPARQLWrapper import SPARQLWrapper, JSON
@@ -235,15 +235,50 @@ dataset.default_context.parse(VOCAB_FILE, format='turtle')
 
 dataset, t_graph = convert_dataset(
     SOURCE_DATA_DIR + 'Theater.json', dataset, URIRef(graph_uri_base + 'theaters'), museums=False)
-serialize_upload(OUTPUT_DIR + 'theaters.trig', dataset)
-dataset.remove_graph(t_graph)
+serialize_upload(OUTPUT_DIR + 'theaters.trig', t_graph)
+# dataset.remove_graph(t_graph)
 
 dataset, mg_graph = convert_dataset(
     SOURCE_DATA_DIR + 'MuseaGalleries.json', dataset, URIRef(graph_uri_base + 'museums'), museums=True)
-serialize_upload(OUTPUT_DIR + 'museums.trig', dataset)
-dataset.remove_graph(mg_graph)
+serialize_upload(OUTPUT_DIR + 'museums.trig', mg_graph)
+# dataset.remove_graph(mg_graph)
 
 dataset, park_graph = convert_parking_dataset(
     SOURCE_DATA_DIR + 'gehandicaptenparkeerplaatsen.json', dataset, URIRef(graph_uri_base + 'parking-slots'))
-serialize_upload(OUTPUT_DIR + 'parking_slots.trig', dataset)
+serialize_upload(OUTPUT_DIR + 'parking_slots.trig', park_graph)
+# dataset.remove_graph(park_graph)
+
+
+# Generate VoID metadata
+from rdflib.void import generateVoID
+from rdflib.namespace import VOID
+dcterms_uri = 'http://purl.org/dc/terms/'
+DCTERMS = Namespace(dcterms_uri)
+
+# Theaters
+void_dataset_t = URIRef(graph_uri_base + 'theaters/void')
+void_g_t, _ = generateVoID(t_graph, dataset=void_dataset_t)
+serialize_upload(OUTPUT_DIR + 'void_theaters.trig', void_g_t)
+
+# Museums
[…]

### 2016-04-23 milestone2/convert-datasets.py
added more VoID metadata

@@ -249,7 +249,7 @@ serialize_upload(OUTPUT_DIR + 'parking_slots.trig', park_graph)
 # dataset.remove_graph(park_graph)
 
 
-# Generate VoID metadata
+### Generate VoID metadata
 from rdflib.void import generateVoID
 from rdflib.namespace import VOID
 dcterms_uri = 'http://purl.org/dc/terms/'
@@ -277,8 +277,13 @@ void_linked_g.add((void_linked_ds, RDF.type, VOID.Linkset))
 void_linked_g.add((void_linked_ds, VOID.target, void_dataset_t))
 void_linked_g.add((void_linked_ds, VOID.target, void_dataset_m))
 void_linked_g.add((void_linked_ds, VOID.target, void_dataset_ps))
+void_linked_g.add((void_linked_ds, VOID.sparqlEndpoint, URIRef(repo_url + '/query')))
 void_linked_g.add((void_linked_ds, DCTERMS['subject'], DBR['Museums']))
 void_linked_g.add((void_linked_ds, DCTERMS['subject'], DBR['Theaters']))
 void_linked_g.add((void_linked_ds, DCTERMS['subject'], DBR['Parking_space']))
+void_linked_g.add((void_linked_ds, DCTERMS['title'], Literal('Find A Slot')))
+void_linked_g.add((void_linked_ds, DCTERMS['description'],
+    Literal('A linked dataset of events, venues, museums and handicap\'s parking slots', lang='en')))
+void_linked_g.add((void_linked_ds, VOID.exampleResource, VOCAB['ParkingSlot']))
 serialize_upload(OUTPUT_DIR + 'void_linked.trig', void_linked_g)
 

### 2016-04-23 milestone2/paper/paper.tex
More report ...sigh

@@
 
-\section{Section 2 - Use Case and Requirements}
+\section{Use Case and Requirements}
 %\textit{Describe the use-case you have in mind that motivates the need for the ontology.
@@
 	% Search by interest
-	\item Toribio is only interested in theatre plays. He is in a wheelchair and needs accessible parking spots to go to Theatres when he selects a play to watch. 
+	\item Toby is a Theatre fan and he is interested in watching as many plays as possible. He is in a wheelchair and needs accessible parking spots to go to Theatres when he selects a play to watch. 
 	% Search by area
-	\item Chachita has appointments once every week at the Femme Amsterdam Hospital. She would like to look for events nearby to attend after her sessions. 
+	\item Chelsea has appointments once every week at the Femme Amsterdam Hospital. She would like to look for events nearby to attend after her sessions. 
 \end{enumerate}
@@
 \subsection{Requirements}
-Given the above, we abstract the presented needs into a high level set of requirements.
+\label{requirements}
+Given the above, we abstract the users needs into a high level set of requirements.
 To keep the project within a manageable scope, we limit the requirements to three items, summarized in the following list.
@@
 \begin{enumerate}
-	\item Search by interest
-	\item Detailed information about Parking Slots (size)
-	\item Detailed location information
+	\item A user should be able to look for specific types of events or specific venues according to his/her interests.
+	\item Information about the size of the parking slots should be readily available through search. 
+	\item Events, Venues and/or Parking Slots within a certain area should be related to each other and they can be easily grouped. 
 \end{enumerate}
 
-\section{Section 3 - Related Work}
-\textit{What other ontologies did you find that cover a similar domain.
+\section{Related Work}
+%\textit{What other ontologies did you find that cover a similar domain.
 To what extent can they be reused.
@@
 ISWC, ESWC, EKAW and FOIS, or the Journal of Web Semantics, and the Semantic Web Journal.}
+While doing research to meet the previous requirements, we ran across a variety of ontologies that aim to cover similar domains as ours.
+Within the domain of information related to cities, we found the work by Komninos et al.\cite{komninos2015smart} to be particularly inspirational for designing this paper's ontology.
+With its project, the authors bring awareness to the fact that, regardless of the effort by developers to create applications for smart cities, the impact of those is still low.
+They attribute the problem to the lack of coordinated effort to create a standardized high quality ontology, and propose to unify the existent ontologies into the Smart City Ontology (SCO).
+%Following a structure thinking, SCO consists of 10 superclasses which reflect the three main aspects of a smart city.
 
-- Ontology for smart cities: \cite{komninos2015smart}. Heavily inspired by this paper for ontology design.
-
-- Our ontology fits in the broader schema of theirs. Specific for Handicap Parking Slots, Venues and Events.
+We want to accentuate the importance of coordination among well-formed ontologies and so we designed our ontology with the thought in mind to fit the broader schema laid down by Komninos el al.
+Ours is a specific and relatively small ontology that focuses on Handicap Parking Slots, Venues and Events.
+Yet, its full of potential can be achieved when assembled together with ontologies regarding other aspects of a city.
 
 \section{Section 4 - Methodology}
-\textit{Describe the methodology you followed for constructing the ontology.
+%\textit{Describe the methodology you followed for constructing the ontology.
 How did you guarantee that the ontology meets the needs and requirements of the use case?
@@
 
-- Use of Protégé
+Given the requirements from Section \ref{requirements}, and with the objective mentioned above, we design the ontology through an iterative process, revising at each step that the users needs were met while keeping the potential for communication with other ontologies open.
+We use Protege 5.0 as a tool for creating the ontology as well as for testing the inferences among the stated facts.
 
-- Iterative process.
-
-- Subclasses, cardinality, object Properties
+Furthermore, we elaborate on the expressiveness of the ontology and exploit the power of the Web Ontology Language (OWL) to represent more complex aspects such as cardinalities and equivalences among existing and newly created Subclasses and Object Properties.
 

### 2016-04-23 milestone2/paper/paper.tex
section 4

@@
 \lstset{language=SQL,morekeywords={and, some, exactly}}
+\usepackage{caption}
+\usepackage{subcaption}
 
@@
 
-\section{Section 4 - Methodology}
+\section{Methodology}
 %\textit{Describe the methodology you followed for constructing the ontology.
@@
 
-Given the requirements from Section \ref{requirements}, and with the objective mentioned above, we design the ontology through an iterative process, revising at each step that the users needs were met while keeping the potential for communication with other ontologies open.
+Given the requirements from Section \ref{requirements}, and with the objective mentioned above, we design the ontology through an iterative process, revising at each step that the users needs were met while keeping the potential for linking to other ontologies open.
 We use Protege 5.0 as a tool for creating the ontology as well as for testing the inferences among the stated facts.
@@
 
-- Extensive use of powerful ontologies like dbo. Use of equivalence between dbo:Place and dbo:Location
+As stated in the previous Milestone, we incorporate other ontologies like \texttt{dbepedia} \footnote{The \texttt{dbepedia} namespace is defined at \url{http://dbpedia.org/ontology/}} for location management, and \texttt{geo} \footnote{The \texttt{geo} namespace is defined at \url{http://www.w3.org/2003/01/geo/wgs84_pos}} for latitude and longitude management.
+This time, we exploit the usage of dbepedia and make use of the equivalence between dbo:Place and dbo:Location.
+Further explanation of the benefits of this are explained in the following section.
 
-\section{Section 5 - The Ontology}
-\textit{Systematically describe the ontology and highlight the (interesting) design choices you had to make.
+\section{The Ontology}
+%\textit{Systematically describe the ontology and highlight the (interesting) design choices you had to make.
 Were there things you wanted to represent but couldn't given the limitations on the KR language?\footnote{If you do not encounter any limitations, you should be more ambitious about the model!} How did you work around these limitations?
 (integrity constraints, additional rules?) Describe how the ontology meets the 5 star model for Linked Vocabulary Use.}
+A comparison between the old knowledge graph and the newly created ontology is graphically depicted in Figure \ref{fig:ontology}.
 
-%TODO insert image
-\begin{figure}[h]
-	\centering
-	\includegraphics[width=.7\textwidth]{img/ontology.png}
-	\caption{Visualization of the Ontology graph}
+\begin{figure}[h] \centering
+	\begin{subfigure}{.5\textwidth} \centering
+		\includegraphics[width=.9\textwidth]{img/old_ontology.jpg}
+		\label{fig:old_ontology}
+	\end{subfigure}%
+	\begin{subfigure}{.5\textwidth} \centering
+		\includegraphics[width=.9\textwidth]{img/ontology.png}
+		\label{fig:new_ontology}
+	\end{subfigure}
+	\caption{Difference between original ontology (left) and updated ontology (right).}
 	\label{fig:ontology}
@@
 
+Given the degree of variation between both ontologies, we divide the updates on Entities and Properties and give a more detailed explanation in the following subsections.
+
 \subsection{Entities}
-- Now we have subclasses for each of the main type of classes we had before
+The main difference with the previous version of the ontology is that each of the three main classes are now subdivided into more specific subclasses. For example:
 
-- Events: into Plays and Exhibitions
-- Venues into Theatres and Museums
-- Parking Slot into Small Medium and Large
+\begin{itemize}
+	\item \textbf{Events}: Divided into Plays and Exhibitions
+	\item \textbf{Venues}: Divided into Theatres and Museums
+	\item \textbf{Parking Slots}: Divided into Small, Medium and Large Slots
+\end{itemize}
 

### 2016-04-23 milestone2/paper/paper.tex
Done till 5.1, missing 5.2, 6, 7 and discussion

@@
 
-- First two distinctions come from the datasets themselves. The third one we created based on size. Parking Slot has datatype property quantity, which serves a a classifier
+The divisions for the first two come straight from the datasets themselves.
+On the one hand, when an event comes from the Theatres dataset, we assume it is of type Play and it happens in a Venue of type Theatre.
+On the other hand, when the event comes from the Museums and Galleries dataset, we assume it is of type Exhibition and it happens in a Venue of type Museum.
+
+The third one, however, is a distinction we propose in order to better describe the Parking Slots.
+Previously, a Parking Slot's capacity was only described by its Datatype Property \textit{Quantity}.
+Now, we take this property and process it to classify Parking Slots into three types: Small (consisting on 1 or 2 individual slots), Medium (consisting of 3 or 4 individual slots) and Large (consisting of 5 or more individual slots).
+This classification is achieved through an equivalence fact as exemplified by the next listing.
+\\
 

### 2016-04-23 milestone2/convert-datasets.py
added VoID license

@@ -278,6 +278,7 @@ void_linked_g.add((void_linked_ds, VOID.target, void_dataset_t))
 void_linked_g.add((void_linked_ds, VOID.target, void_dataset_m))
 void_linked_g.add((void_linked_ds, VOID.target, void_dataset_ps))
 void_linked_g.add((void_linked_ds, VOID.sparqlEndpoint, URIRef(repo_url + '/query')))
+void_linked_g.add((void_linked_ds, DCTERMS['license'], URIRef('http://creativecommons.org/publicdomain/zero/1.0/')))
 void_linked_g.add((void_linked_ds, DCTERMS['subject'], DBR['Museums']))
 void_linked_g.add((void_linked_ds, DCTERMS['subject'], DBR['Theaters']))
 void_linked_g.add((void_linked_ds, DCTERMS['subject'], DBR['Parking_space']))

### 2016-04-23 milestone2/paper/paper.tex
review section 7 & abstract

@@
 \usepackage{subcaption}
+\captionsetup{compatibility=false}
 
@@
 \begin{abstract}
-The abstract should summarize the contents of the paper and should
-contain at least 70 and at most 150 words. It should be written using the
-\emph{abstract} environment.
+% The abstract should summarize the contents of the paper and should
+% contain at least 70 and at most 150 words. It should be written using the
+% \emph{abstract} environment.
+We introduce a Linked Dataset integrating three different datasets related to
+the city of Amsterdam. We present the details of the dataset and the ontology
+that we introduce to cover all the important concepts of those data. Also we
+provide a thoughtful analysis of the methodology that we applied and the
+evaluation techniques that have been embraced. We enhanced our previous dataset
+with a richer ontology and we show how we published our results following the
+5-star model for Linked Data.
 \end{abstract}
@@
 The main difference with the previous version of the ontology is that each of the three main classes are now subdivided into more specific subclasses. For example:
-
 \begin{itemize}
@@
 \end{itemize}
+A visualization of the current class hierarchy is given in Figure
+\ref{fig:ontology-classes}.
+
+\begin{figure}[h] \centering
+	\includegraphics[width=.9\textwidth]{img/ontology-classes.png}
+	\caption{Class hierarchy for the current version of the Find A Slot ontology.}
+	\label{fig:ontology-classes}
+\end{figure}
 
@@
 
-\begin{lstlisting}[captionpos=b, caption=Definition of Large Slot a subclass of Parking Slot, label=lst:owl, basicstyle=\ttfamily\small,frame=bt]
-(dbo:location exactly 1 Location)
-and (info exactly 1 xsd:string)
-and (quantity exactly 1 xsd:unsignedInt)
+\begin{lstlisting}[captionpos=b, caption=Definition of Large Slot a subclass of Parking Slot, label=lst:owl, basicstyle=\ttfamily\small,frame=bt,showstringspaces=false]
+'Parking Slot' 
+and (quantity some xsd:unsignedInt[>= "5"^^xsd:unsignedInt])
 \end{lstlisting}
 
-- Our Location class extends dbo:Location class in the use of Borough
+\begin{lstlisting}[captionpos=b, caption=Definition of Medium Slot a subclass of Parking Slot, label=lst:owl, basicstyle=\ttfamily\small,frame=bt,showstringspaces=false]
+'Parking Slot' 
+and (quantity some xsd:unsignedInt[>= "3"^^xsd:unsignedInt,
+ < "5"^^xsd:unsignedInt])
+\end{lstlisting}
+
+\begin{lstlisting}[captionpos=b, caption=Definition of Small Slot a subclass of Parking Slot, label=lst:owl, basicstyle=\ttfamily\small,frame=bt,showstringspaces=false]
+'Parking Slot' 
+ and (quantity some xsd:unsignedInt[>="1"^^xsd:unsignedInt ,
+  < "3"^^xsd:unsignedInt])
+\end{lstlisting}
+
+The last extension of the entities regards the creation of a class for \textit{Borough} with the purpose to link it to our Location entity.
+As explained before, we use the dbepedia for the management of location.
+However, dbo:Location does not include Boroughs, a crucial part of the description of a  location in Amsterdam.
+Thus, we create a subclass called Location, which is equivalent to a dbo:Location with a Borough, to represent the specific case of locations in Amsterdam.
 
@@
 
-- Restrictions on datatype properties. Cardinalities are explicit, so that they reflect that an Event has only one Venue, for example
+The first extension in the Properties regards restrictions on datatype properties.
+We have included cardinalities with respect to the real world.
+An example can be seen at the Event entity where we state that in order for an Event to be an Event, it also needs to have at least one Venue where it will take place.
 
-- Introduce 'Event venue' which has subproperties 'Exhibition Venue' and 'Play Venue' depending on their range. Also introduce its inverse 'Venue Events'
+Furthermore, we introduced the 'Event venue' property which has sub-properties 'Exhibition Venue' and 'Play Venue' according to their range.
+If event is an Exhibition then it uses the 'Exhibition Venue' property.
+We have also introduced the 'Venue Events' property as the inverse property of 'Event venue'.
 
-- We create a subproperty of dbo:location to be 'venue location'. We restrict dbo:location to have domain Parking Slots while 'venue location' has domain Venues. Both have Location as range.
+Moreover we included in our dbo:location property two sub-properties named 'slot location' and 'venue location'.
+We use these properties to restrict our dbo:location to have domain Parking Slot when we use the 'slot location' property and Venue when we use the 'venue location'.
+Both of them have Location as range.
 
-- Properties for Borough, City and Country
+The last extension of our properties section refers to the addition of the properties \textit{Borough} , \textit{City} and \textit{Country}.
+The reason behind this is that we want to have restrictions.
+In order to ensure that a dbo:location has exactly one country we use the equivalent rule :
+\\
 
-\section{Section 6 - The Dataset}
-\textit{Describe how you recasted the dataset(s) of the previous assignment to the new ontology (perhaps you found other datasets that you want to add).
-What did it take to do this?
-What metadata have you published alongside the dataset, and how did you generate it?
-(Provenance, VOID, etc.) Describe how your data meeds the 5 star model for Linked Data.}
+\begin{lstlisting}[captionpos=b, title=Class equivalent to dbo:Location with the use of our subproperties, label=lst:owl, basicstyle=\ttfamily\small,frame=bt]
+(city exactly 1 dbo:City) 
+and (country exactly 1 dbo:Country) 
+and (address exactly 1 xsd:string)
+\end{lstlisting}
 
-\section{Section 7 - Evaluation}
-\textit{Evaluate the ontology and dataset with respect to each other (does the ontology really sanction only the intended inference) and with respect to the requirements and use case (extend your application?!).
-You may want to analyze the ontology using some quality criteria from the literature.}
+Similarly for our \textit{Location} the equivalent rule is:
 
-\subsection{Comparison with the dataset}
-%TODO insert queries
+\begin{lstlisting}[captionpos=b, title=Class equivalent to Location with the use of our subproperty orough, label=lst:owl, basicstyle=\ttfamily\small,frame=bt]
+dbo:Location 
+and (dbo:borough exactly 1 Borough)
+\end{lstlisting}
 
-\subsection{Comparison with requirements}
+\section{The Dataset}
+% Describe how you recasted the dataset(s) of the previous assignment to the new
+% ontology (perhaps you found other datasets that you want to add). What did it
+% take to do this? What metadata have you published alongside the dataset, and how
+% did you generate it? (Provenance, VOID, etc.) Describe how your data meeds the 5
+% star model for Linked Data.
+The three datasets have been converted to a linked data format using the second
+version of the ontology in a straightforward way. We create
+resources for the newly introduced \texttt{Borough} class. Cities have been
+recasted to point to DBpedia resources (as for countries).
+Entities of class \texttt{Museum} or \texttt{Theater} are created based on their
+original dataset of provenience. An \texttt{Event} is linked to a
+\texttt{Venue} via a newly created object property and this allows the reasoning
+engine to infer if an \texttt{Event} is a \texttt{Play} or an \texttt{Exhibition}.
+
+Given the quantity of slots available for a \texttt{ParkingSlot}, thanks to the
+new ontology, the dataset distinguishes parking slots based their availability
+into \texttt{SmallSlot}, \texttt{MediumSlot} and \texttt{LargeSlot}. This
+provides a richer classification of parking slots than based on the quantity
+property directly. This is something that we get through inference, so it has
+not been directly coded into the conversion script.
+
+Each of the three datasets has been published with its companion VoID dataset,
+describing the contents of the dataset it refers to. Most of the metrics and
+metadata have been generated using \textbf{rdflib}'s \texttt{generateVoID}
+method applied on the three graphs.
+Moreover we publish a VoID Linkedset that links together the three datasets as a
+new one. Alongside this we provide some additional metadata from the
+\texttt{void:}\footnote{\url{http://rdfs.org/ns/void#}} ontology, such as
+\texttt{target}, \texttt{sparqlEndpoint} and
+\texttt{exampleResource} and from the
+\texttt{dcterms:}\footnote{\url{http://purl.org/dc/terms/}} ontology, such as
+\texttt{subject}, \texttt{title} and
+\texttt{description}. Those additional metadata have been added manually
+to the VoID dataset. The \texttt{void:Linkset} can be retrieved at the following
+URL \url{http://data.krw.d2s.labs.vu.nl/doc/group6/findaslot/resource/findaslot/void}.
+
+\subsection{5-star Open Data}
+We say that the published database is conform with standards proposed by the
+5-star model for Linked Data \cite{janowicz2014five}. Here we defend our statement by taking each of the
+five steps into consideration.
+
+\begin{description}
+\item[Available on the Web] We published our data under an open license,
+namely the CC0 1.0 Universal (this is declared in the VoID metadata).
+\item[Available as structured data] The dataset is available in RDF
+format which is structured.
+\item[Available as non-proprietary format] Again, our dataset is specified
+in a W3C language so it is not in a proprietary format but in an
+open and standardized format.
+\item[Use URIs to denote things] We use URIs to denote everything that is
+not an RDF Literal. Events, Venues, Locations and starting from this version of
+the ontology we include countries, cities and boroughs as resources defined by
+URIs.
+\item[Link to other data] We provide external pointers to resources from
+DBpedia such as for cities (e.g. \texttt{dbr:Amsterdam}), countries (e.g.
+\texttt{dbr:Netherlands}) or as \texttt{dcterms:subject}, in the VoID
+specification, we point to \texttt{dbr:Museums} and \texttt{dbr:Parking\_space}.
+\end{description}
+
+\section{Evaluation}
+For evaluating our ontology we got inspired by the work of Hlomani and Stacey
+\cite{hlomani2014approaches} on ontology evaluation and decided to evaluate our
+ontology using three major criteria:
 \begin{enumerate}
-	\item Search by interests: Initial division of events and Venues by personal interest.
-	\item Detailed location information: Ability to search for Venues and Parking Slots in same Borough is simple.
-	\item Detailed information about Parking Slots: Size is explicit
+	\item \textbf{Task-based Evaluation}. First of all we perform a task-based evaluation that typically evaluates how effective our ontology is in the context of an application.
+	\item \textbf{User-based Evaluation}.
+We perform a user-based evaluation that evaluates the ontology through user's experiences.
+Contrary to task-based evaluation, we are not accessing semantic validity and consistency of our ontology but we focus on the subjective information of it.
+	\item \textbf{Data-driven evaluation}. In the last part of this section we focus on evaluating our ontology by comparing it, with existing data about the domain it models.
 \end{enumerate}
 
-\subsection{Evaluate according to five stars}
-- Usage of other ontologies like dbo and geo
-- Metadata ?
+\subsection{Task-based Evaluation}
+\begin{enumerate}
+	\item \textbf{Search by interest}.
+	With the extension of our ontology we succeed in extending our application.
+We have enabled the search by interests, as we initially divide Events and Venues with regard to personal interest.
+This way the users can narrow down their search avoiding nonessential information.
+
+	\item \textbf{Search by Borough}.
+Another main aspect that adds to the improvement of our ontology are the detailed location information that the users have.
+Now the users have the ability to search for Venues and Parking Slots in same Borough in a simple way.
+
+	\item \textbf{Capacity of Parking Slots}.
+We also provide with explicit information about each Parking Slot that is close to the interests of the user.
+Users now have prior knowledge regarding the capacity of the parking spot they need.
+\end{enumerate}
+
+\subsection{User-based Evaluation}
+For our user-based evaluation we simply examined our dataset as a \textit{third
+user}. The source and the meta data that have been added with the void ontology
+provide with important information, not only on each of the three datasets
+separately but on the dataset as a whole. \textit{Labels}, \textit{descriptions}
+and important \textit{metrics}, such as the total number of triples that exist
+in each dataset are only some of the meta-data information that have been added.
+However the risk with the specific way of evaluation, is that it is difficult to
+establish objective standards as it depends on the different type of users
+involved.
+
+\subsection{Data-driven evaluation}
+So far our ontology combines knowledge from three different datasets in order to
+provide a useful service to the potential users of our application. Compared to
+other ontologies in the specific domain of finding parking slots it is clear
+that our ontology is quite innovative, since we focus specifically on people
+with handicap.
+
+With the addition of Borough as a key feature of Location, the data can be
+combined in a more efficient way, increasing the total efficiency of our web
+application even further.Besides efficiency, we wanted to check how well our
+ontology \textit{fits the domain knowledge} \cite{brewster2004data}.
+
+This was done by comparing ontology concepts derived from the three separate
+datasets that we used in milestone 1, with the latest version of our dataset.
+So far our ontology fits the domain knowledge of the three datasets, perfectly,
+however we realistically acknowledge the fact that there is certainly room for
+further improvement in the general domain of Events and Parking Slots.
 

### 2016-04-23 milestone2/paper/paper.tex
started discussion section

@@
 % a short form should be given in case it is too long for the running head
-\titlerunning{Data- and Ontology Paper}
+\titlerunning{Quality Ontology for Handicap Parking Spots around Venues in Amsterdam}
 
@@
 \section{Discussion}
-\textit{Here you summarize the preceding sections, describe the lessons learnt and discuss future work.}
+% \textit{Here you summarize the preceding sections, describe the lessons learnt and discuss future work.}
+In this paper we provided a detailed description of the improved ontology that
+we have published about three datasets related to the city of Amsterdam.
+Moreover we show the methodology that we adopted and how this led our ontology
+to be classified as fully conform with the 5-star model for Linked Data.
+Being conform to this model for Open Data means that publishers will ultimately
+have a dataset that is easily \textit{surfable} and \textit{connected} with
+other Web resources, generating more incoming traffic towards the dataset and
+increasing the value of the contained data. The 5-star model is a way to
+introduce sources of \textit{trust} in both the data and publishers' spaces.
+In particular we have found very useful and powerful the set of propositions offered
+by the VoID framework and how easy it is to define \textit{discoverable}
+ontologies using Web standards.
 

### 2016-04-23 milestone2/paper/paper.tex
pics and report :)

--- 2016-04-23 milestone2/paper/paper.tex
@@
 \begin{abstract}
-% The abstract should summarize the contents of the paper and should
-% contain at least 70 and at most 150 words. It should be written using the
-% \emph{abstract} environment.
-We introduce a Linked Dataset integrating three different datasets related to
-the city of Amsterdam. We present the details of the dataset and the ontology
-that we introduce to cover all the important concepts of those data. Also we
-provide a thoughtful analysis of the methodology that we applied and the
-evaluation techniques that have been embraced. We enhanced our previous dataset
-with a richer ontology and we show how we published our results following the
-5-star model for Linked Data.
+The abstract should summarize the contents of the paper and should
+contain at least 70 and at most 150 words. It should be written using the
+\emph{abstract} environment.
 \end{abstract}
@@
 
-As stated in the previous Milestone, we incorporate other ontologies like \texttt{dbepedia} \footnote{The \texttt{dbepedia} namespace is defined at \url{http://dbpedia.org/ontology/}} for location management, and \texttt{geo} \footnote{The \texttt{geo} namespace is defined at \url{http://www.w3.org/2003/01/geo/wgs84_pos}} for latitude and longitude management.
-This time, we exploit the usage of dbepedia and make use of the equivalence between dbo:Place and dbo:Location.
+As stated in the previous Milestone, we incorporate other ontologies like \texttt{DBpedia} \footnote{The \texttt{DBpedia} namespace is defined at \url{http://dbpedia.org/ontology/}} for location management, and \texttt{geo} \footnote{The \texttt{geo} namespace is defined at \url{http://www.w3.org/2003/01/geo/wgs84_pos}} for latitude and longitude management.
+This time, we exploit the usage of DBpedia and make use of the equivalence between dbo:Place and dbo:Location.
 Further explanation of the benefits of this are explained in the following section.
@@
 (integrity constraints, additional rules?) Describe how the ontology meets the 5 star model for Linked Vocabulary Use.}
-A comparison between the old knowledge graph and the newly created ontology is graphically depicted in Figure \ref{fig:ontology}.
+A comparison between the old knowledge graph (Figure \ref{fig:old_ontology}) and the newly created ontology (Figure \ref{fig:ontology-classes}) is graphically depicted below.
 
+\begin{figure}[h]\centering
+	\includegraphics[width=.7\textwidth]{img/old_ontology.jpg}
+	\caption{Knowledge graph from Milestone 1.}
+	\label{fig:old_ontology}
+\end{figure}
 \begin{figure}[h] \centering
-	\begin{subfigure}{.5\textwidth} \centering
-		\includegraphics[width=.9\textwidth]{img/old_ontology.jpg}
-		\label{fig:old_ontology}
-	\end{subfigure}%
-	\begin{subfigure}{.5\textwidth} \centering
-		\includegraphics[width=.9\textwidth]{img/ontology.png}
-		\label{fig:new_ontology}
-	\end{subfigure}
-	\caption{Difference between original ontology (left) and updated ontology (right).}
-	\label{fig:ontology}
+	\includegraphics[width=.7\textwidth]{img/ontology-classes.png}
+	\caption{Class hierarchy for the current version of the Find A Slot ontology.}
+	\label{fig:ontology-classes}
 \end{figure}
@@
 \subsection{Entities}
-The main difference with the previous version of the ontology is that each of the three main classes are now subdivided into more specific subclasses. For example:
+The main difference with the previous version of the ontology is that each of the three main classes is now subdivided into more specific subclasses. For example:
 \begin{itemize}
@@
 \end{itemize}
-A visualization of the current class hierarchy is given in Figure
-\ref{fig:ontology-classes}.
-
-\begin{figure}[h] \centering
-	\includegraphics[width=.9\textwidth]{img/ontology-classes.png}
-	\caption{Class hierarchy for the current version of the Find A Slot ontology.}
-	\label{fig:ontology-classes}
-\end{figure}
 
@@
 
-The last extension of the entities regards the creation of a class for \textit{Borough} with the purpose to link it to our Location entity.
-As explained before, we use the dbepedia for the management of location.
+The last extension of the entities regards the creation of a class for \textit{Borough} with the purpose of linking it to our Location entity.
+As explained before, we use the DBpedia ontology for the management of locations.
 However, dbo:Location does not include Boroughs, a crucial part of the description of a  location in Amsterdam.
@@
 We have included cardinalities with respect to the real world.
-An example can be seen at the Event entity where we state that in order for an Event to be an Event, it also needs to have at least one Venue where it will take place.
+An example can be seen at the Event entity where we state that an Event must have at least one Venue where it will take place.
 
@@
 The reason behind this is that we want to have restrictions.
-In order to ensure that a dbo:location has exactly one country we use the equivalent rule :
-\\
+In order to ensure that a dbo:location has exactly one country we use the equivalent rule: \\
 
@@
 
-\begin{lstlisting}[captionpos=b, title=Class equivalent to Location with the use of our subproperty orough, label=lst:owl, basicstyle=\ttfamily\small,frame=bt]
+\begin{lstlisting}[captionpos=b, title=Class equivalent to Location with the use of our subproperty borough, label=lst:owl, basicstyle=\ttfamily\small,frame=bt]
 dbo:Location 
@@
 % star model for Linked Data.
-The three datasets have been converted to a linked data format using the second
-version of the ontology in a straightforward way. We create
-resources for the newly introduced \texttt{Borough} class. Cities have been
-recasted to point to DBpedia resources (as for countries).
-Entities of class \texttt{Museum} or \texttt{Theater} are created based on their
-original dataset of provenience. An \texttt{Event} is linked to a
-\texttt{Venue} via a newly created object property and this allows the reasoning
-engine to infer if an \texttt{Event} is a \texttt{Play} or an \texttt{Exhibition}.
+Once again, the three datasets have been converted to a linked data format, now using the second version of the ontology in a straightforward way.
+We create resources for the newly introduced \texttt{Borough} class.
+Cities and countries have been recasted to point to DBpedia resources.
+Entities of class \texttt{Museum} or \texttt{Theatre} are created based on their original dataset of provenance.
+An \texttt{Event} is linked to a \texttt{Venue} via a newly created object property and this allows the reasoning engine to infer if an \texttt{Event} is a \texttt{Play} or an \texttt{Exhibition} based on its Venue type.
 
-Given the quantity of slots available for a \texttt{ParkingSlot}, thanks to the
-new ontology, the dataset distinguishes parking slots based their availability
-into \texttt{SmallSlot}, \texttt{MediumSlot} and \texttt{LargeSlot}. This
-provides a richer classification of parking slots than based on the quantity
-property directly. This is something that we get through inference, so it has
-not been directly coded into the conversion script.
+Given the quantity of slots available for a \texttt{ParkingSlot}, thanks to the new ontology, the dataset distinguishes parking slots based their availability into \texttt{SmallSlot}, \texttt{MediumSlot} and \texttt{LargeSlot}.
+This provides a richer classification of parking slots than based on the quantity
+property directly. It is remarkable that we get this through inference since it has not been directly coded into the conversion script.
 
-Each of the three datasets has been published with its companion VoID dataset,
-describing the contents of the dataset it refers to. Most of the metrics and
-metadata have been generated using \textbf{rdflib}'s \texttt{generateVoID}
+Each of the three datasets has been published with its companion VoID dataset, describing the contents of the dataset it refers to.
+Most of the metrics and metadata have been generated using \textbf{rdflib}'s \texttt{generateVoID}
 method applied on the three graphs.
@@
 
-\section{Evaluation}
-For evaluating our ontology we got inspired by the work of Hlomani and Stacey
-\cite{hlomani2014approaches} on ontology evaluation and decided to evaluate our
-ontology using three major criteria:
+\section{Section 7 - Evaluation}
+For evaluating our ontology we got inspired by the work of Hlomani and Stacey \cite{hlomani2014approaches} on ontology evaluation and decided to evaluate our ontology using three major criterion:
 \begin{enumerate}
@@
 \subsection{User-based Evaluation}
-For our user-based evaluation we simply examined our dataset as a \textit{third
-user}. The source and the meta data that have been added with the void ontology
-provide with important information, not only on each of the three datasets
-separately but on the dataset as a whole. \textit{Labels}, \textit{descriptions}
-and important \textit{metrics}, such as the total number of triples that exist
-in each dataset are only some of the meta-data information that have been added.
-However the risk with the specific way of evaluation, is that it is difficult to
-establish objective standards as it depends on the different type of users
-involved.
+For our user-based evaluation we simply examined our dataset as a \textit{third user}.
+The source and the meta data that have been added with the void ontology provide with important information, no only on each of the three datasets separately but on the dataset as a whole.
+\textit{Labels}, \textit{descriptions} and important \textit{metrics}, such as the total number of triples that exist in each dataset are only some of the meta-data information that have been added.
+However the risk with the specific way of evaluation, is that it is difficult to establish objective standards as it depends on the different type of users involved.
 
 \subsection{Data-driven evaluation}
-So far our ontology combines knowledge from three different datasets in order to
-provide a useful service to the potential users of our application. Compared to
-other ontologies in the specific domain of finding parking slots it is clear
-that our ontology is quite innovative, since we focus specifically on people
-with handicap.
+So far our ontology combines knowledge from three different datasets in order to provide a useful service to the potential users of our application.
+Compared to other ontologies in the specific domain of finding parking slots it is clear that our ontology is quite innovative, since we focus specifically on people with a certain handicap.
 
-With the addition of Borough as a key feature of Location, the data can be
-combined in a more efficient way, increasing the total efficiency of our web
-application even further.Besides efficiency, we wanted to check how well our
-ontology \textit{fits the domain knowledge} \cite{brewster2004data}.
+With the addition of Borough as a key feature of Location, the data can be combined in a more efficient way, increasing the total efficiency of our web application even further.Besides efficiency, we wanted to check how well our ontology \textit{fits the domain knowledge} \cite{brewster2004data}.
 
-This was done by comparing ontology concepts derived from the three separate
-datasets that we used in milestone 1, with the latest version of our dataset.
-So far our ontology fits the domain knowledge of the three datasets, perfectly,
-however we realistically acknowledge the fact that there is certainly room for
-further improvement in the general domain of Events and Parking Slots.
+This was done by comparing ontology concepts derived from the three separate datasets that we used in milestone 1, with the latest version of our dataset. 
+So far our ontology fits the domain knowledge of the three datasets, perfectly, however we realistically acknowledge the fact that there is certainly room for further improvement in the general domain of Events and Parking Slots.
 
@@
 \textit{Here you summarize the preceding sections, describe the lessons learnt and discuss future work.}
+Ontology may be too specific regarding domains and ranges of Object Properties. For example, if a :Location is not related to a Borough, then we will not recognize it as a :Location entity.
 

### 2016-04-23 milestone2/paper/paper.tex

@@
 \begin{abstract}
-The abstract should summarize the contents of the paper and should
-contain at least 70 and at most 150 words. It should be written using the
-\emph{abstract} environment.
+We introduce a Linked Dataset integrating three different datasets related to the city of Amsterdam.
+We present the details of the dataset and the ontology that we introduce to cover all the important concepts of those data.
+Also we provide a thoughtful analysis of the methodology that we applied and the evaluation techniques that have been embraced.
+We enhanced our previous dataset with a richer ontology and we show how we published our results following the 5-star model for Linked Data.
 \end{abstract}
@@
 \section{The Dataset}
-% Describe how you recasted the dataset(s) of the previous assignment to the new
-% ontology (perhaps you found other datasets that you want to add). What did it
-% take to do this? What metadata have you published alongside the dataset, and how
-% did you generate it? (Provenance, VOID, etc.) Describe how your data meeds the 5
-% star model for Linked Data.
+% Describe how you recasted the dataset(s) of the previous assignment to the new ontology (perhaps you found other datasets that you want to add).
+What did it take to do this?
+What metadata have you published alongside the dataset, and how did you generate it?
+(Provenance, VOID, etc.) Describe how your data meeds the 5 star model for Linked Data.
 Once again, the three datasets have been converted to a linked data format, now using the second version of the ontology in a straightforward way.
@@
 Each of the three datasets has been published with its companion VoID dataset, describing the contents of the dataset it refers to.
-Most of the metrics and metadata have been generated using \textbf{rdflib}'s \texttt{generateVoID}
-method applied on the three graphs.
-Moreover we publish a VoID Linkedset that links together the three datasets as a
-new one. Alongside this we provide some additional metadata from the
-\texttt{void:}\footnote{\url{http://rdfs.org/ns/void#}} ontology, such as
-\texttt{target}, \texttt{sparqlEndpoint} and
-\texttt{exampleResource} and from the
-\texttt{dcterms:}\footnote{\url{http://purl.org/dc/terms/}} ontology, such as
-\texttt{subject}, \texttt{title} and
-\texttt{description}. Those additional metadata have been added manually
-to the VoID dataset. The \texttt{void:Linkset} can be retrieved at the following
-URL \url{http://data.krw.d2s.labs.vu.nl/doc/group6/findaslot/resource/findaslot/void}.
+Most of the metrics and metadata have been generated using \textbf{rdflib}'s \texttt{generateVoID} method applied on the three graphs.
+Moreover we publish a VoID Linkedset that links together the three datasets as a new one.
+Alongside, we provide some additional metadata from the \texttt{void:}\footnote{\url{http://rdfs.org/ns/void#}} ontology -such as \texttt{target}, \texttt{sparqlEndpoint} and \texttt{exampleResource}- and from the \texttt{dcterms:}\footnote{\url{http://purl.org/dc/terms/}} ontology -such as \texttt{subject}, \texttt{title} and \texttt{description}.
+Those additional metadata have been added manually to the VoID dataset.
+The \texttt{void:Linkset} can be retrieved at the following URL \url{http://data.krw.d2s.labs.vu.nl/doc/group6/findaslot/resource/findaslot/void}.
 
 \subsection{5-star Open Data}
-We say that the published database is conform with standards proposed by the
-5-star model for Linked Data \cite{janowicz2014five}. Here we defend our statement by taking each of the
-five steps into consideration.
+We say that the published database meets the standards proposed by the 5-star model for Linked Data \cite{janowicz2014five}.
+Here we defend our statement by taking each of the five steps into consideration.
 
 \begin{description}
-\item[Available on the Web] We published our data under an open license,
-namely the CC0 1.0 Universal (this is declared in the VoID metadata).
-\item[Available as structured data] The dataset is available in RDF
-format which is structured.
-\item[Available as non-proprietary format] Again, our dataset is specified
-in a W3C language so it is not in a proprietary format but in an
-open and standardized format.
-\item[Use URIs to denote things] We use URIs to denote everything that is
-not an RDF Literal. Events, Venues, Locations and starting from this version of
-the ontology we include countries, cities and boroughs as resources defined by
-URIs.
-\item[Link to other data] We provide external pointers to resources from
-DBpedia such as for cities (e.g. \texttt{dbr:Amsterdam}), countries (e.g.
+\item[Available on the Web] We published our data under an open license, namely the CC0 1.0 Universal (this is declared in the VoID metadata).
+\item[Available as structured data] The dataset is available in RDF format which is structured.
+\item[Available as non-proprietary format] Our dataset is specified in a W3C language so it is not in a proprietary format but in an open and standardized format.
+\item[Use URIs to denote things] We use URIs to denote everything that is not an RDF Literal.
+Events, Venues, Locations and, starting from this version of the ontology, we include countries, cities and boroughs as resources defined by URIs.
+\item[Link to other data] We provide external pointers to resources from DBpedia such as for cities (e.g.
+\texttt{dbr:Amsterdam}), countries (e.g.
 \texttt{dbr:Netherlands}) or as \texttt{dcterms:subject}, in the VoID
@@
 
-\section{Section 7 - Evaluation}
+\section{Evaluation}
 For evaluating our ontology we got inspired by the work of Hlomani and Stacey \cite{hlomani2014approaches} on ontology evaluation and decided to evaluate our ontology using three major criterion:
 \begin{enumerate}
-	\item \textbf{Task-based Evaluation}. First of all we perform a task-based evaluation that typically evaluates how effective our ontology is in the context of an application.
+	\item \textbf{Task-based Evaluation}.
+First of all we perform a task-based evaluation that typically evaluates how effective our ontology is in the context of an application, using the list of Requirements from Section \ref{requirements} to do so.
 	\item \textbf{User-based Evaluation}.
@@
 Contrary to task-based evaluation, we are not accessing semantic validity and consistency of our ontology but we focus on the subjective information of it.
-	\item \textbf{Data-driven evaluation}. In the last part of this section we focus on evaluating our ontology by comparing it, with existing data about the domain it models.
+	\item \textbf{Data-driven evaluation}. In the last part of this section we focus on evaluating our ontology by comparing it with existing data about the domain it models.
 \end{enumerate}
@@
 \begin{enumerate}
-	\item \textbf{Search by interest}.
-	With the extension of our ontology we succeed in extending our application.
+	\item \textbf{Search by interest:} With the extension of our ontology we succeed in extending our application.
 We have enabled the search by interests, as we initially divide Events and Venues with regard to personal interest.
-This way the users can narrow down their search avoiding nonessential information.
+This way the users can narrow down their search avoiding non-essential information.
 
-	\item \textbf{Search by Borough}.
-Another main aspect that adds to the improvement of our ontology are the detailed location information that the users have.
-Now the users have the ability to search for Venues and Parking Slots in same Borough in a simple way.
+	\item \textbf{Search by area:} Another main aspect that adds to the improvement of our ontology is the detailed location information that users have access to.
+Now, users have the ability to search for Venues and Parking Slots in same Borough in a simple way.
 
-	\item \textbf{Capacity of Parking Slots}.
-We also provide with explicit information about each Parking Slot that is close to the interests of the user.
-Users now have prior knowledge regarding the capacity of the parking spot they need.
+	\item \textbf{Capacity of Parking Slots:} We also provide with explicit information about each Parking Slot that is close to the interests of the user.
+Users now have prior knowledge regarding the capacity of the parking spot they need, increasing their chances of finding an available slot.
 \end{enumerate}
@@
 \subsection{User-based Evaluation}
-For our user-based evaluation we simply examined our dataset as a \textit{third user}.
-The source and the meta data that have been added with the void ontology provide with important information, no only on each of the three datasets separately but on the dataset as a whole.
-\textit{Labels}, \textit{descriptions} and important \textit{metrics}, such as the total number of triples that exist in each dataset are only some of the meta-data information that have been added.
-However the risk with the specific way of evaluation, is that it is difficult to establish objective standards as it depends on the different type of users involved.
+For our user-based evaluation we simply examined our dataset as a \textit{third party user}.
+The source and the metadata that have been added with the void ontology provide with important information, not only on each of the three datasets separately but on the integrated dataset as a whole.
+\textit{Labels}, \textit{descriptions} and important \textit{metrics}, such as the total number of triples that exist in each dataset are only some of the metadata information that have been added.
+This way, a third party user is able to get information about our ontology directly, without having to query it himself, thus making our ontology an easy one to use by fellow ontology designers and developers.
 
@@
 
-With the addition of Borough as a key feature of Location, the data can be combined in a more efficient way, increasing the total efficiency of our web application even further.Besides efficiency, we wanted to check how well our ontology \textit{fits the domain knowledge} \cite{brewster2004data}.
+With the addition of Borough as a key feature of Location, the data can be combined in a more efficient way, increasing the total efficiency of our web application even further.
+Besides efficiency, we wanted to check how well our ontology \textit{fits the domain knowledge} \cite{brewster2004data}.
 
-This was done by comparing ontology concepts derived from the three separate datasets that we used in milestone 1, with the latest version of our dataset. 
-So far our ontology fits the domain knowledge of the three datasets, perfectly, however we realistically acknowledge the fact that there is certainly room for further improvement in the general domain of Events and Parking Slots.
+This was done by comparing ontology concepts derived from the three separate datasets that we used in Milestone 1, with the latest version of our dataset.
+So far our ontology perfectly fits the domain knowledge of Handicap Parking Spots in Amsterdam, given by the three chosen datasets; however we acknowledge that there is certainly room for further improvement in the general domain of Events and Parking Slots.
 
 \section{Discussion}
-\textit{Here you summarize the preceding sections, describe the lessons learnt and discuss future work.}
-Ontology may be too specific regarding domains and ranges of Object Properties. For example, if a :Location is not related to a Borough, then we will not recognize it as a :Location entity.
+%\textit{Here you summarize the preceding sections, describe the lessons learnt and discuss future work.}
+In this paper we provided a detailed description of the improved ontology that we have published about three datasets related to the city of Amsterdam.
+Moreover we show the methodology that we adopted and how this led our ontology to be classified as fully conform with the 5-star model for Linked Data.
+
+Being conform to this model for Open Data means that publishers will ultimately have a dataset that is easily \textit{surfable} and \textit{connected} to other Web resources, generating more incoming traffic towards the dataset and increasing the value of the contained data.
+The 5-star model is a way to introduce sources of \textit{trust} in both the data and publishers' spaces.
+In particular we have found the set of propositions offered by the VoID framework to be very useful and powerful.
+Furthermore, we got experience on how easy it is to define \textit{discoverable} ontologies using Web standards.
 

### 2016-05-07 milestone3/paper/paper.tex
copy vocab

%%%%%%%%%%%%%%%%%%%%%%% file moduleX_template.tex %%%%%%%%%%%%%%%%%
%
%
% This is a template for creating your papers for the course KRW
% It is based on the standard Latex template for Springer publications
% but contains a suggestion for the structure and some content of the
% paper.
%
% Please adapt this document wherever needed.
%
% For more information about the required Latex Style check the document
% typeinst.pdf in the StyleFiles directory.
%
%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%

\documentclass[runningheads,a4paper]{StyleFiles/llncs}

\usepackage{url}
\usepackage{graphicx}
\usepackage{amssymb}

\newcommand{\keywords}[1]{\par\addvspace\baselineskip
\noindent\keywordname\enspace\ignorespaces#1}

\begin{document}

\mainmatter  % start of an individual contribution

% first the title is needed
\title{Ontology Matching Paper}

% a short form should be given in case it is too long for the running head
\titlerunning{Ontology Matching Paper}

% the name(s) of the author(s) follow(s) next
%
% NB: Chinese authors should write their first names(s) in front of
% their surnames. This ensures that the names appear correctly in
% the running heads and the author index.
%
\author{Names}
%
\authorrunning{Put your names here}
% (feature abused for this document to repeat the title also on left hand pages)

% the affiliations are given next; don't give your e-mail address
% unless you accept that it will be published
\institute{\url{first@email.nl} \and \url{second@email.nl}}

\maketitle

\begin{abstract}
The abstract should summarize the contents of the paper and should
contain at least 70 and at most 150 words. It should be written using the
\emph{abstract} environment.
\end{abstract}

\section{Introduction}
%Introduce the sections that follow. What is the problem this paper addresses? What is the core contribution of this paper, and why is that interesting? What method did you develop and implement? What is the research question or hypothesis this paper answers? How did you answer this question or validate your approach (empirically, analytically). You might want to give a brief (qualitative) sketch of the results. 
- ontology matching is important because equivalence allows collaboration

\section{Related Work}
%Give here an overview over related matching methods and how they related to your own solution. Cite papers that might have inspired your approach. Sometimes it makes sense to have this section immediately after the introduction.
- Tools are out of date
- http://www.iro.umontreal.ca/~owlola/index.html

- WordNet:Similarity http://maraca.d.umn.edu/cgi-bin/similarity/similarity.cgi

\section{Methods, Algorithms and Implementation}
% Introduce your method, i.e. the overall approach taken and the general idea, the algorithms in general, maybe in pseudo-code and give a quick overview over the technical implementations (not too much details).

% Maybe you want to separate this part into subsections for your two systems
\subsection{Ontology Matching}
\subsection{Data Linkage}

\section{Validation and Experiments}
% In a scientific paper you want to show that your choice of method and algorithms was the right choice. So, this could be a place where you make claims or ask concrete and explicit research questions (e.g. with respect to runtime and/or precision/recall.

\section{Results and Discussion}
% Give here details about the most important results of your experiments. Use tables and figures, but focus on the interesting and important results. Make sure you describe in the text what the reviewers should see, explain what the reader sees in the tables and point to the interesting findings. Be explicit about your research question and hypothesis, and discuss they might be true, or false.

\section{Conclusion}
%Here you summarize the preceding sections, describe the lessons learnt and discuss future work.

\bibliographystyle{plain}
\bibliography{mybib}

\end{document}

### 2016-05-07 milestone3/convert-datasets.py
fixed stuff in ontology and convert script [mls3]

@@ -1,0 +1,293 @@
+#!/usr/bin/env python
+
+import json
+from datetime import datetime
+from rdflib import Dataset, Graph, URIRef, Literal, Namespace, RDF, RDFS, OWL, XSD
+from iribaker import to_iri
+import requests
+from SPARQLWrapper import SPARQLWrapper, JSON
+from pprint import pprint
+
+
+resource = 'http://data.krw.d2s.labs.vu.nl/group6/findaslot/resource/'
+RESOURCE = Namespace(resource)
+vocab = 'http://data.krw.d2s.labs.vu.nl/group6/findaslot/vocab/'
+VOCAB = Namespace(vocab)
+geo = 'http://www.w3.org/2003/01/geo/wgs84_pos#'
+GEO = Namespace(geo)
+dbo = 'http://dbpedia.org/ontology/'
+DBO = Namespace(dbo)
+dbr = 'http://dbpedia.org/resource/'
+DBR = Namespace(dbr)
+
+repo_url = "http://stardog.krw.d2s.labs.vu.nl/group6"
+
+VOCAB_FILE = 'vocab_v3.ttl'
+SOURCE_DATA_DIR = '../source_datasets/'
+OUTPUT_DIR = 'data/'
+
+
+def convert_dataset(path, dataset, graph_uri, museums=True):
+    f = open(path, 'r')
+    json_data = json.load(f)
+
+    graph = dataset.graph(graph_uri)
+    country = URIRef(to_iri(dbr + 'Kingdom of the Netherlands'))
+
+    for event_data in json_data:
+        event = URIRef(to_iri(resource + event_data['title'].strip()))
+        title = Literal(event_data['title'].strip(), datatype=XSD['string'])
+
+        dates = event_data['dates']
+        if dates != []:
+            single_dates = [Literal(datetime.strptime(d, '%d-%m-%Y').date())
+                for d in dates['singles']] if dates.has_key('singles') else []
+            start_date = Literal(datetime.strptime(dates['startdate'], '%d-%m-%Y').date()) \
+                if dates.has_key('startdate') else None
+            end_date = Literal(datetime.strptime(dates['enddate'], '%d-%m-%Y').date()) \
+                if dates.has_key('enddate') and dates['enddate'] != '' else None
+
+        location_dict = event_data['location']
+        location_d_name = location_dict['name'].strip()
+        if location_d_name != '':
+            place = URIRef(to_iri(resource + location_d_name))
+            place_name = Literal(location_d_name, datatype=XSD['string'])
[…]

### 2016-05-07 milestone3/paper/paper.tex
intro

@@
 %
-\author{Names}
+\author{Alivanistos, Dimitris. \\ Baez, Selene. \\ Jemmett, Andrea.}
 %
-\authorrunning{Put your names here}
+\authorrunning{Alivanistos, Dimitris. \\ Baez, Selene. \\ Jemmett, Andrea.}
 % (feature abused for this document to repeat the title also on left hand pages)
@@
 % unless you accept that it will be published
-\institute{\url{first@email.nl} \and \url{second@email.nl}}
+\institute{\url{d.alivanistos@student.vu.nl} \and \url{s.baezsantamaria@student.vu.nl} \and \url{a.jemmett@student.vu.nl}}
 
@@
 You might want to give a brief (qualitative) sketch of the results.
-- ontology matching is important because equivalence allows collaboration
+In this paper we continue the work related for creating an application for finding Handicap Parking Spots close to Event Venues in Amsterdam.
+In the previous paper, we improved on the ontology to comply with the Five Star model and linked it to other existing ontologies.
+In this paper, we continue the work by matching and aligning the ontology to other subject-related ontologies.
+
+In general, the problem of matching ontologies has been studied before by Semantic Web researchers.
+As Shvaiko et al.
+state, the problem of heterogeneity is still a challenge to be solved since ambiguity in meanings and interpretations prevent from finding equivalences in same domain ontologies \cite{shvaiko2013ontology}.
+Ontology matching and alignment allow to merge, translate, and extend ontologies, finding correspondences both in entities and instances.
+
+With that in mind, in this paper we select relevant vocabularies from the pool of Amsterdam related ontologies in our class.
+After some comparison we selected groups 10, 13 and 15.
+Group 10 presents a vocabulary for cultural activities, Group 13 presents an ontology about safety for tourists using statistical area information; finally, Group 15 present an ontology for general activity finding.
+
+In the following sections we revise existing tools for matching and aligning ontologies. We proceed to use some tools for matching and aligning our ontology to the aforementioned vocabularies.
+
+- We use SILK, which provides visual tools for matching and alignment. 
+- Research question: Investigate the state-of-the-art tools, use them to match ontologies related to recreation in Amsterdam, and evaluate its performance.
+
+Try several matching algorithms, with different transformations and comparators.
 
@@
 Sometimes it makes sense to have this section immediately after the introduction.
+- Tried several tools from \cite{ai3:::adaptiveinformation_2014} and \cite{euzenat2007ontology}
+
+\begin{enumerate}
+	\item OLA : Out of date \cite{euzenat2004ontology}
+	\item S-Match: Cannot read RDF files
+	\item MapONTO: Old version of Protege
+	\item AML
+\end{enumerate}
+
 - Tools are out of date
@@
 \section{Methods, Algorithms and Implementation}
-% Introduce your method, i.e.
-the overall approach taken and the general idea, the algorithms in general, maybe in pseudo-code and give a quick overview over the technical implementations (not too much details).
+% Introduce your method, i.e. the overall approach taken and the general idea, the\bibliography{paper}
+ algorithms in general, maybe in pseudo-code and give a quick overview over the technical implementations (not too much details).
 

### 2016-05-07 milestone3/paper/paper.tex
more stuff

@@
 As Shvaiko et al.
-state, the problem of heterogeneity is still a challenge to be solved since ambiguity in meanings and interpretations prevent from finding equivalences in same domain ontologies \cite{shvaiko2013ontology}.
-Ontology matching and alignment allow to merge, translate, and extend ontologies, finding correspondences both in entities and instances.
+state, the problem of heterogeneity is still a challenge to be solved since ambiguity in meanings and interpretations prevent us from finding equivalences in same domain ontologies \cite{shvaiko2013ontology}.
+Ontology matching and alignment allow to merge, translate, and extend ontologies, finding correspondences both in entities, properties and instances.
+The Ontology Alignment Evaluation Initiative is an annual international competition that serves as an evaluation for state of the art alignment tools.
 
 With that in mind, in this paper we select relevant vocabularies from the pool of Amsterdam related ontologies in our class.
-After some comparison we selected groups 10, 13 and 15.
-Group 10 presents a vocabulary for cultural activities, Group 13 presents an ontology about safety for tourists using statistical area information; finally, Group 15 present an ontology for general activity finding.
+After some comparison we selected Group 10 -an ontology for cultural activities-, Group 13 -an ontology about safety for tourists using statistical area information-, and Group 15 -an ontology for general activity finding.
 
-In the following sections we revise existing tools for matching and aligning ontologies. We proceed to use some tools for matching and aligning our ontology to the aforementioned vocabularies.
-
-- We use SILK, which provides visual tools for matching and alignment. 
-- Research question: Investigate the state-of-the-art tools, use them to match ontologies related to recreation in Amsterdam, and evaluate its performance.
-
-Try several matching algorithms, with different transformations and comparators.
+In the following sections we first revise existing tools for matching and aligning ontologies.
+Then we select and apply tools for matching and aligning our ontologies to the aforementioned ones, experimenting with different comparators.
+We continue to evaluate such algorithms and discuss the results.
+Finally, we conclude by summarizing the findings of the alignment to different ontologies.
 
@@
 Sometimes it makes sense to have this section immediately after the introduction.
-- Tried several tools from \cite{ai3:::adaptiveinformation_2014} and \cite{euzenat2007ontology}
+In order to match our ontology to others, we did research about state of the art matching and alignment tools.
+\cite{adaptiveInformation_2014} is a comprehensive list of the top 50 tools, separating active from inactive tools.
+Additionally, we looked at some of the tools revised by Euzenat et Al \cite{euzenat2007ontology}.
+Furthermore, we looked at the participants from the most recent OAEI.
+
+In the following we list the most relevant tools.
 
 \begin{enumerate}
-	\item OLA : Out of date \cite{euzenat2004ontology}
+	\item \textbf{OLA \cite{euzenat2004ontology}:} Developed in 2004, the OWL Lite Alignment (OLA) is a tool for automatic matching of ontologies that implements the OLA algorithm designed in collaboration by the DIRO, University of Montréal and INRIA Rhône Alpes.
+It participated in OEIA 2005 \cite{euzenat2005ola} and 2007 \cite{djoufak2007ola} and increased its own results from 0.80 to 0.89 in Precision, and 0.74 to 0.87 in Recall.
+At the time, it was one of the pioneers of ontology matching, yet no it is nowadays outdated.
+
 	\item S-Match: Cannot read RDF files
 	\item MapONTO: Old version of Protege
+	\item WordNet:Similarity: http://maraca.d.umn.edu/cgi-bin/similarity/similarity.cgi
 	\item AML
 \end{enumerate}
-
-- Tools are out of date
-- http://www.iro.umontreal.ca/~owlola/index.html
-
-- WordNet:Similarity http://maraca.d.umn.edu/cgi-bin/similarity/similarity.cgi
 
@@
 \subsection{Ontology Matching}
+- Decided to use one of the best candidates in the OAEI of 2014, AML (AgreementMakerLight) the best system (as measured in terms of F-measure) for lightweight ontologies.
+The reasons behind this choice was that AML exceeded our expectations with regard to run time results, comprehensive user interface and integrated evaluation mechanism.
+The procedure can be fully or semi automatic, with the user being presented to a fully customizable matching.
+We can choose between different metrics with respect to structure,content etc
+-examples with pictures, String Matcher, Word matcher, Property matcher, Cardinality matcher and background knowledge matcher.
+
+\begin{figure}[h]\centering
+	\includegraphics[width=.75\textwidth]{img/match_city.png}
+	\caption{Visual representation of a single correct match in AML.}
+	\label{fig:single_match}
+\end{figure}
+\begin{figure}[h] \centering
+	\includegraphics[width=.75\textwidth]{img/match_combo.png}
+	\caption{Visual representation of multiple correct matches in AML.}
+	\label{fig:multiple_match}
+\end{figure}
+\begin{figure}[h] \centering
+	\includegraphics[width=.75\textwidth]{img/conflict_exhibition_exposition.png}
+	\caption{Visual representation of an incorrect match in AML.}
+	\label{fig:incorrect_match}
+\end{figure}
+
 \subsection{Data Linkage}

### 2016-05-07 milestone3/paper/paper.tex
report structure and added pics

@@
 At the time, it was one of the pioneers of ontology matching, yet no it is nowadays outdated.
-
-	\item S-Match: Cannot read RDF files
-	\item MapONTO: Old version of Protege
-	\item WordNet:Similarity: http://maraca.d.umn.edu/cgi-bin/similarity/similarity.cgi
-	\item AML
+	\item \textbf{S-Match \cite{giunchiglia2004s}:} S-Match is a semantic matching tool that is suitable for many applications.
+However, it is not specific for ontology matching and it has not participated in the latest OAEI.
+	\item \textbf{MapONTO \cite{an2004refining}:} MapOnto, just as S-Match, is a general purpose semantic matcher.
+It is an Initiative from the University of Toronto and it is implemented as a plug-in for Protege.
+At first sight, this option seemed promising, however the latest release is compatible with obsolete versions of Protege.
+	%\item \textbf{WordNet:Similarity \cite{pedersen2004wordnet}:} Semantic 
+	\item \textbf{AML \cite{faria2013agreementmakerlight}:} The Agreement
+	Maker Light (AML) is the improved version of the original Agreement Maker.
+It is a simple, user-friendly application for matching ontologies which also provides visualization and evaluation of the alignment.
+Further details will be discussed in Section \ref{Ontology_Matching}.
 \end{enumerate}
@@
 \subsection{Ontology Matching}
+\label{Ontology_Matching}
 - Decided to use one of the best candidates in the OAEI of 2014, AML (AgreementMakerLight) the best system (as measured in terms of F-measure) for lightweight ontologies.
@@
 
+\subsection{Group 10: Cultural Ontology}
+We match to the main entities of Events and Venues.
+
+\begin{figure}[h]\centering
+	\includegraphics[width=.75\textwidth]{img/match_g10.png}
+	\caption{Matching to group 10}
+	\label{fig:match_g10}
+\end{figure}
+
+\subsection{Group 13: Tourist safety Ontology}
+
+\subsection{Group 15: Activity finding Ontology}
+Six correct matchings versus six incorrect matchings
+
+\begin{figure}[h]\centering
+	\includegraphics[width=.75\textwidth]{img/match_g15.png}
+	\caption{Matching to group 15}
+	\label{fig:match_g15}
+\end{figure}
+
 \section{Results and Discussion}
@@
 Be explicit about your research question and hypothesis, and discuss they might be true, or false.
+- Led to ? 98\%  name comparison 99\% class comparison 100\%
+
+- Intuitively, our ontology should have had more matches with group 10, since they model the exact same datasets as we do.
+However, they model the details of events as Entities, while we do it as Properties.
+To the best of our knowledge, AML cannot match entities to properties.
+This discovery raises more serious questions since the limitations of matching are evident when design decisions like the ones in this case rigidly prevent matches.
+
+- Matches to ill formed ontologies are hard to predict. For example, Group 15 has two Venues entities which are matched to our single Venue entity in a cyclic way.
 
@@
 %Here you summarize the preceding sections, describe the lessons learnt and discuss future work.
+- 
+- Note: the field is messy and outdated tools are often referred.
 

### 2016-05-08 milestone3/paper/paper.tex
data linking paper stuff

@@
 \subsection{Data Linkage}
+In this section the developed Data Linkage system is presented.
+It interlinks our dataset with two other datasets from groups 13 and 15. We
+decided to implement the linking workflow and procedures using the
+\textit{Silk framework}\footnote{\url{http://silkframework.org/}} which captions
+itself as ``The Linked Data Integration Framework''. Silk is an open source
+project for integrating heterogeneous data sources and among its use cases is
+generating links between Linked Data sources, which is exactly within our needs.
+Moreover Silk provides the user with a nice and friendly Web-based GUI and a visual
+editor for linkage rules.
+
+To link two Linked Datasets using Silk first we need to define their sources,
+e.g. using a SPARQL endpoint or uploading an RDF dump. Then it is possible to
+create linkage rules by applying four different kind of operations:
+\begin{enumerate}
+	\item path-like queries to retrieve values;
+	\item transformations over those values (e.g. to-lowercase, tokenization);
+	\item comparators over values (e.g. Levenshtein distance, Jaccard
+		coefficient, equality);
+	\item aggregators over comparators output (e.g. average, minimum, maximum).
+\end{enumerate}
+It is also possible to specify a threshold for the comparator's output score,
+its weight when computing an aggregation for it or whether it is required that a
+value exists for that block\footnote{We say block because Silk uses a visual
+editor with block-shaped functionalities.}.
+
+\subsubsection{Linking the Cultural Dataset}
+This dataset has a domain in part similar to our so the linking procedure
+is trivial and reduces to a check on the \texttt{rdfs:label} and some other
+property. An example Silk linkage rule is shown in Figure \ref{fig:link_event_g10}
+that matches events; in this case the match is checked against
+\texttt{rdfs:label} and \texttt{dc:title}.
+%TODO link other entities
+
+\begin{figure}[h]
+	\centering
+	\includegraphics[width=1\textwidth]{img/link_event_g10.png}
+	\caption{Silk linkage rules for events in group 10's dataset.}
+	\label{fig:link_event_g10}
+\end{figure}
+
+\subsubsection{Linking the Tourist Safety Dataset}
+In spite being about a different domain, this dataset can still be linked with
+ours for what concerns events and locations / venues. Indeed the overlap between
+events in this dataset and ours is big and we are able to match a big proportion
+of entities by using a linkage rule similar to that shown in Figure
+\ref{fig:link_event_g10} but using \texttt{rdfs:label} for both data sources.
+
+\subsubsection{Linking the Activity Finding Dataset}
+For events the linkage rule is less trivial and immediate than that for the
+Cultural Dataset and involves the use of more properties and an aggregator as
+shown in Figure \ref{fig:link_event_g15}.
+
+\begin{figure}[h]
+	\centering
+	\includegraphics[width=1\textwidth]{img/link_event_g15.png}
+	\caption{Silk linkage rule for events in the Activity Finding Dataset.
+		\texttt{sourcePath2} contains
+		\texttt{/schema:location/schema:streetAddress} while
+		\texttt{targetPath2} contains
+		\texttt{/g6v:hasVenue/dbo:location/dbo:address}.}
+	\label{fig:link_event_g15}
+\end{figure}
 

### 2016-05-08 milestone3/paper/paper.tex
Matching part done. Abstract missing

@@
 \section{Related Work}
+\label{related_work}
 %Give here an overview over related matching methods and how they related to your own solution.
@@
 \section{Methods, Algorithms and Implementation}
-% Introduce your method, i.e. the overall approach taken and the general idea, the\bibliography{paper}
- algorithms in general, maybe in pseudo-code and give a quick overview over the technical implementations (not too much details).
+% Introduce your method, i.e.
+the overall approach taken and the general idea, the\bibliography{paper} algorithms in general, maybe in pseudo-code and give a quick overview over the technical implementations (not too much details).
+With the results from our Related Work research, we selected AML for ontology matching and SILK for ontology alignment.
+The similarity measures applied for both of the above were studied from \cite{sun2015comparative}.
 
@@
 \label{Ontology_Matching}
-- Decided to use one of the best candidates in the OAEI of 2014, AML (AgreementMakerLight) the best system (as measured in terms of F-measure) for lightweight ontologies.
-The reasons behind this choice was that AML exceeded our expectations with regard to run time results, comprehensive user interface and integrated evaluation mechanism.
+Looking at the most recent OAEI results, we decided to use one of the best candidates in the OAEI of 2014: AML.
+This tool performed the best for lightweight ontologies, as measured in terms of F-measure.
+The reasons behind this choice are that AML exceeded our expectations with regard to run time results, comprehensive user interface and integrated evaluation mechanism.
 The procedure can be fully or semi automatic, with the user being presented to a fully customizable matching.
-We can choose between different metrics with respect to structure,content etc
--examples with pictures, String Matcher, Word matcher, Property matcher, Cardinality matcher and background knowledge matcher.
+A lexical matching is always performed, followed by other metrics the user can choose from, ranging from structure to content based and others.
+Furthermore, AML provides with visualizations for the matches as shown in Figure \ref{fig:single_match}, \ref{fig:multiple_match} and \ref{fig:incorrect_match}.
+%examples with pictures, String Matcher, Word matcher, Property matcher, Cardinality matcher and background knowledge matcher.
 
 \begin{figure}[h]\centering
-	\includegraphics[width=.75\textwidth]{img/match_city.png}
+	\includegraphics[width=.8\textwidth]{img/match_city.png}
 	\caption{Visual representation of a single correct match in AML.}
 	\label{fig:single_match}
-\end{figure}
-\begin{figure}[h] \centering
-	\includegraphics[width=.75\textwidth]{img/match_combo.png}
+%\end{figure}
+%\begin{figure}[h] \centering
+	\includegraphics[width=.8\textwidth]{img/match_combo.png}
 	\caption{Visual representation of multiple correct matches in AML.}
 	\label{fig:multiple_match}
-\end{figure}
-\begin{figure}[h] \centering
-	\includegraphics[width=.75\textwidth]{img/conflict_exhibition_exposition.png}
+%\end{figure}
+%\begin{figure}[h] \centering
+	\includegraphics[width=.8\textwidth]{img/conflict_exhibition_exposition.png}
 	\caption{Visual representation of an incorrect match in AML.}
@@
 \end{figure}
+
+The power of AML is shown as its ability to combine different types of matchers, in a hierarchical or concurrent manner.
+Our method was to test each matcher separately in order to study the results obtained, while in a later stage we experimented with different combination of matching (i.e.
+Word matching, String matching and Structural matching).
+Furthermore, AML also allows the user to customize the settings of the matchers.
+For example, regarding String matcher it gives the option to choose between four different similarity measures: iSub, Levenstein, Jaro-Winkler and Q-gram, as described by Sun et al.
+\cite{sun2015comparative}.
 
@@
 with respect to runtime and/or precision/recall.
+We conducted a variety of experiments regarding the matching of our ontology (consisting of 16 classes, 24 properties and 6 individuals) to others. This was made possible by how customizable AML is.
+
+We tried different similarity measures for String and Word matching as well as different filters regarding cardinality and coherence.
+Results mostly remained unchanged, and we believe this is due to the limited size and complexity of the ontologies presented.
+However, it is worth mentioning that strict, permissive and hybrid cardinality filters had a significant impact on the resulting alignment.
+For example, with regards to the matching with group 15, hybrid or permissive filters matched our Event class with 3 different classes of their ontology while with strict filter, we got a single match.
+
+AML also has the ability to evaluate a certain match with respect to a reference match.
+This gives the option to the end user to manually force or evaluate the match and thus supervise and validate the final match.
+As so, the user can match classes or properties by hand and use the corrected match as reference for future matchings.
+
+Hereby we report the results for the best matched alignments to the three selected ontologies.
+Basic characteristics for the ontologies, as well as a visualization of the matching in AML are given for each case.
 
 \subsection{Group 10: Cultural Ontology}
-We match to the main entities of Events and Venues.
+This ontology consists of 11 classes, 23 properties, 1 individual. Our ontology matches to their main entities of Events and Venues.
 
 \begin{figure}[h]\centering
-	\includegraphics[width=.75\textwidth]{img/match_g10.png}
+	\includegraphics[width=.7\textwidth]{img/match_g10.png}
 	\caption{Matching to group 10}
@@
 
+AML found two mappings leading to the following evaluation metrics:
+
+\begin{center}
+	\begin{tabular}{| c | c | c |}
+		\hline
+		\textbf{Precision} & \textbf{Recall} & \textbf{F-measure} \\ \hline
+		100\% & 100\% & 100\% \\ \hline
+	\end{tabular}
+\end{center}
+
 \subsection{Group 13: Tourist safety Ontology}
+This ontology consists of 16 classes, 20 properties, 973 individuals. We matched Events, Location, City as well as Start and End date. The entity for Country was mistakenly matched to the Area entity.
+
+\begin{figure}[h]\centering
+	\includegraphics[width=.7\textwidth]{img/match_g13.png}
+	\caption{Matching to group 13}
+	\label{fig:match_g13}
+\end{figure}
+
+AML found 6 mappings, leading to the following evaluation metrics:
+
+\begin{center}
+	\begin{tabular}{| c | c | c |}
+		\hline
+		\textbf{Precision} & \textbf{Recall} & \textbf{F-measure} \\ \hline
+		83.3\% & 100\% & 90.9\% \\ \hline
+	\end{tabular}
+\end{center}
 
 \subsection{Group 15: Activity finding Ontology}
-Six correct matchings versus six incorrect matchings
+In this case, the target ontology consists of 66 classes, 599 properties and 57 individuals. This is, by far, a larger ontology than ours and the previous examined ontologies.
 
 \begin{figure}[h]\centering
-	\includegraphics[width=.75\textwidth]{img/match_g15.png}
+	\includegraphics[width=.7\textwidth]{img/match_g15.png}
 	\caption{Matching to group 15}
@@
 \end{figure}
+
+AML found 12 mappings, six correct versus six incorrect matchings, leading to the following evaluation metrics:
+
+\begin{center}
+	\begin{tabular}{| c | c | c |}
+		\hline
+		\textbf{Precision} & \textbf{Recall} & \textbf{F-measure} \\ \hline
+		54.5\% & 46.2\% & 50.0\% \\ \hline
+	\end{tabular}
+\end{center}
 
@@
 Be explicit about your research question and hypothesis, and discuss they might be true, or false.
-- Led to ? 98\%  name comparison 99\% class comparison 100\%
+From the previous section we conclude that the ontology for group 13 matches the best to our ontology since it has the highest number of matches with the least number of mismatches.
+Yet, the matching only works for one of our three basic entities (Events, Venues and Parking Spots).
 
-- Intuitively, our ontology should have had more matches with group 10, since they model the exact same datasets as we do.
-However, they model the details of events as Entities, while we do it as Properties.
+Moreover, conflicting with our initial hypothesis, the matching with the group 10's ontology did not perform as well as expected.
+Intuitively, we believed that our ontology should have had more matches with this group, since they model the same datasets as we do.
+However, they model characteristics of events as Entities (such as Image, Description and Time Period), while we do it as Properties.
 To the best of our knowledge, AML cannot match entities to properties.
-This discovery raises more serious questions since the limitations of matching are evident when design decisions like the ones in this case rigidly prevent matches.
+This discovery raises more serious questions since the limitations of matching are evident when design decisions like the ones in this case rigidly prevent proper matching and alignment.
 
-- Matches to ill formed ontologies are hard to predict. For example, Group 15 has two Venues entities which are matched to our single Venue entity in a cyclic way.
+A different problem occurs in the case of the matching to the ontology of group 15.
+In this case, we found overmatching since their ontology has duplicate classes for Venue and Event.
+Therefore, several metrics failed to distinguish the duplicate match resulting in AML outputting misleading results.
+This matching required the most amount of work regarding experimenting and tuning of matching.
+As stated before, details as fine as the specific type of cardinality filter greatly affected the end result.
 
@@
 %Here you summarize the preceding sections, describe the lessons learnt and discuss future work.
-- 
-- Note: the field is messy and outdated tools are often referred.
+In this paper we matched our ontology for finding Handicap Parking Spots in Amsterdam to other ontologies related to entertainment in Amsterdam.
+We found that the match with the highest confidence corresponds to Group 10, but the match with highest overlap corresponds to Group 15 closely followed by Group 13.
+
+From the experiments performed we learned that great amount of work is invested in applying the correct similarity measures.
+
+Furthermore, our experience is backed up by the findings described in Section \ref{related_work}.
+As we see, Ontology matching is a growing field, that comes up with new promising tools every year.
+Yet, follow up is not consistent and a robust solution for automatic, or semi-automatic ontology matching has yet to be developed.
 

### 2016-05-08 milestone3/paper/paper.tex
more data linking stuff

@@
 
+In the following sections we show how we implemented a Data Linking system to
+link our dataset with three other datasets created by peers following our same
+class\footnote{Knowledge Representation on the Web at VU Amsterdam, 2015/2016}.
+Moreover we tried to look-up the Linked Open Data cloud searching for similar
+datasets that we could link to ours. We used
+LOTUS\footnote{\url{http://lotus.lodlaundromat.org/}}, a tool from the LOD
+Laundromat suite\footnote{\url{http://lodlaundromat.org/}}\cite{beek2014lod}
+that allows to search the LOD cloud for statements based on some query
+parameters. Unfortunately we were not able to find interesting datasets there.
+
 \subsubsection{Linking the Cultural Dataset}
@@
 that matches events; in this case the match is checked against
-\texttt{rdfs:label} and \texttt{dc:title}.
-%TODO link other entities
+\texttt{rdfs:label} and \texttt{dc:title}. With this rule we are able to create
+15 links over 239 source and 479 target event entities.
 
@@
 \ref{fig:link_event_g10} but using \texttt{rdfs:label} for both data sources.
+Using this linkage rule we are able to link 45 events and locations between the
+two datasets.
 
@@
 Cultural Dataset and involves the use of more properties and an aggregator as
-shown in Figure \ref{fig:link_event_g15}.
+shown in Figure \ref{fig:link_event_g15}. With this linkage rule we are able to
+link 84 activities / events.
 

### 2016-05-08 milestone3/paper/paper.tex
done body, missing abstract

@@
 % first the title is needed
-\title{Ontology Matching Paper}
+\title{Ontology Matching Paper An ontology alignment over Amsterdam (Parking spots, events and activities)}
 
@@
 state, the problem of heterogeneity is still a challenge to be solved since ambiguity in meanings and interpretations prevent us from finding equivalences in same domain ontologies \cite{shvaiko2013ontology}.
-Ontology matching and alignment allow to merge, translate, and extend ontologies, finding correspondences both in entities, properties and instances.
+Ontology matching and alignment allow to merge, translate, and extend ontologies, finding correspondences in entities, properties and instances.
 The Ontology Alignment Evaluation Initiative is an annual international competition that serves as an evaluation for state of the art alignment tools.
@@
 It participated in OEIA 2005 \cite{euzenat2005ola} and 2007 \cite{djoufak2007ola} and increased its own results from 0.80 to 0.89 in Precision, and 0.74 to 0.87 in Recall.
-At the time, it was one of the pioneers of ontology matching, yet no it is nowadays outdated.
+At the time, it was one of the pioneers of ontology matching, yet the project was abandoned and it is nowadays outdated.
 	\item \textbf{S-Match \cite{giunchiglia2004s}:} S-Match is a semantic matching tool that is suitable for many applications.
@@
 	\item \textbf{MapONTO \cite{an2004refining}:} MapOnto, just as S-Match, is a general purpose semantic matcher.
-It is an Initiative from the University of Toronto and it is implemented as a plug-in for Protege.
-At first sight, this option seemed promising, however the latest release is compatible with obsolete versions of Protege.
+It is an initiative from the University of Toronto and it is implemented as a plug-in for Protege.
+At first sight, this option seemed promising, however the latest release is only compatible with obsolete versions of Protege.
 	%\item \textbf{WordNet:Similarity \cite{pedersen2004wordnet}:} Semantic 
@@
 the overall approach taken and the general idea, the\bibliography{paper} algorithms in general, maybe in pseudo-code and give a quick overview over the technical implementations (not too much details).
-With the results from our Related Work research, we selected AML for ontology matching and SILK for ontology alignment.
+With the results from Section \ref{related_work}, we selected AML for ontology matching and SILK for ontology alignment.
 The similarity measures applied for both of the above were studied from \cite{sun2015comparative}.
@@
 Looking at the most recent OAEI results, we decided to use one of the best candidates in the OAEI of 2014: AML.
-This tool performed the best for lightweight ontologies, as measured in terms of F-measure.
-The reasons behind this choice are that AML exceeded our expectations with regard to run time results, comprehensive user interface and integrated evaluation mechanism.
+This tool performed the best for lightweight ontologies, as measured in terms of F-measure \footnote{The F-measure is the harmonic mean of Precision and Recall.}.
+AML exceeded our expectations with regards to run time results, comprehensive user interface and integrated evaluation mechanism.
 The procedure can be fully or semi automatic, with the user being presented to a fully customizable matching.
-A lexical matching is always performed, followed by other metrics the user can choose from, ranging from structure to content based and others.
+A lexical matching is always performed as default, followed by other metrics the user can choose from, ranging from structure to content based and others.
 Furthermore, AML provides with visualizations for the matches as shown in Figure \ref{fig:single_match}, \ref{fig:multiple_match} and \ref{fig:incorrect_match}.
@@
 In this section the developed Data Linkage system is presented.
-It interlinks our dataset with two other datasets from groups 13 and 15. We
-decided to implement the linking workflow and procedures using the
-\textit{Silk framework}\footnote{\url{http://silkframework.org/}} which captions
-itself as ``The Linked Data Integration Framework''. Silk is an open source
-project for integrating heterogeneous data sources and among its use cases is
-generating links between Linked Data sources, which is exactly within our needs.
-Moreover Silk provides the user with a nice and friendly Web-based GUI and a visual
-editor for linkage rules.
+It interlinks our dataset with the previously mentioned datasets from groups 10, 13 and 15.
+We decided to implement the linking workflow and procedures using the \textit{Silk framework}\footnote{\url{http://silkframework.org/}} which captions itself as ``The Linked Data Integration Framework''.
+Silk is an open source project for integrating heterogeneous data sources.
+Its use cases include generating links between Linked Data sources, which is exactly within our needs.
+Moreover Silk provides the user with a nice and friendly Web-based GUI and a visual editor for linkage rules.
 
-To link two Linked Datasets using Silk first we need to define their sources,
-e.g. using a SPARQL endpoint or uploading an RDF dump. Then it is possible to
-create linkage rules by applying four different kind of operations:
+To link two Linked Datasets using Silk first we need to define their sources, e.g.
+using a SPARQL endpoint or uploading an RDF dump.
+Then it is possible to create linkage rules by applying four different kind of operations:
 \begin{enumerate}
@@
 \end{enumerate}
-It is also possible to specify a threshold for the comparator's output score,
-its weight when computing an aggregation for it or whether it is required that a
-value exists for that block\footnote{We say block because Silk uses a visual
-editor with block-shaped functionalities.}.
+It is also possible to specify a threshold for the comparator's output score, its weight when computing an aggregation for it or whether it is required that a value exists for that block\footnote{We say block because Silk uses a visual editor with block-shaped functionalities.}.
 
@@
 
-\subsubsection{Linking the Cultural Dataset}
-This dataset has a domain in part similar to our so the linking procedure
-is trivial and reduces to a check on the \texttt{rdfs:label} and some other
-property. An example Silk linkage rule is shown in Figure \ref{fig:link_event_g10}
-that matches events; in this case the match is checked against
-\texttt{rdfs:label} and \texttt{dc:title}. With this rule we are able to create
-15 links over 239 source and 479 target event entities.
+\subsubsection{Linking Group 10: Cultural Ontology}
+This dataset has a domain similar to ours so the linking procedure
+is trivial and is reduced to a check on the \texttt{rdfs:label} combined with some other property.
+An example of a Silk linkage rule that matches Events is shown in Figure \ref{fig:link_event_g10}.
+In this case the match is checked against \texttt{rdfs:label} and \texttt{dc:title}.
+With this rule we are able to create 15 links over 239 source and 479 target event entities.
 
@@
 
-\subsubsection{Linking the Tourist Safety Dataset}
-In spite being about a different domain, this dataset can still be linked with
-ours for what concerns events and locations / venues. Indeed the overlap between
-events in this dataset and ours is big and we are able to match a big proportion
-of entities by using a linkage rule similar to that shown in Figure
-\ref{fig:link_event_g10} but using \texttt{rdfs:label} for both data sources.
-Using this linkage rule we are able to link 45 events and locations between the
-two datasets.
+\subsubsection{Linking Group 13: Tourist safety Ontology}
+In spite having a different domain, this dataset can still be linked to ours for what concerns events and locations / venues.
+Indeed the overlap between events in this dataset and ours is large.
+We are able to match a larger proportion of entities by using a linkage rule similar to that shown in Figure\ref{fig:link_event_g10} but using \texttt{rdfs:label} for both data sources.
+Using this linkage rule we are able to link 45 events and locations between the two datasets.
 
-\subsubsection{Linking the Activity Finding Dataset}
-For events the linkage rule is less trivial and immediate than that for the
-Cultural Dataset and involves the use of more properties and an aggregator as
-shown in Figure \ref{fig:link_event_g15}. With this linkage rule we are able to
-link 84 activities / events.
+\subsubsection{Linking Group 15: Activity finding Ontology}
+\label{link_g15}
+This time the linkage rule for events is less trivial and immediate than that for the previous two datasets.
+As such, it involves the use of more properties and an aggregator as shown in Figure \ref{fig:link_event_g15}.
+With this linkage rule we are able to link 84 activities / events.
 
@@
 AML also has the ability to evaluate a certain match with respect to a reference match.
-This gives the option to the end user to manually force or evaluate the match and thus supervise and validate the final match.
+This gives the option for the end user to manually force or evaluate the match and thus supervise and validate the final match.
 As so, the user can match classes or properties by hand and use the corrected match as reference for future matchings.
 
-Hereby we report the results for the best matched alignments to the three selected ontologies.
+Hereby we report the results of evaluating the automatic matching procedure, as performed by AML, with the human validated alignment for the three selected ontologies.
 Basic characteristics for the ontologies, as well as a visualization of the matching in AML are given for each case.
@@
 \subsection{Group 10: Cultural Ontology}
-This ontology consists of 11 classes, 23 properties, 1 individual. Our ontology matches to their main entities of Events and Venues.
+This ontology consists of 11 classes, 23 properties, 1 individual.
+Our ontology matches to their main entities of Events and Venues.
+A visualization of the matching is presented in Figure \ref{fig:match_g10}.
 
@@
 \subsection{Group 13: Tourist safety Ontology}
-This ontology consists of 16 classes, 20 properties, 973 individuals. We matched Events, Location, City as well as Start and End date. The entity for Country was mistakenly matched to the Area entity.
+This ontology consists of 16 classes, 20 properties, 973 individuals.
+We matched Events, Location, City as well as Start and End date.
+The entity for Country was mistakenly matched to the Area entity.
+A visualization of the matching is presented in Figure \ref{fig:match_g13}.
 
@@
 \subsection{Group 15: Activity finding Ontology}
-In this case, the target ontology consists of 66 classes, 599 properties and 57 individuals. This is, by far, a larger ontology than ours and the previous examined ontologies.
+In this case, the target ontology consists of 66 classes, 599 properties and 57 individuals.
+This is, by far, a larger ontology than ours and the previous examined ontologies.
+A visualization of the matching is presented in Figure \ref{fig:match_g15}.
 
@@
 Be explicit about your research question and hypothesis, and discuss they might be true, or false.
-From the previous section we conclude that the ontology for group 13 matches the best to our ontology since it has the highest number of matches with the least number of mismatches.
+From the previous section we observe that the ontology for group 13 has the highest number of matches (six) with the least number of mismatches (one).
 Yet, the matching only works for one of our three basic entities (Events, Venues and Parking Spots).
 
-Moreover, conflicting with our initial hypothesis, the matching with the group 10's ontology did not perform as well as expected.
+At the same time, the ontology for group 15 produces the same number of matches (six) but it has a high number of mismatches as well (six).
+Most of the mismatches come from Properties, since this particular ontology has a high degree of customizable properties with ambiguous names.
+
+However, regardless of having the same number of matches, the ontology for group 15 led to a higher number of links to our ontology than for group 13.
+This is due to the higher overlap in instances that allows for a closer alignment.
+
+A second observation is one made for the performance of matching with group 10.
+Conflicting with our initial hypothesis, the matching with the group 10's ontology did not perform as well as expected.
 Intuitively, we believed that our ontology should have had more matches with this group, since they model the same datasets as we do.
@@
 
-A different problem occurs in the case of the matching to the ontology of group 15.
-In this case, we found overmatching since their ontology has duplicate classes for Venue and Event.
+A third observation regards a different problem occurring in the case of the matching to the ontology of group 15.
+In this case, we found overmatching since their ontology has duplicate classes for Museum, Venue and Event.
 Therefore, several metrics failed to distinguish the duplicate match resulting in AML outputting misleading results.
-This matching required the most amount of work regarding experimenting and tuning of matching.
+This matching required the most amount of work regarding experimenting and tuning of matching, as well as alignment with SILK as mentioned in Section \ref{link_g15}.
 As stated before, details as fine as the specific type of cardinality filter greatly affected the end result.
@@
 From the experiments performed we learned that great amount of work is invested in applying the correct similarity measures.
-
 Furthermore, our experience is backed up by the findings described in Section \ref{related_work}.

### 2016-05-08 milestone3/paper/paper.tex
done done done done done done dooooone

@@
 \begin{abstract}
-The abstract should summarize the contents of the paper and should
-contain at least 70 and at most 150 words. It should be written using the
-\emph{abstract} environment.
+	In this paper we build on the Ontology for Handicap Parking Spots and tackle the problem of ontology matching with same domain datasets.
+We research state of the art methods for ontology alignment and apply them to own and three other candidate ontologies.
+	We observe that for finding equivalence some matchings are straightforward while others require great amount of human interference for selecting the appropriate matching algorithm. 
+	We present the results for matching and aligning the ontologies, and discuss the findings placing them in the wider picture of Ontology matching for the Semantic Web.
 \end{abstract}

### 2016-05-17 milestone4/paper/paper.tex
uploaded paper template mls4

--- 2016-05-08 milestone3/paper/paper.tex
@@
 % first the title is needed
-\title{Ontology Matching Paper}
+\title{Data- and Systems Paper}
 
 % a short form should be given in case it is too long for the running head
-\titlerunning{Ontology Matching Paper}
+\titlerunning{Data- and Systems Paper}
 
@@
 %
-\author{Alivanistos, Dimitris. \\ Baez, Selene. \\ Jemmett, Andrea.}
+\author{Names}
 %
-\authorrunning{Alivanistos, Dimitris. \\ Baez, Selene. \\ Jemmett, Andrea.}
+\authorrunning{Put your names here}
 % (feature abused for this document to repeat the title also on left hand pages)
@@
 % unless you accept that it will be published
-\institute{\url{d.alivanistos@student.vu.nl} \and \url{s.baezsantamaria@student.vu.nl} \and \url{a.jemmett@student.vu.nl}}
+\institute{\url{first@email.nl} \and \url{second@email.nl}}
 
@@
 \section{Introduction}
-%Introduce the sections that follow.
-What is the problem this paper addresses?
-What is the core contribution of this paper, and why is that interesting?
-What method did you develop and implement?
-What is the research question or hypothesis this paper answers?
-How did you answer this question or validate your approach (empirically, analytically).
-You might want to give a brief (qualitative) sketch of the results.
-In this paper we continue the work related for creating an application for finding Handicap Parking Spots close to Event Venues in Amsterdam.
-In the previous paper, we improved on the ontology to comply with the Five Star model and linked it to other existing ontologies.
-In this paper, we continue the work by matching and aligning the ontology to other subject-related ontologies.
 
-In general, the problem of matching ontologies has been studied before by Semantic Web researchers.
-As Shvaiko et al.
-state, the problem of heterogeneity is still a challenge to be solved since ambiguity in meanings and interpretations prevent us from finding equivalences in same domain ontologies \cite{shvaiko2013ontology}.
-Ontology matching and alignment allow to merge, translate, and extend ontologies, finding correspondences both in entities, properties and instances.
-The Ontology Alignment Evaluation Initiative is an annual international competition that serves as an evaluation for state of the art alignment tools.
+\section{}
 
-With that in mind, in this paper we select relevant vocabularies from the pool of Amsterdam related ontologies in our class.
-After some comparison we selected Group 10 -an ontology for cultural activities-, Group 13 -an ontology about safety for tourists using statistical area information-, and Group 15 -an ontology for general activity finding.
+\subsection{}
 
-In the following sections we first revise existing tools for matching and aligning ontologies.
-Then we select and apply tools for matching and aligning our ontologies to the aforementioned ones, experimenting with different comparators.
-We continue to evaluate such algorithms and discuss the results.
-Finally, we conclude by summarizing the findings of the alignment to different ontologies.
+\subsection{}
 
-\section{Related Work}
-\label{related_work}
-%Give here an overview over related matching methods and how they related to your own solution.
-Cite papers that might have inspired your approach.
-Sometimes it makes sense to have this section immediately after the introduction.
-In order to match our ontology to others, we did research about state of the art matching and alignment tools.
-\cite{adaptiveInformation_2014} is a comprehensive list of the top 50 tools, separating active from inactive tools.
-Additionally, we looked at some of the tools revised by Euzenat et Al \cite{euzenat2007ontology}.
-Furthermore, we looked at the participants from the most recent OAEI.
+\section{}
 
-In the following we list the most relevant tools.
-
-\begin{enumerate}
-	\item \textbf{OLA \cite{euzenat2004ontology}:} Developed in 2004, the OWL Lite Alignment (OLA) is a tool for automatic matching of ontologies that implements the OLA algorithm designed in collaboration by the DIRO, University of Montréal and INRIA Rhône Alpes.
-It participated in OEIA 2005 \cite{euzenat2005ola} and 2007 \cite{djoufak2007ola} and increased its own results from 0.80 to 0.89 in Precision, and 0.74 to 0.87 in Recall.
-At the time, it was one of the pioneers of ontology matching, yet no it is nowadays outdated.
-	\item \textbf{S-Match \cite{giunchiglia2004s}:} S-Match is a semantic matching tool that is suitable for many applications.
-However, it is not specific for ontology matching and it has not participated in the latest OAEI.
-	\item \textbf{MapONTO \cite{an2004refining}:} MapOnto, just as S-Match, is a general purpose semantic matcher.
-It is an Initiative from the University of Toronto and it is implemented as a plug-in for Protege.
-At first sight, this option seemed promising, however the latest release is compatible with obsolete versions of Protege.
-	%\item \textbf{WordNet:Similarity \cite{pedersen2004wordnet}:} Semantic 
-	\item \textbf{AML \cite{faria2013agreementmakerlight}:} The Agreement
-	Maker Light (AML) is the improved version of the original Agreement Maker.
-It is a simple, user-friendly application for matching ontologies which also provides visualization and evaluation of the alignment.
-Further details will be discussed in Section \ref{Ontology_Matching}.
-\end{enumerate}
-
-\section{Methods, Algorithms and Implementation}
-% Introduce your method, i.e.
-the overall approach taken and the general idea, the\bibliography{paper} algorithms in general, maybe in pseudo-code and give a quick overview over the technical implementations (not too much details).
-With the results from our Related Work research, we selected AML for ontology matching and SILK for ontology alignment.
-The similarity measures applied for both of the above were studied from \cite{sun2015comparative}.
-
-% Maybe you want to separate this part into subsections for your two systems
-\subsection{Ontology Matching}
-\label{Ontology_Matching}
-Looking at the most recent OAEI results, we decided to use one of the best candidates in the OAEI of 2014: AML.
-This tool performed the best for lightweight ontologies, as measured in terms of F-measure.
-The reasons behind this choice are that AML exceeded our expectations with regard to run time results, comprehensive user interface and integrated evaluation mechanism.
-The procedure can be fully or semi automatic, with the user being presented to a fully customizable matching.
-A lexical matching is always performed, followed by other metrics the user can choose from, ranging from structure to content based and others.
-Furthermore, AML provides with visualizations for the matches as shown in Figure \ref{fig:single_match}, \ref{fig:multiple_match} and \ref{fig:incorrect_match}.
-%examples with pictures, String Matcher, Word matcher, Property matcher, Cardinality matcher and background knowledge matcher.
-
-\begin{figure}[h]\centering
-	\includegraphics[width=.8\textwidth]{img/match_city.png}
-	\caption{Visual representation of a single correct match in AML.}
-	\label{fig:single_match}
-%\end{figure}
-%\begin{figure}[h] \centering
-	\includegraphics[width=.8\textwidth]{img/match_combo.png}
-	\caption{Visual representation of multiple correct matches in AML.}
-	\label{fig:multiple_match}
-%\end{figure}
-%\begin{figure}[h] \centering
-	\includegraphics[width=.8\textwidth]{img/conflict_exhibition_exposition.png}
-	\caption{Visual representation of an incorrect match in AML.}
-	\label{fig:incorrect_match}
-\end{figure}
-
-The power of AML is shown as its ability to combine different types of matchers, in a hierarchical or concurrent manner.
-Our method was to test each matcher separately in order to study the results obtained, while in a later stage we experimented with different combination of matching (i.e.
-Word matching, String matching and Structural matching).
-Furthermore, AML also allows the user to customize the settings of the matchers.
-For example, regarding String matcher it gives the option to choose between four different similarity measures: iSub, Levenstein, Jaro-Winkler and Q-gram, as described by Sun et al.
-\cite{sun2015comparative}.
-
-\subsection{Data Linkage}
-In this section the developed Data Linkage system is presented.
-It interlinks our dataset with two other datasets from groups 13 and 15. We
-decided to implement the linking workflow and procedures using the
-\textit{Silk framework}\footnote{\url{http://silkframework.org/}} which captions
-itself as ``The Linked Data Integration Framework''. Silk is an open source
-project for integrating heterogeneous data sources and among its use cases is
-generating links between Linked Data sources, which is exactly within our needs.
-Moreover Silk provides the user with a nice and friendly Web-based GUI and a visual
-editor for linkage rules.
-
-To link two Linked Datasets using Silk first we need to define their sources,
-e.g. using a SPARQL endpoint or uploading an RDF dump. Then it is possible to
-create linkage rules by applying four different kind of operations:
-\begin{enumerate}
-	\item path-like queries to retrieve values;
-	\item transformations over those values (e.g. to-lowercase, tokenization);
-	\item comparators over values (e.g. Levenshtein distance, Jaccard
-		coefficient, equality);
-	\item aggregators over comparators output (e.g. average, minimum, maximum).
-\end{enumerate}
-It is also possible to specify a threshold for the comparator's output score,
-its weight when computing an aggregation for it or whether it is required that a
-value exists for that block\footnote{We say block because Silk uses a visual
-editor with block-shaped functionalities.}.
-
-In the following sections we show how we implemented a Data Linking system to
-link our dataset with three other datasets created by peers following our same
-class\footnote{Knowledge Representation on the Web at VU Amsterdam, 2015/2016}.
-Moreover we tried to look-up the Linked Open Data cloud searching for similar
-datasets that we could link to ours. We used
-LOTUS\footnote{\url{http://lotus.lodlaundromat.org/}}, a tool from the LOD
-Laundromat suite\footnote{\url{http://lodlaundromat.org/}}\cite{beek2014lod}
-that allows to search the LOD cloud for statements based on some query
-parameters. Unfortunately we were not able to find interesting datasets there.
-
-\subsubsection{Linking the Cultural Dataset}
-This dataset has a domain in part similar to our so the linking procedure
-is trivial and reduces to a check on the \texttt{rdfs:label} and some other
-property. An example Silk linkage rule is shown in Figure \ref{fig:link_event_g10}
-that matches events; in this case the match is checked against
-\texttt{rdfs:label} and \texttt{dc:title}. With this rule we are able to create
-15 links over 239 source and 479 target event entities.
-
-\begin{figure}[h]
-	\centering
-	\includegraphics[width=1\textwidth]{img/link_event_g10.png}
-	\caption{Silk linkage rules for events in group 10's dataset.}
-	\label{fig:link_event_g10}
-\end{figure}
-
-\subsubsection{Linking the Tourist Safety Dataset}
-In spite being about a different domain, this dataset can still be linked with
-ours for what concerns events and locations / venues. Indeed the overlap between
-events in this dataset and ours is big and we are able to match a big proportion
-of entities by using a linkage rule similar to that shown in Figure
-\ref{fig:link_event_g10} but using \texttt{rdfs:label} for both data sources.
-Using this linkage rule we are able to link 45 events and locations between the
-two datasets.
-
-\subsubsection{Linking the Activity Finding Dataset}
-For events the linkage rule is less trivial and immediate than that for the
-Cultural Dataset and involves the use of more properties and an aggregator as
-shown in Figure \ref{fig:link_event_g15}. With this linkage rule we are able to
-link 84 activities / events.
-
-\begin{figure}[h]
-	\centering
-	\includegraphics[width=1\textwidth]{img/link_event_g15.png}
-	\caption{Silk linkage rule for events in the Activity Finding Dataset.
-		\texttt{sourcePath2} contains
-		\texttt{/schema:location/schema:streetAddress} while
-		\texttt{targetPath2} contains
-		\texttt{/g6v:hasVenue/dbo:location/dbo:address}.}
-	\label{fig:link_event_g15}
-\end{figure}
-
-\section{Validation and Experiments}
-% In a scientific paper you want to show that your choice of method and algorithms was the right choice.
-So, this could be a place where you make claims or ask concrete and explicit research questions (e.g.
-with respect to runtime and/or precision/recall.
-We conducted a variety of experiments regarding the matching of our ontology (consisting of 16 classes, 24 properties and 6 individuals) to others. This was made possible by how customizable AML is.
-
-We tried different similarity measures for String and Word matching as well as different filters regarding cardinality and coherence.
-Results mostly remained unchanged, and we believe this is due to the limited size and complexity of the ontologies presented.
-However, it is worth mentioning that strict, permissive and hybrid cardinality filters had a significant impact on the resulting alignment.
-For example, with regards to the matching with group 15, hybrid or permissive filters matched our Event class with 3 different classes of their ontology while with strict filter, we got a single match.
-
-AML also has the ability to evaluate a certain match with respect to a reference match.
-This gives the option to the end user to manually force or evaluate the match and thus supervise and validate the final match.
-As so, the user can match classes or properties by hand and use the corrected match as reference for future matchings.
-
-Hereby we report the results for the best matched alignments to the three selected ontologies.
-Basic characteristics for the ontologies, as well as a visualization of the matching in AML are given for each case.
-
-\subsection{Group 10: Cultural Ontology}
-This ontology consists of 11 classes, 23 properties, 1 individual. Our ontology matches to their main entities of Events and Venues.
-
-\begin{figure}[h]\centering
-	\includegraphics[width=.7\textwidth]{img/match_g10.png}
-	\caption{Matching to group 10}
-	\label{fig:match_g10}
-\end{figure}
-
-AML found two mappings leading to the following evaluation metrics:
-
-\begin{center}
-	\begin{tabular}{| c | c | c |}
-		\hline
-		\textbf{Precision} & \textbf{Recall} & \textbf{F-measure} \\ \hline
-		100\% & 100\% & 100\% \\ \hline
-	\end{tabular}
-\end{center}
-
-\subsection{Group 13: Tourist safety Ontology}
-This ontology consists of 16 classes, 20 properties, 973 individuals. We matched Events, Location, City as well as Start and End date. The entity for Country was mistakenly matched to the Area entity.
-
-\begin{figure}[h]\centering
-	\includegraphics[width=.7\textwidth]{img/match_g13.png}
-	\caption{Matching to group 13}
-	\label{fig:match_g13}
-\end{figure}
-
-AML found 6 mappings, leading to the following evaluation metrics:
-
-\begin{center}
-	\begin{tabular}{| c | c | c |}
-		\hline
-		\textbf{Precision} & \textbf{Recall} & \textbf{F-measure} \\ \hline
-		83.3\% & 100\% & 90.9\% \\ \hline
-	\end{tabular}
-\end{center}
-
-\subsection{Group 15: Activity finding Ontology}
-In this case, the target ontology consists of 66 classes, 599 properties and 57 individuals. This is, by far, a larger ontology than ours and the previous examined ontologies.
-
-\begin{figure}[h]\centering
-	\includegraphics[width=.7\textwidth]{img/match_g15.png}
-	\caption{Matching to group 15}
-	\label{fig:match_g15}
-\end{figure}
-
-AML found 12 mappings, six correct versus six incorrect matchings, leading to the following evaluation metrics:
-
-\begin{center}
-	\begin{tabular}{| c | c | c |}
-		\hline
-		\textbf{Precision} & \textbf{Recall} & \textbf{F-measure} \\ \hline
-		54.5\% & 46.2\% & 50.0\% \\ \hline
-	\end{tabular}
-\end{center}
-
-\section{Results and Discussion}
-% Give here details about the most important results of your experiments.
-Use tables and figures, but focus on the interesting and important results.
-Make sure you describe in the text what the reviewers should see, explain what the reader sees in the tables and point to the interesting findings.
-Be explicit about your research question and hypothesis, and discuss they might be true, or false.
-From the previous section we conclude that the ontology for group 13 matches the best to our ontology since it has the highest number of matches with the least number of mismatches.
-Yet, the matching only works for one of our three basic entities (Events, Venues and Parking Spots).
-
-Moreover, conflicting with our initial hypothesis, the matching with the group 10's ontology did not perform as well as expected.
-Intuitively, we believed that our ontology should have had more matches with this group, since they model the same datasets as we do.
-However, they model characteristics of events as Entities (such as Image, Description and Time Period), while we do it as Properties.
-To the best of our knowledge, AML cannot match entities to properties.
-This discovery raises more serious questions since the limitations of matching are evident when design decisions like the ones in this case rigidly prevent proper matching and alignment.
-
-A different problem occurs in the case of the matching to the ontology of group 15.
-In this case, we found overmatching since their ontology has duplicate classes for Venue and Event.
-Therefore, several metrics failed to distinguish the duplicate match resulting in AML outputting misleading results.
-This matching required the most amount of work regarding experimenting and tuning of matching.
-As stated before, details as fine as the specific type of cardinality filter greatly affected the end result.
-
-\section{Conclusion}
-%Here you summarize the preceding sections, describe the lessons learnt and discuss future work.
-In this paper we matched our ontology for finding Handicap Parking Spots in Amsterdam to other ontologies related to entertainment in Amsterdam.
-We found that the match with the highest confidence corresponds to Group 10, but the match with highest overlap corresponds to Group 15 closely followed by Group 13.
-
-From the experiments performed we learned that great amount of work is invested in applying the correct similarity measures.
-
-Furthermore, our experience is backed up by the findings described in Section \ref{related_work}.
-As we see, Ontology matching is a growing field, that comes up with new promising tools every year.
-Yet, follow up is not consistent and a robust solution for automatic, or semi-automatic ontology matching has yet to be developed.
+\section{}
 

### 2016-05-26 milestone4/paper/paper.tex
Report structure

@@
 % first the title is needed
-\title{Data- and Systems Paper}
+\title{Data- and Systems Paper : Finding events}
 
@@
 \section{Introduction}
+- Motivation: 
+- Objective: Find events and their location
+- compare reasoning is small designed dataset versus a large complex dataset.
 
-\section{}
+\section{Related Work}
+- explain what Laundromat is
 
-\subsection{}
+\section{Datasets}
+We performed an exploratory analysis on the datasets we will be using. Hereby we describe the characteristics of both datasets.
 
-\subsection{}
+\subsection{Find a Slot dataset}
+- 1874 instances of owl:Thing
+- 479 instances of Event
+- 681 instances of Location
 
-\section{}
+\begin{lstlisting}[captionpos=b, caption=SPARQL query for counting resources per class, label=lst:sparql, basicstyle=\ttfamily\small,frame=bt]
 
-\section{}
+SELECT ?class (COUNT(?resource) as ?count) WHERE {
+?resource a ?class . 
+} GROUP BY ?class ORDER BY DESC(?count)
+
+\end{lstlisting}
+
+Graph visualization using networkx and python plotting libraries.
+
+\begin{figure}[h]
+	\centering
+	\includegraphics[width=1\textwidth]{img/findaslot_network_graph.png}
+	\caption{Silk linkage rules for events in group 10's dataset.}
+	\label{fig:link_event_g10}
+\end{figure}
+
+\subsection{LOD dataset}
+- 25 Events with Location
+
+\begin{lstlisting}[captionpos=b, caption=SPARQL query for getting Event with Location, label=lst:sparql, basicstyle=\ttfamily\small,frame=bt]
+
+prefix event: <http://purl.org/NET/c4dm/event.owl#>
+
+SELECT ?s ?p ?l
+WHERE {
+?s a event:Event .
+{ 
+bind(<http://vivoweb.org/ontology/core#hasGeographicLocation> as ?p) .
+?s ?p ?lEn
+}
+UNION
+{ 
+bind(event:place as ?p) .
+?s ?p ?lEn
+}
+?lEn rdfs:label ?l .
+}
+
+\end{lstlisting}
+
+\section{Sub-graph extraction}
+Event related graph
+
+\subsection{Sub-graph analysis}
+- new statistics
+
+\section{Event finding}
+- Query both datasets and report on instances gotten
+
+\section{Conclusion}
+Weight the differences between designing an ontology or cleaning existing ontologies.
 

### 2016-05-26 milestone4/convert-datasets.py
v4 vocab

@@ -1,0 +1,293 @@
+#!/usr/bin/env python
+
+import json
+from datetime import datetime
+from rdflib import Dataset, Graph, URIRef, Literal, Namespace, RDF, RDFS, OWL, XSD
+from iribaker import to_iri
+import requests
+from SPARQLWrapper import SPARQLWrapper, JSON
+from pprint import pprint
+
+
+resource = 'http://data.krw.d2s.labs.vu.nl/group6/findaslot/resource/'
+RESOURCE = Namespace(resource)
+vocab = 'http://data.krw.d2s.labs.vu.nl/group6/findaslot/vocab/'
+VOCAB = Namespace(vocab)
+geo = 'http://www.w3.org/2003/01/geo/wgs84_pos#'
+GEO = Namespace(geo)
+dbo = 'http://dbpedia.org/ontology/'
+DBO = Namespace(dbo)
+dbr = 'http://dbpedia.org/resource/'
+DBR = Namespace(dbr)
+
+repo_url = "http://stardog.krw.d2s.labs.vu.nl/group6"
+
+VOCAB_FILE = 'vocab_v4.ttl'
+SOURCE_DATA_DIR = '../source_datasets/'
+OUTPUT_DIR = 'data/'
+
+
+def convert_dataset(path, dataset, graph_uri, museums=True):
+    f = open(path, 'r')
+    json_data = json.load(f)
+
+    graph = dataset.graph(graph_uri)
+    country = URIRef(to_iri(dbr + 'Kingdom of the Netherlands'))
+
+    for event_data in json_data:
+        event = URIRef(to_iri(resource + event_data['title'].strip()))
+        title = Literal(event_data['title'].strip(), datatype=XSD['string'])
+
+        dates = event_data['dates']
+        if dates != []:
+            single_dates = [Literal(datetime.strptime(d, '%d-%m-%Y').date())
+                for d in dates['singles']] if dates.has_key('singles') else []
+            start_date = Literal(datetime.strptime(dates['startdate'], '%d-%m-%Y').date()) \
+                if dates.has_key('startdate') else None
+            end_date = Literal(datetime.strptime(dates['enddate'], '%d-%m-%Y').date()) \
+                if dates.has_key('enddate') and dates['enddate'] != '' else None
+
+        location_dict = event_data['location']
+        location_d_name = location_dict['name'].strip()
+        if location_d_name != '':
+            place = URIRef(to_iri(resource + location_d_name))
+            place_name = Literal(location_d_name, datatype=XSD['string'])
[…]

### 2016-05-26 milestone4/paper/paper.tex
analytics and report

--- 2016-05-17 milestone4/paper/paper.tex
@@
 % first the title is needed
-\title{Data- and Systems Paper}
+\title{Data- and Systems Paper : Finding Amsterdam}
 
@@
 \section{Introduction}
+In the journey of having a Semantic Web where everything is linked, open and reusable, dealing with volume is necessary.
+Finding specific information, and reasoning in large heterogeneous datasets will become everyday routine, thus efficient mechanisms are required to achieve these goals.
 
-\section{}
+In fact, http://iswc2016.semanticweb.org/pages/calls/research-track.html
 
-\subsection{}
+In this paper we address the previous challenge with approximation techniques as a tool for efficient reasoning over a large dataset.
+To link this to our previous work, we select the specific domain of Amsterdam, and aim to retrieve all the Amsterdam-related information from the provided \texttt{dataset} in Stardog.
 
-\subsection{}
+The goal of this assignment is to compare two approximation techniques.
+On the one hand, we randomly choose a subset of nodes, and retrieve all information related to Amsterdam.
+On the other hand, we do a smarter selection of nodes and repeat the process.
+We hypothesize the "smart selection" approach will have higher accuracy than the "random" approach on approximating the original set.
+Yet, smart selection requires statistical analysis and reasoning over the set, which brings in time and memory costs.
+Therefore, we will weight in the pros and cons of each approach.
 
-\section{}
+\section{Related Work}
+- the problem of volume in the semantic web \\
+- approximation techniques
 
-\section{}
+\section{Data Analytics}
+The \texttt{dataset} was provided on Stardog. It was created by filtering datasets on \textit{Laundromat}\footnote{\url{http://lodlaundromat.org/}}
+
+Cleaning of data, removing \#
+
+To obtain frequency statistics we use the following query:
+
+\begin{lstlisting}[captionpos=b, caption=SPARQL query for getting Event witSh Location, label=lst:sparql, basicstyle=\ttfamily\small,frame=bt]
+SELECT ?class (COUNT(?resource) as ?count) WHERE {
+?resource a ?class . 
+} GROUP BY ?class ORDER BY DESC(?count)
+\end{lstlisting}
+
+138568 owl:Thing and 36273 owl:class
+
+\begin{figure}[h]
+	\centering
+	\includegraphics[width=1\textwidth]{img/dataset_frequency.png}
+	\caption{Plot of frequencies for classes in \texttt{dataset}. \textit{owl:Thing} is excluded.}
+	\label{fig:frequency}
+\end{figure}
+
+\section{Reasoning system}
+The Stardog only interface handles the limits 
+Python code for querying and using Stardog as endpoint. 
+Query the dataset to calculate the in degree and out degree.
+
+In degree takes 55 seconds, out degree takes 46 seconds.
+
+\begin{lstlisting}[captionpos=b, caption=SPARQL query for calculating in degree of entities, label=lst:sparql, basicstyle=\ttfamily\small,frame=bt]
+SELECT
+DISTINCT ?entity
+(COUNT(distinct ?pin) as ?indegree)
+WHERE { 
+?entity a owl:Thing .
+?something ?pin ?entity .}
+GROUP by ?entity
+ORDER by desc(?indegree)
+\end{lstlisting}
+
+\begin{lstlisting}[captionpos=b, caption=SPARQL query for calculating out degree of entities, label=lst:sparql, basicstyle=\ttfamily\small,frame=bt]
+SELECT
+DISTINCT ?entity
+(COUNT(distinct ?pout) as ?outdegree)
+WHERE { 
+?entity a owl:Thing .
+?entity ?pout ?somethingelse .
+}
+GROUP by ?entity
+ORDER by desc(?outdegree)
+\end{lstlisting}
+
+\subsection{Sub-graph extraction}
+Event related graph
+
+\subsection{Sub-graph analysis}
+- new statistics
+
+\section{Experimental set up}
+
+\subsection{Event finding}
+- Query both datasets and report on instances gotten
+
+\section{Results and Discussion}
+
+\section{Conclusion}
+Through empirical methods, we compared the performance of two subsets of the main \texttt{dataset}.
+
+Weight the differences between designing an ontology or cleaning existing ontologies.
 

### 2016-05-26 milestone4/datasets analysis/frequency.py

@@ -1,0 +1,20 @@
+import numpy as np
+import matplotlib.patches as mpatches
+import matplotlib.pyplot as plt
+import csv
+
+classes = []
+count = []
+
+with open('dataset_frequency.csv', 'rb') as csvfile:
+	classreader = csv.reader(csvfile, delimiter=',', quotechar='|')
+	for row in classreader:
+		classes.append(row[0])
+		count.append(row[1])
+
+
+plt.plot(count, 'b-',linestyle='None', marker='.')
+plt.title(("Frequencies by class"))
+plt.ylabel("frequency")
+plt.xlabel("class")
+plt.show()

### 2016-05-26 milestone4/datasets analysis/outdegree.py

@@ -1,0 +1,20 @@
+import numpy as np
+import matplotlib.patches as mpatches
+import matplotlib.pyplot as plt
+import csv
+
+entities = []
+outdegree = []
+
+with open('dataset_outdegree.csv', 'rb') as csvfile:
+	classreader = csv.reader(csvfile, delimiter=',', quotechar='|')
+	for row in classreader:
+		entities.append(row[0])
+		outdegree.append(row[1])
+
+
+plt.plot(outdegree, 'b-',linestyle='None', marker='.')
+plt.title(("Out degree by entity"))
+plt.ylabel("outdegree")
+plt.xlabel("entity")
+plt.show()

### 2016-05-26 milestone4/big-queries.py
change pc...

@@ -94,6 +94,34 @@ where {
 order by asc(?dist)
 '''
 
+Q5 = '''
+prefix : <http://data.krw.d2s.labs.vu.nl/group6/findaslot/vocab/>
+prefix res: <http://data.krw.d2s.labs.vu.nl/group6/findaslot/resource/>
+prefix geof: <http://www.opengis.net/def/function/geosparql/>
+prefix ogc: <http://www.opengis.net/ont/geosparql#>
+prefix wgs: <http://www.w3.org/2003/01/geo/wgs84_pos#>
+prefix dbo: <http://dbpedia.org/ontology/>
+prefix unit: <http://qudt.org/vocab/unit#>
+
+select ?venue ?saddr ?dist
+where {
+  ?venue a :Venue ;
+        dbo:location ?vloc .
+
+  {
+    select ?saddr ?dist
+    where {
+      ?spot a :ParkingSlot ;
+			dbo:location ?sloc .
+      ?sloc dbo:address ?saddr.
+      bind(geof:distance(?vloc, ?sloc, unit:Meter) as ?dist) .
+    }
+    order by asc(?dist)
+    limit 1
+  }
+}
+'''
+
 
 if __name__ == '__main__':
     parser = argparse.ArgumentParser(
@@ -122,3 +150,8 @@ if __name__ == '__main__':
     print 'Executing Q4 on small dataset:', q4, '\n'
     q4_time = timed_query(q4, large=False, reasoning='true')
     print 'Q4 query executed in %i seconds' % q4_time
+
+    q5 = Q5 + 'limit ' + str(args.limit) if args.limit else Q5
+    print 'Executing Q5 on small dataset:', q5, '\n'
+    q5_time = timed_query(q5, large=False, reasoning='true')
+    print 'Q5 query executed in %i seconds' % q5_time

### 2016-05-27 milestone4/paper/paper.tex
related work

@@
 In the journey of having a Semantic Web where everything is linked, open and reusable, dealing with volume is necessary.
-Finding specific information, and reasoning in large heterogeneous datasets will become everyday routine, thus efficient mechanisms are required to achieve these goals.
+The same way as in "Finding Wally", the tangled world of Linked Data makes it virtually impossible to find some specific information.
+The problem becomes even more complex when the information to be retrieved is not clear, in which case the task is comparable to fishing in the darkness.
 
-In fact, http://iswc2016.semanticweb.org/pages/calls/research-track.html
+Given the trends in the Semantic Web, it is undeniable that finding specific information, and reasoning in large heterogeneous datasets will become a need.
+Thus efficient mechanisms are required to achieve these goals.
+In fact, this year's \textit{International Semantic Web Conference} \footnote{\url{http://iswc2016.semanticweb.org/pages/calls/research-track.html}}, held in Kobe, Japan, recognizes it as one of the main topics of interest, phrasing it as "Architectures and algorithms for extreme volume, heterogeneity, dynamicity, and decentralization of Semantic Web data"
 
@@
 \section{Related Work}
-- the problem of volume in the semantic web \\
-- approximation techniques
+Regardless of its importance, very few research has been done to deal with volume on the Semantic Web.
+So far, the growth rate of the Web is winning the race against scientist trying to analyse it accurately within reasonable time.
+As mentioned by many researchers in the field of the Semantic Web, reasoning with large or complex terminology is one of the well-known bottlenecks in application of ontologies, because of the computational difficulty of the task.
+
+As early as 2007, Schlobach et al.
+proposed approximation techniques based on logical assumptions of monotonicity.
+These techniques aimed to reduce the volume of data in order to improve on the running time \cite{schlobach2007anytime}
+
+Another perspective was introduced by Mika and Tummarello \cite{mika2008web} who proposed to use Grid Computing to tackle the problem of volume.
+As stated in their paper, parallelism can be used in order to analyse, query and reason with large scale RDF Data.
+Specifically for complex reasoning tasks, the strategy described includes the use of several “reasoning servers” shared across MapReduce jobs, which then cache reasoning results in large main memories, in order to complete the task at hand.
+
+%TODO done?
+%Reasoning with large or complex terminology is computationally difficult and
+%is one of the known bottlenecks in application of ontologies on the Semantic
+%Web
+
+\section{The dataset}
+\textit{Laundromat}\footnote{\url{http://lodlaundromat.org/}} is a tool for cleaning data that provides well-formed datasets of different domains and volumes.
+Searching the LOD for sets linked to the OWL ontology, we found a set of ontologies that are expressive and complex enough to pose a challenge in the context of this assignment.
+Merging of the previous produced the \texttt{dataset} that we work on in this milestone.
+This \texttt{datset} was provided to us via StarDog.
+
+The reasons why this dataset is challenging are the following:
+
+\begin{enumerate}
+	\item \textbf{Volume}: The given dataset is about 200 times larger than the ontology we created for the previous milestones.
+	\item \textbf{Heterogeneity}: It is composed by several ontologies from different domains (foaf \footnote{Friend of a friend ontology \url{http://lov.okfn.org/dataset/lov/vocabs/foaf}}, wine, scientific-research, tourism).
+	\item \textbf{Decentralization}: There is no central ontology that acts as an intermediate node for other ontologies to connect.
+\end{enumerate}
+
+Due to the above attributes, unforeseen challenges need to be tackled. These were not present in the well-designed dataset that we created previously.
 
 \section{Data Analytics}
-The \texttt{dataset} was provided on Stardog. It was created by filtering datasets on \textit{Laundromat}\footnote{\url{http://lodlaundromat.org/}}
+In order to get more detailed information regarding the \texttt{dataset} at hand, we performed an exploratory study of its most basic statistical characteristics.
+This is a X-step process that we describe now/here/something %TODO
 
-Cleaning of data, removing \#
+Step 1: Query for finding the different ontologies
+
+Step 2: Frequency of classes
 
@@
 
-\section{Reasoning system}
+Step 3: Degree
+
 The Stardog only interface handles the limits 
@@
 
-\subsection{Sub-graph extraction}
-Event related graph
+\section{Reasoning system}
+Approximation by taking high quality entities.
+For the purpose of this paper we define the quality of an entity as its in and out degree measures.
+As such, when forming subgraphs based on the "smart selection" approach we take the entities in the top X\% entities.
 
-\subsection{Sub-graph analysis}
-- new statistics
+Stardog
 
 \section{Experimental set up}
+By now we have better understanding of what the \texttt{dataset} contains. We decide to investigate information related to Amsterdam via the following query:
 
-\subsection{Event finding}
-- Query both datasets and report on instances gotten
+\begin{lstlisting}[captionpos=b, caption=SPARQL query for calculating out degree of entities, label=lst:sparql, basicstyle=\ttfamily\small,frame=bt]
+SELECT distinct ?s ?p ?a
+WHERE { 
+?a a owl:Thing ;
+rdfs:label ?la .
+?s ?p ?a .
+FILTER(contains(?la, 'msterdam'))
+} GROUP by ?a ?s ?p
+\end{lstlisting}
+
+%TODO revise
+$X$ has values of 1, 10 and 50
 
 \section{Results and Discussion}
+When ran against the whole \texttt{datset} we obtain 31 results.
+
+- results when random
+
+- results when "smart"
 

### 2016-05-27 milestone4/paper/paper.tex
anlaytics sort of maybe

@@
 As early as 2007, Schlobach et al.
-proposed approximation techniques based on logical assumptions of monotonicity.
-These techniques aimed to reduce the volume of data in order to improve on the running time \cite{schlobach2007anytime}
+\cite{schlobach2007anytime} proposed approximation techniques based on logical assumptions of monotonicity.
+These techniques aimed to reduce the volume of data in order to improve on the running time, without loosing any or most of the logic entailment.
+Similar to us, they compared the selection of random axioms to two more sophisticated methods of selection.
+However, their procedure is based on frequency, either taking the most or least occurring entities, while we propose a degree approach, taking the best well-connected entities.
 
@@
 %TODO done?
-%Reasoning with large or complex terminology is computationally difficult and
-%is one of the known bottlenecks in application of ontologies on the Semantic
-%Web
 
@@
 \textit{Laundromat}\footnote{\url{http://lodlaundromat.org/}} is a tool for cleaning data that provides well-formed datasets of different domains and volumes.
-Searching the LOD for sets linked to the OWL ontology, we found a set of ontologies that are expressive and complex enough to pose a challenge in the context of this assignment.
-Merging of the previous produced the \texttt{dataset} that we work on in this milestone.
-This \texttt{datset} was provided to us via StarDog.
+Searching the LOD for sets linked to the OWL ontology, one can find a set of ontologies that are expressive and complex enough to pose a challenge in the context of this assignment.
+Merging of some of the previous produced the \texttt{dataset} that we work on in this milestone.
+This \texttt{datset} was provided to us via the StarDog server.
 
-The reasons why this dataset is challenging are the following:
+At a first glance, the \texttt{dataset} is particularly challenging because of many varied reasons, mainly:
 
@@
 	\item \textbf{Volume}: The given dataset is about 200 times larger than the ontology we created for the previous milestones.
-	\item \textbf{Heterogeneity}: It is composed by several ontologies from different domains (foaf \footnote{Friend of a friend ontology \url{http://lov.okfn.org/dataset/lov/vocabs/foaf}}, wine, scientific-research, tourism).
+	\item \textbf{Heterogeneity}: It is composed by several ontologies from different domains (e.g the foaf \footnote{Friend of a friend ontology \url{http://lov.okfn.org/dataset/lov/vocabs/foaf}}, a wine ontology, a scientific-research ontology and a tourism ontology).
+Furthermore it comprises several different languages.
 	\item \textbf{Decentralization}: There is no central ontology that acts as an intermediate node for other ontologies to connect.
@@
 
-Due to the above attributes, unforeseen challenges need to be tackled. These were not present in the well-designed dataset that we created previously.
+Due to the above attributes, unforeseen challenges need to be tackled.
+These were not present in the well-designed dataset that we created previously, therefore the reasoning methods we used before are not sufficient and need to be extended.
 
 \section{Data Analytics}
-In order to get more detailed information regarding the \texttt{dataset} at hand, we performed an exploratory study of its most basic statistical characteristics.
-This is a X-step process that we describe now/here/something %TODO
+Before reasoning or extracting any valuable information about the \texttt{dataset}, we first need to delve deeper into it to understand its content.
+In order to get more details, we performed an exploratory study of its most basic statistical characteristics.
+We did this in a 3-step process the we describe in the following subsections.
 
-Step 1: Query for finding the different ontologies
+\subsection{Step 1: Query for finding the different ontologies}
+First we needed to characterize the content of the \texttt{dataset} by the domains it refers to. To do so we query the ontologies that are present
 
-Step 2: Frequency of classes
+\begin{lstlisting}[captionpos=b, caption=SPARQL query for getting different Ontologies in the \texttt{dataset}, label=lst:sparql, basicstyle=\ttfamily\small,frame=bt]
+SELECT DISTINCT ?entity ?elabel ?type ?tlabel 
+WHERE { 
+	?entity a ?type .
+	?type rdfs:label 'Ontology' .
+	OPTIONAL { ?entity rdfs:label ?elabel } . 
+	OPTIONAL { ?type rdfs:label ?tlabel } 
+}
+\end{lstlisting}
 
+\subsection{Step 2: Frequency of classes}
 To obtain frequency statistics we use the following query:
@@
 
-138568 owl:Thing and 36273 owl:class
+The most frequent is owl:Thing with 138568 occurrences.
+Interestingly the second most frequent is not the owl:Class, with 36273 occurrences, but a class related to provenance as opmo:WasControlledBy with 38165 occurrences.
 

### 2016-05-27 milestone4/paper/paper.tex
reasoning

@@
 Before reasoning or extracting any valuable information about the \texttt{dataset}, we first need to delve deeper into it to understand its content.
-In order to get more details, we performed an exploratory study of its most basic statistical characteristics.
-We did this in a 3-step process the we describe in the following subsections.
+In order to get more details, we perform an exploratory study of its most basic statistical characteristics.
+We do this in a 3-step process that we describe in the following subsections.
 
 \subsection{Step 1: Query for finding the different ontologies}
-First we needed to characterize the content of the \texttt{dataset} by the domains it refers to. To do so we query the ontologies that are present
+First we need to characterize the content of the \texttt{dataset} by the domains it refers to.
+To do so we query the \texttt{dataset}, using Stardog as endpoint, to get the ontologies that are present.
+The query is presented in Listing \ref{ontology_query}.
 
@@
 \end{lstlisting}
+\label{ontology_query}
+
+We note that the \texttt{dataset} is composed of 103 ontologies with seemingly unrelated domains. Some examples are listed here:
+
+\begin{itemize}
+	\item \url{http://www.kanzaki.com/ns/music}: A music vocabulary
+	\item \url{http://www.w3.org/TR/2003/PR-owl-guide-20031209/wine}: A wine ontology
+	\item \url{http://aims.fao.org/aos/geopolitical.owl}: A geopolitical ontology
+	\item \url{ http://rhizomik.net/ontologies/copyrightonto.owl}: A copyright ontology
+\end{itemize}
 
 \subsection{Step 2: Frequency of classes}
-To obtain frequency statistics we use the following query:
+Secondly, we would like to count the class occurrences in the \texttt{dataset}, similar to Schlobach et al \cite{schlobach2007anytime}.
+To do so, we obtain frequency statistics using the following query:
 
-\begin{lstlisting}[captionpos=b, caption=SPARQL query for getting Event witSh Location, label=lst:sparql, basicstyle=\ttfamily\small,frame=bt]
-SELECT ?class (COUNT(?resource) as ?count) WHERE {
+\begin{lstlisting}[captionpos=b, caption=SPARQL query for getting class frequencies, label=lst:sparql, basicstyle=\ttfamily\small,frame=bt]
+SELECT ?class (COUNT(?resource) as ?count) 
+WHERE {
 	?resource a ?class . 
@@
 
-The most frequent is owl:Thing with 138568 occurrences.
-Interestingly the second most frequent is not the owl:Class, with 36273 occurrences, but a class related to provenance as opmo:WasControlledBy with 38165 occurrences.
+The most frequent class is owl:Thing with 138,568 occurrences.
+Interestingly the second most frequent class is not the owl:Class, with 36,273 occurrences, but a class related to provenance as opmo:WasControlledBy with 38,165 occurrences.
+More details on the top 10 classes is given in Table \ref{frequency_table}.
+A visualization of the frequencies is shown in Figure \ref{fig:frequency}, excluding the first (owl:Thing) due to axis boundaries.
+
+\begin{table}[h]
+	\begin{center}
+		\begin{tabular}{| l | c |}
+			\hline
+			\textbf{Class} & \textbf{Count} \\ \hline
+			owl:Thing &	138568 \\ \hline
+			http://openprovenance.org/model/opmo\#WasControlledBy & 38165 \\ \hline
+			owl:Class &	36273 \\ \hline
+			owl:Restriction	& 30554 \\ \hline
+			http://vivoweb.org/ontology/core\#DateTimeValue &	27041 \\ \hline
+			http://vivoweb.org/ontology/core\#DateTimeInterval &	24804 \\ \hline
+			http://vivoweb.org/ontology/core\#Role &	23561 \\ \hline
+			http://vivoweb.org/ontology/core\#TeacherRole &	23373 \\ \hline
+			http://vivoweb.org/ontology/core\#Relationship &	20946 \\ \hline
+			http://vivoweb.org/ontology/core\#Authorship &	20938 \\ \hline
+		\end{tabular}
+		\caption{Top 10 classes with respect to frequency in \texttt{dataset}.}
+		\label{frequency_table}
+	\end{center}
+\end{table}
 
@@
 	\centering
-	\includegraphics[width=1\textwidth]{img/dataset_frequency.png}
+	\includegraphics[width=.7\textwidth]{img/dataset_frequency.png}
 	\caption{Plot of frequencies for classes in \texttt{dataset}. \textit{owl:Thing} is excluded.}
@@
 
-Step 3: Degree
+\subsection{Step 3: Degree}
+Finally, inspired by network analytics we decided to calculate the in-degree and out-degree of each entity.
+This time the queries could not be computed directly in the Stardog web application, since it automatically handles the limits of the queries and truncates the results.
+Therefore, we create our own Python script to submit queries to the Stardog endpoint and get full results.
 
-The Stardog only interface handles the limits 
-Python code for querying and using Stardog as endpoint. 
-Query the dataset to calculate the in degree and out degree.
-
-In degree takes 55 seconds, out degree takes 46 seconds.
+The in-degree and out-degree queries are shown in the following two Listings:
 
 \begin{lstlisting}[captionpos=b, caption=SPARQL query for calculating in degree of entities, label=lst:sparql, basicstyle=\ttfamily\small,frame=bt]
-SELECT
-DISTINCT ?entity
+SELECT DISTINCT ?entity
 	(COUNT(distinct ?pin) as ?indegree)
@@
 		?entity a owl:Thing .
-?something ?pin ?entity .}
+		?something ?pin ?entity .
+	}
 GROUP by ?entity
@@
 \begin{lstlisting}[captionpos=b, caption=SPARQL query for calculating out degree of entities, label=lst:sparql, basicstyle=\ttfamily\small,frame=bt]
-SELECT
-DISTINCT ?entity
+SELECT DISTINCT ?entity
 	(COUNT(distinct ?pout) as ?outdegree)
@@
 
+We observe an increase in the time complexity for these queries.
+The in-degree query takes 55 seconds, while out-degree query takes 46 seconds, compared to the queries in the previous two subsections that are performed almost instantaneously.
+
+The results for in-degree range between [1, 13] while the ones for out-degree lie in the range of [1, 81]. Figures \ref{fig:indegree} and \ref{fig:outdegree} visualize the distributions.
+
+\begin{figure}[h]
+	\centering
+	\includegraphics[width=.7\textwidth]{img/dataset_indegree.png}
+	\caption{Plot of in-degree for entities in \texttt{dataset}.}
+	\label{fig:indegree}
+\end{figure}
+
+\begin{figure}[h]
+	\centering
+	\includegraphics[width=.7\textwidth]{img/dataset_outdegree.png}
+	\caption{Plot of out-degree for entities in \texttt{dataset}.}
+	\label{fig:outdegree}
+\end{figure}
+
 \section{Reasoning system}
-Approximation by taking high quality entities.
-For the purpose of this paper we define the quality of an entity as its in and out degree measures.
-As such, when forming subgraphs based on the "smart selection" approach we take the entities in the top X\% entities.
+Using the last information, we can now perform approximation techniques by taking high quality entities.
+For the purpose of this paper we define the quality of an entity as its out-degree, since we believe it reflects how well-connected an entity is.
+As such, when forming subgraphs we take only entities that satisfy a certain threshold $ out-degree > threshold$.
 
-Stardog
+Since the out-degree distribution has a heavy tail, we select $threshold = 10, 20, 40, 75$ as approximate quartiles.
+We observe that the number of triples retrieved by the query is linear to the proposed quartiles.
 
 \section{Experimental set up}
-By now we have better understanding of what the \texttt{dataset} contains. We decide to investigate information related to Amsterdam via the following query:
+By now we have better understanding of what the \texttt{dataset} contains. We decide to investigate information related to The Netherlands via the following query:
 
 \begin{lstlisting}[captionpos=b, caption=SPARQL query for calculating out degree of entities, label=lst:sparql, basicstyle=\ttfamily\small,frame=bt]
-SELECT distinct ?s ?p ?a
+SELECT ?s ?p
 WHERE {
-?a a owl:Thing ;
-rdfs:label ?la .
-?s ?p ?a .
-FILTER(contains(?la, 'msterdam'))
-} GROUP by ?a ?s ?p
+bind(<http://aims.fao.org/aos/geopolitical.owl#Netherlands_the> 
+	as ?nl) .
+{ ?s ?p ?nl }
+UNION
+{ ?nl ?p ?s }
+UNION
+{
+?s ?p ?o .
+?o ?p1 ?nl
+}
+UNION
+{
+?nl ?p ?o .
+?o ?p1 ?s
+}
+}
 \end{lstlisting}
-
-%TODO revise
-$X$ has values of 1, 10 and 50
 

### 2016-05-27 milestone4/datasets analysis/indegree.py

@@ -1,0 +1,20 @@
+import numpy as np
+import matplotlib.patches as mpatches
+import matplotlib.pyplot as plt
+import csv
+
+entities = []
+indegree = []
+
+with open('dataset_indegree.csv', 'rb') as csvfile:
+	classreader = csv.reader(csvfile, delimiter=',', quotechar='|')
+	for row in classreader:
+		entities.append(row[0])
+		indegree.append(row[1])
+
+
+plt.plot(indegree, 'b-',linestyle='None', marker='.')
+plt.title(("In degree by entity"))
+plt.ylabel("indegree")
+plt.xlabel("entity")
+plt.show()

### 2016-05-27 milestone4/big-queries.py
query local db

@@ -30,7 +30,7 @@ def run_query(query, large=True, reasoning='true'):
 def timed_query(query, large=True, reasoning='false'):
     """Run a timed SPARQL query"""
     t1 = time.time()
-    run_query(IN_QUERY, large=large, reasoning=reasoning)
+    run_query(query, large=large, reasoning=reasoning)
     t2 = time.time()
     return t2 - t1
 

### 2016-05-27 milestone4/query_local.py

@@ -1,0 +1,74 @@
+#!/usr/bin/env python
+
+from SPARQLWrapper import SPARQLWrapper, JSON
+from datetime import datetime
+import time
+
+
+def run_query(query, reasoning='true', endpoint='http://localhost:5820/out-75/query'):
+    """Run a SPARQL query against the endpoint"""
+    sparql = SPARQLWrapper(endpoint)
+
+    sparql.setQuery(query)
+
+    sparql.setReturnFormat(JSON)
+    sparql.addParameter('Accept','application/sparql-results+json')
+
+    sparql.addParameter('reasoning',reasoning)
+    sparql.setCredentials('admin', 'admin')
+
+    response = sparql.query().convert()
+
+    return response['results']['bindings']
+
+
+def timed_query(query, reasoning='true', endpoint='http://localhost:5820/out-75/query'):
+    """Run a timed SPARQL query"""
+    t1 = datetime.now().microsecond
+    print run_query(query, reasoning=reasoning, endpoint=endpoint)
+    t2 = datetime.now().microsecond
+    return t2 - t1
+
+Q = '''
+select (count(distinct ?s) as ?count)
+where {
+	bind(<http://aims.fao.org/aos/geopolitical.owl#Netherlands_the> as ?nl) .
+	{ ?s ?p ?nl }
+	union
+	{ ?nl ?p ?s }
+}
+'''
+'''
+	union
+	{
+	?s ?p ?o .
+		?o ?p1 ?nl
+    }
+	union
+	{
+	?nl ?p ?o .
+		?o ?p1 ?s
+    }
+}
+'''
+endpoint = 'http://localhost:5820/out-{}/query'
+
+if __name__ == '__main__':
+    print 'Executing query out-10:', Q, '\n'
+    in_time = timed_query(Q, endpoint=endpoint.format(10))
+    print 'Query executed in %i microseconds\n' % in_time
+    time.sleep(1)
+
+    print 'Executing query out-20:', Q, '\n'
+    in_time = timed_query(Q, endpoint=endpoint.format(20))
+    print 'Query executed in %i microseconds\n' % in_time
+    time.sleep(1)
+
+    print 'Executing query out-40:', Q, '\n'
+    in_time = timed_query(Q, endpoint=endpoint.format(40))
+    print 'Query executed in %i microseconds\n' % in_time
+    time.sleep(1)
+
+    print 'Executing query out-75:', Q, '\n'
[…]

### 2016-05-27 milestone4/paper/paper.tex
full reasoning

@@
 In this paper we address the previous challenge with approximation techniques as a tool for efficient reasoning over a large dataset.
-To link this to our previous work, we select the specific domain of Amsterdam, and aim to retrieve all the Amsterdam-related information from the provided \texttt{dataset} in Stardog.
+To link this to our previous work, we select the specific domain of Geographical Locations, and aim to retrieve all the information related to The Netherlands from the provided \texttt{dataset} in Stardog.
 
-The goal of this assignment is to compare two approximation techniques.
-On the one hand, we randomly choose a subset of nodes, and retrieve all information related to Amsterdam.
-On the other hand, we do a smarter selection of nodes and repeat the process.
-We hypothesize the "smart selection" approach will have higher accuracy than the "random" approach on approximating the original set.
-Yet, smart selection requires statistical analysis and reasoning over the set, which brings in time and memory costs.
-Therefore, we will weight in the pros and cons of each approach.
+The goal of this assignment is to perform approximation techniques by a smart selection of nodes that successfully retrieve all, or nearly all, information related to The Netherlands.
 
@@
 
-%TODO done?
-
 \section{The dataset}
-\textit{Laundromat}\footnote{\url{http://lodlaundromat.org/}} is a tool for cleaning data that provides well-formed datasets of different domains and volumes.
+\textit{Laundromat}\footnote{\url{http://lodlaundromat.org/}} is a tool for cleaning data that provides well-formed datasets of different domains and volumes \cite{beek2014lod}.
 Searching the LOD for sets linked to the OWL ontology, one can find a set of ontologies that are expressive and complex enough to pose a challenge in the context of this assignment.
@@
 As such, when forming subgraphs we take only entities that satisfy a certain threshold $ out-degree > threshold$.
+The subgraphs are retrieved by the query described in the following Listing, and downloaded to reason in a local instance of Stardog.
 
-Since the out-degree distribution has a heavy tail, we select $threshold = 10, 20, 40, 75$ as approximate quartiles.
-We observe that the number of triples retrieved by the query is linear to the proposed quartiles.
+\begin{lstlisting}[captionpos=b, caption=SPARQL query for calculating out degree of entities, label=lst:sparql, basicstyle=\ttfamily\small,frame=bt]
+CONSTRUCT {
+	?entity ?pout ?something
+} WHERE { 
+{
+	SELECT
+	DISTINCT ?entity
+	(count(distinct ?pout) as ?outdegree)
+	WHERE {
+		?entity ?pout ?something .
+	}
+	GROUP by ?entity
+}
+FILTER(?outdegree > 75) .
+?entity ?pout ?something
+}
+\end{lstlisting}
+
+Since the out-degree distribution has a heavy tail, we select $threshold = 10, 20, 40, 75$ as approximate quartiles. As you see here the number of triples grows linearly .
+
+\begin{table}[h]
+	\begin{center}
+		\begin{tabular}{| l | c | c |}
+			\hline
+			\textbf{Threshold} & \textbf{n of triples} & \textbf{Time} \\ \hline
+			10 &  505,993 & 00:00:03.663 \\ \hline
+			20 & 34,785 & 00:00:00.294 \\ \hline
+			40 & 25,602 & 00:00:00.200 \\ \hline
+			75 & 17,359 & 00:00:00.128 \\ \hline
+		\end{tabular}
+		\caption{Statistics for subgraph formation.}
+		\label{frequency_table}
+	\end{center}
+\end{table}
 
@@
 \section{Conclusion}
-Through empirical methods, we compared the performance of two subsets of the main \texttt{dataset}.
-
-Weight the differences between designing an ontology or cleaning existing ontologies.
+In this paper we used empirical and statistical methods in order to tackle the problem of volume while reasoning over large RDF triple-stores.
+We analyzed the reasons behind the necessity of dealing with this issue, as the Semantic Web grows with an exponential rate.
+Thus we analyzed the large dataset that was provided to us in order to find meaningful way of approximation.
+After analyzing the dataset we chose 3 criteria for approximation: Entity frequency, In-degree and Out-degree.
+Visualization of the results into graphs proved to be insightful and useful in deciding how to extract sub-sets.
+Furthermore we have conducted experiments and got promising results.
+After comparing our chosen methods, we came to the conclusion that splitting a large set of ontologies into smaller ones that are more meaningful to the domain of the task, is the proper way to tackle the problem.
+The inspiration derived from the methods used in the paper of blabla, who deal with volume with a Map-Reduce framework.
+Even though we did not implement a Map-Reduce framework for the experiments of this paper, the concept is similar.
+We firmly believe that \texttt{divide and conquer}  can be proved to be the way to deal with the problem of Volume in reasoning and overcome what has been considered a bottleneck of the Semantic Web for years.
 

### 2016-05-27 milestone4/paper/paper.tex
results table

@@
 
-Since the out-degree distribution has a heavy tail, we select $threshold = 10, 20, 40, 75$ as approximate quartiles. As you see here the number of triples grows linearly .
+Since the out-degree distribution has a heavy tail, we select $threshold = 10, 20, 40, 75$ as approximate quartiles. As you see in Table \ref{subgraph_table} the number of triples grows linearly .
 
@@
 		\caption{Statistics for subgraph formation.}
-		\label{frequency_table}
+		\label{subgraph_table}
 	\end{center}
@@
 \section{Results and Discussion}
-When ran against the whole \texttt{datset} we obtain 31 results.
-
-- results when random
-
-- results when "smart"
+\begin{table}[h]
+	\begin{center}
+		\begin{tabular}{| l | c | c |}
+			\hline
+			\textbf{Subgraph} & \textbf{Results count} & \textbf{Time in microseconds} \\ \hline
+			out-10 & 1144 & -343883 \\ \hline
+			out-20 & 99 & 138225 \\ \hline
+			out-40 & 95 & 59086 \\ \hline
+			out-75 & 94 & 51484 microseconds \\ \hline
+		\end{tabular}
+		\caption{Statistics for subgraph formation.}
+		\label{subgraph_table}
+	\end{center}
+\end{table}
 

### 2016-05-27 milestone4/paper/paper.tex
abstract and results table

@@
 % first the title is needed
-\title{Data- and Systems Paper : Finding Amsterdam}
+\title{Reasoning : A well known bottleneck and ways to tackle it}
 
@@
 \begin{abstract}
-The abstract should summarize the contents of the paper and should
-contain at least 70 and at most 150 words. It should be written using the
-\emph{abstract} environment.
+In this paper we aim to tackle the well-known problem of dealing with large volume in the Semantic Web.
+We do so by applying approximation techniques and query subgraphs of a large heterogeneous, decentralized dataset.
+We perform different analysis of the given dataset on order to have a better understanding of its content, as well as to gain some insight as to which entities might be more relevant when having a domain specific query.
+The formation of the subgraphs is done by selecting highly connected entities, which is defined and controlled by its out-degree measure.
 \end{abstract}
@@
 	\begin{center}
-		\begin{tabular}{| l | c | c |}
+		\begin{tabular}{| l | c | c | c |}
 			\hline
-			\textbf{Subgraph} & \textbf{Results count} & \textbf{Time in microseconds} \\ \hline
-			out-10 & 1144 & -343883 \\ \hline
-			out-20 & 99 & 138225 \\ \hline
-			out-40 & 95 & 59086 \\ \hline
-			out-75 & 94 & 51484 microseconds \\ \hline
+			\textbf{Subgraph} & \textbf{Results count} & \textbf{Time in microseconds} & \textbf{Time/Count ratio} \\ \hline
+			out-10 & 1144 & 343,883 & 2388,076388889 \\ \hline
+			out-20 & 99 & 138,225 & 1396,212121212 \\ \hline
+			out-40 & 95 & 59,086 & 621,957894737 \\ \hline
+			out-75 & 94 & 51,484 & 547,70212766 \\ \hline
 		\end{tabular}
@@
 Furthermore we have conducted experiments and got promising results.
-After comparing our chosen methods, we came to the conclusion that splitting a large set of ontologies into smaller ones that are more meaningful to the domain of the task, is the proper way to tackle the problem.
+After comparing our chosen methods, we came to the conclusion that splitting a large set of ontologies into smaller ones that are more meaningful out-degree wise, is the proper way to tackle the problem.
 The inspiration derived from the methods used in the paper of blabla, who deal with volume with a Map-Reduce framework.

### 2016-05-27 milestone4/paper/paper.tex
done :dancer:

@@
 \begin{lstlisting}[captionpos=b, caption=SPARQL query for calculating out degree of entities, label=lst:sparql, basicstyle=\ttfamily\small,frame=bt]
-CONSTRUCT {
-	?entity ?pout ?something
+CONSTRUCT { ?entity ?pout ?something
 } WHERE { 
@@
 		?entity ?pout ?something .
-	}
-	GROUP by ?entity
+	} 	GROUP by ?entity
 }
@@
 SELECT ?s ?p
-WHERE {
-bind(<http://aims.fao.org/aos/geopolitical.owl#Netherlands_the> 
+WHERE { bind(<http://aims.fao.org/aos/geopolitical.owl#Netherlands_the> 
 	as ?nl) .
 { ?s ?p ?nl }
-UNION
-{ ?nl ?p ?s }
-UNION
-{
-?s ?p ?o .
-?o ?p1 ?nl
-}
-UNION
-{
-?nl ?p ?o .
-?o ?p1 ?s
-}
+UNION { ?nl ?p ?s }
+UNION { ?s ?p ?o .
+		?o ?p1 ?nl }
+UNION {	?nl ?p ?o .
+		?o ?p1 ?s }
 }
@@
 \section{Results and Discussion}
+We run the query against the four extracted subsets. Results are visible in Table~\ref{query_table}.
+
 \begin{table}[h]
@@
 			\textbf{Subgraph} & \textbf{Results count} & \textbf{Time in microseconds} & \textbf{Time/Count ratio} \\ \hline
-			out-10 & 1144 & 343,883 & 2388,076388889 \\ \hline
-			out-20 & 99 & 138,225 & 1396,212121212 \\ \hline
-			out-40 & 95 & 59,086 & 621,957894737 \\ \hline
-			out-75 & 94 & 51,484 & 547,70212766 \\ \hline
+			out-10 & 1144 & 343883 & 2388,076388889 \\ \hline
+			out-20 & 99 & 138225 & 1396,212121212 \\ \hline
+			out-40 & 95 & 59086 & 621,957894737 \\ \hline
+			out-75 & 94 & 51484 & 547,70212766 \\ \hline
 		\end{tabular}
-		\caption{Statistics for subgraph formation.}
-		\label{subgraph_table}
+		\caption{Statistics for retrieving information about The Netherlands.}
+		\label{query_table}
 	\end{center}
 \end{table}
+
+It is possible to see how a bigger dataset requires
+increasingly more time to return information. At the same time the number
+of triples returned decreases meaningfully. From the ratio column we can see that
+this metric can be increased significantly by extracting a subset until we reach
+40 as out-degree, after which the time gain is not representative of the increase in the triple-set returned.
+Furthermore, we note that after the 10 out-degree, the number of triples returned is reduced by 90\%.
 
@@
 Visualization of the results into graphs proved to be insightful and useful in deciding how to extract sub-sets.
+
 Furthermore we have conducted experiments and got promising results.
-After comparing our chosen methods, we came to the conclusion that splitting a large set of ontologies into smaller ones that are more meaningful out-degree wise, is the proper way to tackle the problem.
-The inspiration derived from the methods used in the paper of blabla, who deal with volume with a Map-Reduce framework.
+After comparing different thresholds, we come to the conclusion that splitting a large set of ontologies into smaller ones that are more meaningful out-degree wise is a valid way to tackle the problem.
+The inspiration derived from the methods used in the paper of Mika \cite{mika2008web}, who deal with volume with a Map-Reduce framework.
 Even though we did not implement a Map-Reduce framework for the experiments of this paper, the concept is similar.
+
 We firmly believe that \texttt{divide and conquer}  can be proved to be the way to deal with the problem of Volume in reasoning and overcome what has been considered a bottleneck of the Semantic Web for years.
